### 2021-01-18 paper/authors.tex
Adding paper draft

\collaboration{1000}{The LSST Dark Energy Science Collaboration (LSST DESC)}
\noaffiliation

% paper leads
\author{Denize Lanzieri}
\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}

\author[0000-0001-7956-0542]{Fran\c{c}ois Lanusse}
\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}

%main partticipants and text contributors  (alphabetical)
\author{Chirag Modi}
\noaffiliation

% minor contributions and/or text writers (alphabetical)

### 2021-01-18 paper/paper.tex
Adding paper draft

\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
\documentclass[twocolumn,twocolappendix]{aastex63}

% Add your own macros here:
\pdfoutput=1 %for arXiv submission
%\usepackage{amsmath,amssymb,amstext}
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage{ae,aecompl}
\usepackage[utf8]{inputenc}
\usepackage[figure,figure*]{hypcap}

\usepackage{url}
\urlstyle{same}

\usepackage{lineno}
\linenumbers
%\modulolinenumbers[2]

\newcommand{\placeholder}[1]{\textit{PLACEHOLDER: #1}}

% header settings
\shorttitle{Tomographic binning optimization}
\shortauthors{Author A et al.\ (LSST~DESC)}

% ======================================================================

\begin{document}
\title{Forecasting the power of Higher Order Weak Lensing Statistics with automatically differentiable simulations}
\input{authors}

\begin{abstract}
In this project we investigate the relative constraining power of various map-based higher order weak lensing statistics in an LSST setting. Such comparisons are typically very costly as they require a large number of simulations, and become intractable for more than 3 or 4 cosmological parameters. Instead we propose a new methodology based on the TensorFlow framework for automatic differentiation, and more specifically the public FlowPM N-body simulation code. By implementing ray-tracing in this framework, we will be able to simulate lensing lightcones, and compute Higher Order lensing statistics on the resulting maps. These statistics can then be differentiated with respect to cosmology, or any systematics included in the simulations, thus allowing, for exact Fisher forecasts.  
\end{abstract}

\keywords{methods: statistical -- dark energy}

%\accepted{}
%\submitjournal{the Astrophysical Journal Supplement}

%\tableofcontents%-----------------------------
%===========================
% BEGINNING OF THE MAIN TEXT
%===========================

\section{Introduction}

\section{Ray-tracing}

\section{Methods}

\section{Results}

\section{Discussion}

\subsection{Future directions}

\section{Conclusions}

%=====================
% END OF THE MAIN TEXT
%=====================

\end{document}

### 2021-03-08 DifferentiableHOS/__init__.py
Adds wavelet decomposition

@@ -1,0 +1,1 @@
+import DifferentiableHOS.transforms as transforms

### 2021-03-08 DifferentiableHOS/statistics/__init__.py

@@ -1,0 +1,1 @@
+from .angular_power_tf.py import measure_power_spectrum_tf as power_spectrum

### 2021-03-08 DifferentiableHOS/transforms.py

@@ -1,0 +1,38 @@
+# This module contains code for computing a wavelet transform of a field
+import tensorflow as tf
+
+
+def starlet2d(image, nscales=4, name="starlet2d"):
+  """ Computes the multiscale 2D starlet transform of an image.
+
+  This function only keeps "VALID" regions, i.e. discarding coefficients
+  affected by border effects. As a result, each wavelet scale has a
+  different shape.
+
+  Args:
+    image: `tf.Tensor` of shape [batch_size, h, w] representing the input
+      image.
+    nscales: `int`. Number of scales to include in the decomposition.
+  Returns:
+    wavelet_decomposition: `list` of `tf.Tensor` representing each wavelet
+      scale plus the smooth approximation.
+  """
+  with tf.name_scope(name):
+    image = tf.convert_to_tensor(image, dtype=tf.float32)
+    image = tf.expand_dims(image, axis=-1)
+
+    # Create the b-spline filter
+    h = tf.constant([1, 4, 6, 4, 1], dtype=tf.float32) / 16.
+    # Expand to 2d, and reshape appropriately
+    W = tf.reshape(tf.tensordot(h, h, axes=0), [5, 5, 1, 1])
+
+    coeffs = []
+    approx = image
+
+    for i in range(nscales):
+      c_i = tf.nn.atrous_conv2d(approx, W, 2**i, padding="VALID")
+      _, h, w, c = tf.shape(c_i)
+      coeffs.append(tf.image.resize_with_crop_or_pad(approx, h, w) - c_i)
+      approx = c_i
+    coeffs.append(approx)
+    return coeffs

### 2021-03-08 setup.py

@@ -1,0 +1,24 @@
+from setuptools import find_packages
+from setuptools import setup
+
+setup(name='DifferentiableHOS',
+      description='Differentiable Higher Order Statistics in TensorFlow',
+      author='Denise Lanzieri',
+      license='MIT',
+      packages=find_packages(),
+      install_requires=[
+          'flowpm'
+      ],
+      tests_require=['lenspack'],
+      extras_require={
+          'testing': ['lenspack'],
+      },
+      use_scm_version=True,
+      setup_requires=['setuptools_scm'],
+      classifiers=[
+          'Development Status :: 3 - Alpha', 'Intended Audience :: Developers',
+          'Intended Audience :: Science/Research',
+          'License :: OSI Approved :: MIT License',
+          'Topic :: Scientific/Engineering :: Physics'
+      ],
+      keywords='cosmology')

### 2021-03-08 tests/test_wavelet.py

@@ -1,0 +1,27 @@
+import tensorflow as tf
+import numpy as np
+import lenspack
+import DifferentiableHOS
+from numpy.testing import assert_allclose
+
+
+def test_starlet2d():
+  """ Tests the starlet decomposition against lenspack
+  """
+  # Create test image
+  im = np.random.rand(64, 64).astype('float32')
+
+  # Compute wavelet decomposition using TF
+  tf_coeffs = DifferentiableHOS.transforms.starlet2d(im.reshape(1, 64, 64),
+                                                     nscales=3)
+
+  # Compute wavelet decomposition using Lenspack
+  lp_coeffs = lenspack.image.transforms.starlet2d(im, nscales=3)
+
+  # And now comparing results
+  for tf_coeff, lp_coeff in zip(tf_coeffs, lp_coeffs):
+    _, h, w, c = tf.shape(tf_coeff)
+    # Discarding borders from the lenspack image
+    lp_coeff = tf.image.resize_with_crop_or_pad(lp_coeff.reshape((1, 64, 64, 1)),
+                                                h, w)
+    assert_allclose(tf_coeff, lp_coeff, atol=1e-6)

### 2021-03-09 DifferentiableHOS/__init__.py
Add differentiable l1norm

@@ -1,1 +1,2 @@
 import DifferentiableHOS.transforms as transforms
+import DifferentiableHOS.statistics as statistics

### 2021-03-09 DifferentiableHOS/statistics/__init__.py

@@ -1,1 +1,2 @@
-from .angular_power_tf.py import measure_power_spectrum_tf as power_spectrum
+from .angular_power_tf import measure_power_spectrum_tf as power_spectrum
+from .l1norm import l1norm

### 2021-03-09 DifferentiableHOS/statistics/l1norm.py

@@ -1,0 +1,57 @@
+# This module implements the l1 norm statistic described in
+# Ajani et al. 2021 https://arxiv.org/abs/2101.01542
+import tensorflow as tf
+import numpy as np
+from DifferentiableHOS.transforms import starlet2d
+
+__all__ = ['l1norm']
+
+
+def _get_wavelet_normalization(image, nscales):
+  """ Computes normalizing constant for starlet, for given image.
+  """
+  _, nx, ny = image.get_shape()
+  knorm = tf.ones((1, 1, 1, 1), dtype=tf.float32)
+  knorm = tf.image.resize_with_crop_or_pad(knorm, nx, ny)
+  wt = starlet2d(knorm[..., 0], nscales=nscales)
+  return [tf.math.sqrt(tf.reduce_sum(c**2)) for c in wt]
+
+
+def l1norm(image, nscales=3, value_range=[-1., 1.], nbins=16, name='l1norm'):
+  """ Computes the starlet l1-norm statistic on the input image.
+
+  Args:
+    image: `tf.Tensor` reprensenting the input image to process.
+    nscales: `int` representing the number of wavelet scales to include
+      in the decomposition.
+    value_range: Shape [2] Tensor of same dtype as image, determines the
+      range of values in the Histogram.
+    nbins: `int`. Number of bins.
+  Returns:
+    l1norm: `tf.Tensor` containing the l1 norm statistic.
+  """
+  with tf.name_scope(name):
+    image = tf.convert_to_tensor(image, dtype=tf.float32)
+
+    # Compute the wavelet normalization factor
+    norm_factors = _get_wavelet_normalization(image, nscales)
+
+    # Compute wavelet transform
+    wt = starlet2d(image, nscales)
+    results = []
+    # Loop over all wavelet scales
+    for coeffs, factor in zip(wt, norm_factors):
+      # Normalizing coefficients to preserve standard deviations
+      # across scales
+      coeffs = coeffs / factor
+
+      # Histogram the coefficient values
+      bins = tf.histogram_fixed_width_bins(coeffs,
+                                           value_range,
+                                           nbins=nbins,
+                                           dtype=tf.int32)
+      # Compute l1 norm in each bin
+      l1norm = [tf.reduce_sum(tf.math.abs(tf.where(bins == i, coeffs, 0)))
+                for i in range(nbins)]
+      results.append(tf.stack(l1norm))
+    return results

### 2021-03-09 DifferentiableHOS/transforms.py

@@ -31,7 +31,7 @@ def starlet2d(image, nscales=4, name="starlet2d"):
 
     for i in range(nscales):
       c_i = tf.nn.atrous_conv2d(approx, W, 2**i, padding="VALID")
-      _, h, w, c = tf.shape(c_i)
+      _, h, w, c = c_i.get_shape()
       coeffs.append(tf.image.resize_with_crop_or_pad(approx, h, w) - c_i)
       approx = c_i
     coeffs.append(approx)

### 2021-03-09 DifferentiableHOS/statistics/l1norm.py
Fix batching l1norm

@@ -51,7 +51,8 @@ def l1norm(image, nscales=3, value_range=[-1., 1.], nbins=16, name='l1norm'):
                                            nbins=nbins,
                                            dtype=tf.int32)
       # Compute l1 norm in each bin
-      l1norm = [tf.reduce_sum(tf.math.abs(tf.where(bins == i, coeffs, 0)))
+      l1norm = [tf.reduce_sum(tf.math.abs(tf.where(bins == i, coeffs, 0)),
+                              axis=[1, 2, 3])
                 for i in range(nbins)]
-      results.append(tf.stack(l1norm))
+      results.append(tf.stack(l1norm, axis=-1))
     return results

### 2021-03-09 paper/paper.tex
change short title
Added a new section

@@
 % header settings
-\shorttitle{Tomographic binning optimization}
-\shortauthors{Author A et al.\ (LSST~DESC)}
+\shorttitle{Differentiable Lensing Simulations}
+\shortauthors{Lanzieri et al.\ (LSST~DESC)}
 
@@
 
+\section{FlowPM}
+
 \section{Ray-tracing}
+In this section, we provide a brief overview of the lensing convergence and the basic concepts of cosmic shear.
+Weak gravitational lensing is a promising observational technique to infer the projected matter density distribution between an observer and a source by measuring galaxy shape correlations.
+
+In a homogeneous FLRW Universe, the geodesic equation of Light ray trajectories induced by the density fluctuations are expressed as :
+\begin{equation}\label{geod}
+    \frac{d^2\textbf{x}_{\bot}(\chi)}{d\chi^2}
+    = -2 \nabla_{\bot} \Phi(\textbf{x}_{\bot},\chi).
+\end{equation}
+If we integrate Eq.\ref{geod} over the line of sight along $\chi'$ the solution $\textbf{x}_{\bot}$ for the radial comoving distance becomes:
+\begin{equation}
+    \textbf{x}(\chi)=f_k(\chi)\boldsymbol{\theta}-\frac{2}{c^2} 
+    \int_0^{\chi} d\chi'f_k(\chi-\chi')[\boldsymbol{\nabla}_{\bot}\Phi(\textbf{x},\chi')-\boldsymbol{\nabla}_{\bot}\Phi^{(0)}(\chi')]
+\end{equation}
+ where we indicate as $f_k(\chi)$ and $\chi$ the angular and radial comoving distance, respectively.
+ In the absence of lensing the observer would see the distance \textbf{x} under an angle $\boldsymbol{\beta}$$=\textbf{x}(\chi)/f_k(\chi)$.
+
+ In the presence of lensing the separation vector \textbf{x} will be seen under an angle $\boldsymbol{\alpha}$, defining as:
+ \begin{equation}
+     \boldsymbol{\alpha}=\frac{2}{c^2} \int_0^{\chi} d\chi'
+     \frac{f_k(\chi-\chi')}{f_k(\chi)}
+     [\boldsymbol{\nabla}_{\bot}\Phi(\textbf{x},\chi')-\boldsymbol{\nabla}_{\bot}\Phi^{(0)}(\chi')].
+ \end{equation}
+ So that, the difference between the apparent angle $\theta$ and the source position $\beta$ defines the lens equation:
+ \begin{equation}
+ \boldsymbol{\alpha=\theta - \beta}.
+ \end{equation}
+In the next section we will infer the lensing potential  $\Phi$ by solving the Poisson equation from the three dimensional density contrast $\delta$:
+\begin{equation}\label{Poisson}
+    \nabla_{\bot}^2 \Phi(x_{\bot},\chi)=
+    \frac{3H_0^2 \Omega_m}{2c^2a(\chi)}
+    \delta(x_{\bot},\chi)
+\end{equation}
+where we indicate as $a$ the scale factor, and  as $\Omega_m$ and $H_0$ the matter density and the Hubble parameter, respectively.
+
+\subsection{The Born approximation}
+
+In this work we implement the Born approximation, integrating the potential gradient along the unperturbed ray.
+If we consider the series expansion in powers of $\Phi$, assuming that the $\Phi$ is small and considering just the first-order approximation, the gravitational potential  can be written as:
+\begin{equation}
+    \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
+\end{equation}
+We can now define the Jacobian matrix \textbf{A}$=\partial\boldsymbol{\beta}/\partial\boldsymbol{\theta}$, describing the linear mapping from the lensed image to the unlensed source:
+\begin{align}
+    A_{ij}=& \frac{\partial\beta_i}{\partial\theta_j}=
+    \delta_{ij}-\frac{\partial\alpha_i}{\partial\theta_j} \\
+     & =\delta_{ij}-\frac{2}{c^2}
+    \int_0^{\chi} d\chi'
+     \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)}
+     \frac{\partial^2}{\partial x_i \partial x_j} \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
+\end{align}
+From the parametrization of the symmetrical matrix \textbf{A}, we can define the spin-two shear $\gamma=(\gamma_1,\gamma_2)$ and the scalar convergence field, $\kappa$. 
+Considering this definition the convergence and the shear are defined as second derivative of the potential:
+\begin{equation}\label{kshear}
+    \kappa=\frac{1}{2}(\partial_1\partial_1+\partial_2\partial_2)\psi; \ \gamma_1=\frac{1}{2}(\partial_1\partial_1-\partial_2\partial_2)\psi; \ 
+    \gamma_2=\partial_1\partial_2\psi;
+\end{equation}
+where we define the 2D \textit{lensing potential} $\psi$,
+\begin{equation}
+    \psi(\boldsymbol{\theta},\chi)=
+    -\frac{2}{c^2}
+    \int_0^{\chi} d\chi'
+     \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)}
+    \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
+\end{equation}
+The two fields $\gamma$ and $\kappa$ describe the distortion in the shape of the image, and the change in the angular size, respectively.
+Considering the Eq.\ref{Poisson} and the Eq.\ref{kshear} the convergence $\kappa$ becomes:
+\begin{equation}
+    \kappa_{born}(\boldsymbol{\theta},\chi_s)= \frac{3H_0^2 \Omega_m}{2c^2}
+    \int_0^{\chi_s} 
+    \frac{d\chi'}{a(\chi')}
+     \frac{f_k(\chi-\chi')}{f_k(\chi)}
+     f_k(\chi')
+    \delta(f_k(\chi')\boldsymbol{\theta},\chi').
+\end{equation}
+
+%\begin{equation}
+%where $n(\chi)$ is a redshift independent factor of normalization from Poisson equation.
+ %   n(\chi)=(AB)(\chi^2)
+%\end{equation}
+%where $A$ is the two dimensional mesh area in $rad^2$ per pixel and $B$ is the mean 3 dimensional particle density in the all cube.
 

### 2021-03-09 DifferentiableHOS/statistics/__init__.py
removes l1norm for now

@@ -1,2 +1,1 @@
 from .angular_power_tf import measure_power_spectrum_tf as power_spectrum
-from .l1norm import l1norm

### 2021-03-09 DifferentiableHOS/statistics/l1norm.py

@@ -1,58 +1,0 @@
-# This module implements the l1 norm statistic described in
-# Ajani et al. 2021 https://arxiv.org/abs/2101.01542
-import tensorflow as tf
-import numpy as np
-from DifferentiableHOS.transforms import starlet2d
-
-__all__ = ['l1norm']
-
-
-def _get_wavelet_normalization(image, nscales):
-  """ Computes normalizing constant for starlet, for given image.
-  """
-  _, nx, ny = image.get_shape()
-  knorm = tf.ones((1, 1, 1, 1), dtype=tf.float32)
-  knorm = tf.image.resize_with_crop_or_pad(knorm, nx, ny)
-  wt = starlet2d(knorm[..., 0], nscales=nscales)
-  return [tf.math.sqrt(tf.reduce_sum(c**2)) for c in wt]
-
-
-def l1norm(image, nscales=3, value_range=[-1., 1.], nbins=16, name='l1norm'):
-  """ Computes the starlet l1-norm statistic on the input image.
-
-  Args:
-    image: `tf.Tensor` reprensenting the input image to process.
-    nscales: `int` representing the number of wavelet scales to include
-      in the decomposition.
-    value_range: Shape [2] Tensor of same dtype as image, determines the
-      range of values in the Histogram.
-    nbins: `int`. Number of bins.
-  Returns:
-    l1norm: `tf.Tensor` containing the l1 norm statistic.
-  """
-  with tf.name_scope(name):
-    image = tf.convert_to_tensor(image, dtype=tf.float32)
-
-    # Compute the wavelet normalization factor
-    norm_factors = _get_wavelet_normalization(image, nscales)
-
-    # Compute wavelet transform
-    wt = starlet2d(image, nscales)
-    results = []
-    # Loop over all wavelet scales
-    for coeffs, factor in zip(wt, norm_factors):
-      # Normalizing coefficients to preserve standard deviations
-      # across scales
-      coeffs = coeffs / factor
-
-      # Histogram the coefficient values
-      bins = tf.histogram_fixed_width_bins(coeffs,
-                                           value_range,
-                                           nbins=nbins,
-                                           dtype=tf.int32)
-      # Compute l1 norm in each bin
-      l1norm = [tf.reduce_sum(tf.math.abs(tf.where(bins == i, coeffs, 0)),
-                              axis=[1, 2, 3])
-                for i in range(nbins)]
-      results.append(tf.stack(l1norm, axis=-1))
-    return results

### 2021-04-19 paper/paper.tex
description of light cone and ray tracing

@@
 
-In this work we implement the Born approximation, integrating the potential gradient along the unperturbed ray.
+We know that the knowledge of the lensing potential and the use of accurate solvers for light ray trajectories could be computationally expensive.
+For this reason, in this work we implement the Born approximation, integrating the potential gradient along the unperturbed ray.
 If we consider the series expansion in powers of $\Phi$, assuming that the $\Phi$ is small and considering just the first-order approximation, the gravitational potential  can be written as:
@@
 
+Our weak lensing simulation tool is based on FlowPM (/cite Modi, Lanusse et al.
+), a fast particle-mesh solver that implements the time integration for gravitational evolution starting from the Gaussian initial conditions of the Universe to the observed large scale structures through a Kick-Drift scheme.
+
+After instantiating the $\Lambda$CDM cosmology with our desired parameters, (the initial power spectrum and the evolution of the particles depend from $\sigma_8$ and $\Omega_{c}$) we created the initial condition for the N-body simulation using the normalised linear matter power spectrum as implemented by (/cite Eisenstein and Hu of '98 ) and generated the linear field at requested scale.
+After that, we implemented the N-body.
+As said before, The N-body simulation does the time integration of a given initial linear field  across a given array of scale factors implementing a series of Kick-Drift-Kick operations.
+During the \textit{Kick} operation we estimate the gravitational force experienced by every particles implementing Fast Fourier Transform and update their momentum.
+In the next state, \textit{Drift}, the particles are displaced and their positions is updated with the velocity estimated in the previous step.
+This operation is continued until the observed large scale structures at the final time-step.
+To perform the lightcone computation and extract the lens planes,  we export several intermediate state from the N-body simulation.
+From a given intermediate state we extract a slice and project it as a density plane by painting the particles on a 2D mesh.
+After creating a grid of coordinates, the lens planes are interpolated onto sky coordinates. 
+ At this point, we have constructed a ray tracer object, to compute the convergence, we directly integrate the lensing density along the unperturbed line of sight.
+
 \section{Results}

### 2021-09-10 scripts/compute_jacobian.py
new lensplane resolution

@@ -14,9 +14,12 @@ from itertools import cycle
 import tensorflow_addons as tfa
 import time
 from flowpm import tfpm
+import tensorflow_probability as tfp
+from scipy.stats import norm
 
-flags.DEFINE_string("filename", "jac_ps_.pkl", "Output filename")
-flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl", "PGD parameter files")
+flags.DEFINE_string("filename", "jac_ps__halo.pkl", "Output filename")
+flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
+                    "PGD parameter files")
 flags.DEFINE_float("Omega_c", 0.2589, "Fiducial CDM fraction")
 flags.DEFINE_float("sigma8", 0.8159, "Fiducial sigma_8 value")
 flags.DEFINE_integer("nc", 128,
@@ -33,82 +36,109 @@ flags.DEFINE_integer("batch_size", 1,
 FLAGS = flags.FLAGS
 
 
+def make_power_map(power_spectrum, size, kps=None):
+    #Ok we need to make a map of the power spectrum in Fourier space
+    k1 = np.fft.fftfreq(size)
+    k2 = np.fft.fftfreq(size)
+    kcoords = np.meshgrid(k1, k2)
+    # Now we can compute the k vector
+    k = np.sqrt(kcoords[0]**2 + kcoords[1]**2)
+    if kps is None:
+        kps = np.linspace(0, 0.5, len(power_spectrum))
+    # And we can interpolate the PS at these positions
+    ps_map = np.interp(k.flatten(), kps, power_spectrum).reshape([size, size])
+    ps_map = ps_map
+    return ps_map
+
+
+def fourier_smoothing(kappa, sigma, resolution):
+    im = tf.signal.fft2d(tf.cast(kappa, tf.complex64))
+    kps = np.linspace(0, 0.5, resolution)
+    filter = norm(0, 1. / (2. * np.pi * sigma)).pdf(kps)
+    m = make_power_map(filter, resolution, kps=kps)
+    m /= m[0, 0]
+    im = tf.cast(tf.reshape(m, [1, resolution, resolution]), tf.complex64) * im
+    return tf.cast(tf.signal.ifft2d(im), tf.float32)
+
+
 @tf.function
 def compute_kappa(Omega_c, sigma8, pgdparams):
-  """ Computes a convergence map using ray-tracing through an N-body for a given
[…]

### 2021-09-10 scripts/compute_maps.py

@@ -27,108 +27,113 @@ flags.DEFINE_float("box_size", 205.,
                    "Transverse comoving size of the simulation volume")
 flags.DEFINE_float("field_size", 5., "TSize of the lensing field in degrees")
 flags.DEFINE_integer("n_lens", 11, "Number of lensplanes in the lightcone")
-flags.DEFINE_integer("batch_size", 1, "Number of simulations to run in parallel")
+flags.DEFINE_integer("batch_size", 1,
+                     "Number of simulations to run in parallel")
 flags.DEFINE_integer("nmaps", 10, "Number maps to generate.")
 
 FLAGS = flags.FLAGS
 
+
 @tf.function
 def compute_kappa(Omega_c, sigma8, pgdparams):
-  """ Computes a convergence map using ray-tracing through an N-body for a given
+    """ Computes a convergence map using ray-tracing through an N-body for a given
     set of cosmological parameters
     """
-  # Instantiates a cosmology with desired parameters
-  cosmology = flowpm.cosmology.Planck15(Omega_c=Omega_c, sigma8=sigma8)
+    # Instantiates a cosmology with desired parameters
+    cosmology = flowpm.cosmology.Planck15(Omega_c=Omega_c, sigma8=sigma8)
 
-  # Schedule the center of the lensplanes we want for ray tracing
-  r = tf.linspace(0., FLAGS.box_size * FLAGS.n_lens, FLAGS.n_lens + 1)
-  r_center = 0.5 * (r[1:] + r[:-1])
+    # Schedule the center of the lensplanes we want for ray tracing
+    r = tf.linspace(0., FLAGS.box_size * FLAGS.n_lens, FLAGS.n_lens + 1)
+    r_center = 0.5 * (r[1:] + r[:-1])
 
-  # Retrieve the scale factor corresponding to these distances
-  a = flowpm.tfbackground.a_of_chi(cosmology, r)
-  a_center = flowpm.tfbackground.a_of_chi(cosmology, r_center)
+    # Retrieve the scale factor corresponding to these distances
+    a = flowpm.tfbackground.a_of_chi(cosmology, r)
+    a_center = flowpm.tfbackground.a_of_chi(cosmology, r_center)
 
-  # We run 4 steps from initial scale factor to start of raytracing
-  init_stages = tf.linspace(0.1, a[-1], 4)
-  # Then one step per lens plane
-  stages = tf.concat([init_stages, a_center[::-1]], axis=0)
[…]

### 2021-09-10 scripts/fit_online_pgd.py

@@ -20,7 +20,8 @@ flags.DEFINE_string("filename", "results_fit_PGD.pkl", "Output filename")
 flags.DEFINE_integer("niter", 51, "Number of iterations of the first PGD fit")
 flags.DEFINE_integer("niter_refine", 21,
                      "Number of iterations of subsequent PGD fit")
-flags.DEFINE_float("learning_rate", 0.1, "ADAM learning rate for the PGD optim")
+flags.DEFINE_float("learning_rate", 0.1,
+                   "ADAM learning rate for the PGD optim")
 flags.DEFINE_integer("batch_size", 2, "Number of random draws")
 
 flags.DEFINE_float("alpha0", 0.1, "Initial guess for alpha at z=0")
@@ -41,39 +42,41 @@ FLAGS = flags.FLAGS
 
 
 def pgd_loss(pgdparams, state, target_pk, return_pk=False):
-  """
+    """
   Defines the loss function for the PGD parameters
   """
-  shape = state.get_shape()
-  batch_size = shape[1]
+    shape = state.get_shape()
+    batch_size = shape[1]
 
-  # Step I: Apply PGD to the state vector
-  pdgized_state = tfpm.pgd(
-      state, pgdparams, nc=[FLAGS.nc] * 3, pm_nc_factor=FLAGS.B)
+    # Step I: Apply PGD to the state vector
+    pdgized_state = tfpm.pgd(state,
+                             pgdparams,
+                             nc=[FLAGS.nc] * 3,
+                             pm_nc_factor=FLAGS.B)
 
-  # Step II: Painting and compensating for cic window
-  field = cic_paint(tf.zeros([batch_size] + [FLAGS.nc] * 3), pdgized_state[0])
-  field = compensate_cic(field)
+    # Step II: Painting and compensating for cic window
+    field = cic_paint(tf.zeros([batch_size] + [FLAGS.nc] * 3),
+                      pdgized_state[0])
+    field = compensate_cic(field)
 
-  # Step III: Compute power spectrum
-  k, pk = flowpm.power_spectrum(
-      field,
-      boxsize=np.array([FLAGS.box_size] * 3),
-      kmin=np.pi / FLAGS.box_size,
-      dk=2 * np.pi / FLAGS.box_size)
-  # Averaging pk over realisations
-  pk = tf.reduce_mean(pk, axis=0)
+    # Step III: Compute power spectrum
+    k, pk = flowpm.power_spectrum(field,
[…]

### 2021-09-11 DifferentiableHOS/statistics/peak_counts_tf.py
Adds differentiable peak counts

@@ -1,7 +1,7 @@
 """
 Created on Fri Feb 12 12:54:33 2021
 
-@author: Ben Horowitz
+@author: Ben Horowitz (and friends)
 
 From lenspack implementation
 """
@@ -64,9 +64,57 @@ def find_peaks2d_tf(image,mask = None, ordered=True,threshold=None):
         return tf.gather(XY[:,0],ind),tf.gather(XY[:,1],ind),tf.gather(heights,ind)
     return XY[:,0], XY[:,1],heights
 
+
 @tf.function
-def peaks_histogram_tf(image, bins=None, mask=None):
+def peaks_histogram_tf(image, bins=None, mask=None, bw_factor=2.):
     """Compute a histogram of peaks in a 2d image.
+
+    Parameters
+    ----------
+    image : tensor (2D)
+        Two-dimensional input tensor
+    bins : int or tensor (1D), optional
+        Specification of centers or the number of bins to use for the
+        histogram. If not provided, a default of 10 bins linearly spaced
+        between the image minimum and maximum (inclusive) is used.
+    mask : tensor (same shape as `image`), optional
+        Tensor identifying which pixels of `image` to consider/exclude
+        in finding peaks. Can either either be numeric (0 or 1) or boolean 
+        (false or true)
+    bw_factor: float
+        Factor by which to divide the bin width to define the bandwidth of the
+        smoothing kernel.
+    Returns
+    -------
+    counts, bins : tuple of 1D tensors
+        Histogram and bin boundary values. If the returned `counts` has 
+        N values, `bin_edges` will have N + 1 values.
+     """
+    if bins is None:
+        bins = tf.linspace(tf.math.reduce_min(image), tf.math.reduce_max(image), 10)
+    elif isinstance(bins, int):
+        bins = tf.linspace(tf.math.reduce_min(image), tf.math.reduce_max(image), bins)
+    else:
+        bins = bins
+
+    x, y, heights = find_peaks2d_tf(image, threshold=None, mask=mask)
+
+    # To avoid issues, we clip the image to within the peaks
+    heights = tf.clip_by_value(heights, bins[0], bins[-1])
+
+    w = tf.reshape(tf.ones_like(heights), [-1])
+    k = _kernel(tf.reduce_mean((bins[1:] -  bins[:-1]))/bw_factor, tf.reshape(heights,[-1,1]), bins)
[…]

### 2021-09-11 paper/paper.tex

@@
 
+\section{Additional validation for our ray-tracing implementation } 
+As an additional test to validate our ray-tracing, instead of running the N-body simulation to generate the snapshots of particles for different scale factors, we create these snapshots by using a linear matter power spectrum at a given fixed redshift $z=0.52$ .
+\\
+Specifically, we estimate the initial LPT displacement given an input linear (real) field.
+
+As we said, the aim of this test is to prove the validity of our ray-tracing.
+In principle, without the N-body simulations and his possible approximations and systematics, any disagreement between the angular power spectrum computed from the final convergence map
+and the angular power spectrum we use as reference can be attributable to the ray-tracing.
+
+Fig.
+shows a comparison between the theoretical linear matter power spectrum computed using the Jax-cosmo library at the redshift $0.52$ and the matter power spectrum computed from the resulting snapshots, after applying the painting operations.
+As we can see the matter power spectrum start to lack in power for $k$(maggiore o circa uguale)1.
+This is probably due to the paint operation and is something to take into account when we will study the final power spectrum.
+
+Then, we exported the lens planes, created the Convergence map and computed the angular power spectrum from it. The final angular power spectrum is obtained averaging over 20 samples.
+We also tried to investigate the behaviour of the angular power spectrum for large scale for different values of the field and Box size.
+
+\section{Potential Gradient Descendent (PGD)}    
+Fast N-body simulations can be used as viable alternative to full N-body to model the galaxy statistics and create fast and low computational costs realizations of the large scale structure.
+Nevertheless, this kind of simulations lack resolution on small scale and can't give accurate halo matter profiles or matter power spectrum.
+
+To recover this missing accuracy, we employs the PGD scheme (\citet{Dai_2018}). 
+The main goal is to mimic the physics lost in the low resolution simulations by computing the short range force operation as an additional correction displacements in a post-processing step. \\
+The additional displacement is computed by pointing the particles towards a filtered potential minimum of the particle mesh solver:
+\begin{equation}
+    \textbf{S}=4\pi G \bar{\rho}\alpha_{PM}/H_0^2 \nabla(
+   \hat{\textbf{O}}_l(k)
+     \hat{\textbf{O}}_s(k)
+    \nabla^{-2}\delta),
+\end{equation}
+where $\hat{\textbf{O}}_l(k)= \exp{(\frac{k^2}{k^4_l})}$ and $\hat{\textbf{O}}_s(k)= \exp{(-\frac{k^4}{k^4_s}})$ are the low and high pass filter introduced to remove the long range force and to reduce the numerical effect induced by the mesh resolution.
+\\
+As we can see, PGD introduces control parameters ($k_s$,$k_l$,$\alpha$) that can be tuned comparing high and low resolution simulations.
+Specifically, $\alpha$ is scale factor dependent according the following relation: $\alpha=\alpha_0a^{\mu}$, where $\alpha_0$ and $\mu$ are two free parameters that can be varied to match the power spectrum against the higher resolution N-body simulations.
+
+We see from the Figure that, at fixed $k_l,k_s,\mu$, increasing $\alpha_0$ the power spectrum increases at small scale.
+For $\alpha_0$ between 0.008 and 0.01 the power spectrum reaches the maximum power.
+For lower values the power spectrum starts to decrease at small scale.
+
+Fig.
+shows that the PGD scheme allows to achieve higher accuracy at the same computational cost.
+We compare the low resolution DLL matter power spectra (128 particles, 128 $Mpc/h$, $B=2$) complemented by the PGD scheme to a conventional DLL simulation with the same resolution.
+Both the outputs are computed using $\alpha_0=0.01$ and showed for different redshift.
+
+\section{Summary statistics}
+
+\subsection{Lensing Angular Power Spectrum}
+
+\subsection{Wavelet Peak Counts}
+
+\FL{Explain wavelets}
+
+One of the difficulties with traditional peak counting is that it relies on building
+an histogram of peak intensities, and histograms, due to the discrete nature of the bins, are not differentiable.
+However, the underlying idea of peak counting is just to build an estimate of the density distribution of number of peaks as a function of their intensity.
+Histograms are one way to build such an estimate, and have been historically preferred, but for no particular reason.
+To circumvent the non-differentiability of histograms, we prefer here to estimate this density using an alternative method: Kernel Density Estimation (KDE).
+As a continuous equivalent to an histogram, KDEs are differentiables and can just as well be used to define the peak counts statistic.
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/}
+    \caption{Caption}
+    \label{fig:my_label}
+\end{figure}
+
 \section{Results}

### 2021-09-13 scripts/compute_jacobian_l1norm.py
Flags correction

@@ -27,12 +27,13 @@ flags.DEFINE_float("field_size", 5., "TSize of the lensing field in degrees")
 flags.DEFINE_float("a_init", 0.1, "Initial scale factor")
 flags.DEFINE_integer("init_nsteps", 4, "Number of steps before the lightcone")
 flags.DEFINE_integer("n_lens", 36, "Number of lensplanes in the lightcone")
-flags.DEFIN_integer("batch_size", 1, "Number of simulations to run in parallel")
+flags.DEFIN_integer("batch_size", 1,
+                    "Number of simulations to run in parallel")
 flags.DEFINE_integer("nmaps", 20, "Number maps to generate.")
 flags.DEFINE_integer("B", 1, "Scale resolution factor")
 
-
 FLAGS = flags.FLAGS
+
 
 @tf.function
 def compute_kappa(Omega_c, sigma8):
@@ -66,10 +67,10 @@ def compute_kappa(Omega_c, sigma8):
         [FLAGS.nc, FLAGS.nc, FLAGS.nc],
         [FLAGS.box_size, FLAGS.box_size, FLAGS.box_size],
         pk_fun,
-        batch_size=FLAGS.batch_size))
+        batch_size=FLAGS.batch_size)
     initial_state = flowpm.lpt_init(cosmology, initial_conditions, 0.1)
 
-        # Run the Nbody
+    # Run the Nbody
     states = flowpm.nbody(cosmology,
                           initial_state,
                           stages, [FLAGS.nc, FLAGS.nc, FLAGS.nc],
@@ -119,7 +120,8 @@ def compute_kappa(Omega_c, sigma8):
                                           coords=c,
                                           z_source=z_source)
 
-    m = tf.reshape(m, [FLAGS.batch_size, FLAGS.field_npix, FLAGS.field_npix,-1])
+    m = tf.reshape(m,
+                   [FLAGS.batch_size, FLAGS.field_npix, FLAGS.field_npix, -1])
 
     return m, lensplanes, r_center, a_center
 

### 2021-09-13 scripts/compute_jacobian_ps.py

@@ -14,29 +14,55 @@ from itertools import cycle
 import tensorflow_addons as tfa
 from flowpm import tfpm
 import time
+from scipy.stats import norm
 
 flags.DEFINE_string("filename", "jac_1_20.pkl", "Output filename")
+flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
+                    "PGD parameter files")
 flags.DEFINE_float("Omega_c", 0.2589, "Fiducial CDM fraction")
 flags.DEFINE_float("sigma8", 0.8159, "Fiducial sigma_8 value")
-flags.DEFINE_integer("nc", 64,
+flags.DEFINE_integer("nc", 128,
                      "Number of transverse voxels in the simulation volume")
 flags.DEFINE_integer("field_npix", 1024,
                      "Number of pixels in the lensing field")
-flags.DEFINE_float("box_size", 64.,
+flags.DEFINE_float("box_size", 205.,
                    "Transverse comoving size of the simulation volume")
 flags.DEFINE_float("field_size", 5., "TSize of the lensing field in degrees")
-flags.DEFINE_float("a_init", 0.1, "Initial scale factor")
-flags.DEFINE_integer("init_nsteps", 4, "Number of steps before the lightcone")
-flags.DEFINE_integer("n_lens", 36, "Number of lensplanes in the lightcone")
-flags.DEFINE_float("batch_size", 1, "Number of simulations to run in parallel")
+flags.DEFINE_integer("n_lens", 11, "Number of lensplanes in the lightcone")
+flags.DEFINE_integer("batch_size", 1,
+                     "Number of simulations to run in parallel")
 flags.DEFINE_integer("nmaps", 20, "Number maps to generate.")
-flags.DEFINE_integer("B", 1, "Scale resolution factor")
 
 FLAGS = flags.FLAGS
 
 
+def make_power_map(power_spectrum, size, kps=None):
+    #Ok we need to make a map of the power spectrum in Fourier space
+    k1 = np.fft.fftfreq(size)
+    k2 = np.fft.fftfreq(size)
+    kcoords = np.meshgrid(k1, k2)
+    # Now we can compute the k vector
+    k = np.sqrt(kcoords[0]**2 + kcoords[1]**2)
+    if kps is None:
+        kps = np.linspace(0, 0.5, len(power_spectrum))
+    # And we can interpolate the PS at these positions
+    ps_map = np.interp(k.flatten(), kps, power_spectrum).reshape([size, size])
+    ps_map = ps_map
[…]

### 2021-09-13 scripts/compute_maps.py

@@ -14,9 +14,11 @@ from itertools import cycle
 import tensorflow_addons as tfa
 import time
 from flowpm import tfpm
+from scipy.stats import norm
 
 flags.DEFINE_string("filename", "results_maps.pkl", "Output filename")
-flags.DEFINE_string("pgd_params", "results_fit_PGD.pkl", "PGD parameter files")
+flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
+                    "PGD parameter files")
 flags.DEFINE_float("Omega_c", 0.2589, "Fiducial CDM fraction")
 flags.DEFINE_float("sigma8", 0.8159, "Fiducial sigma_8 value")
 flags.DEFINE_integer("nc", 128,
@@ -32,6 +34,31 @@ flags.DEFINE_integer("batch_size", 1,
 flags.DEFINE_integer("nmaps", 10, "Number maps to generate.")
 
 FLAGS = flags.FLAGS
+
+
+def make_power_map(power_spectrum, size, kps=None):
+    #Ok we need to make a map of the power spectrum in Fourier space
+    k1 = np.fft.fftfreq(size)
+    k2 = np.fft.fftfreq(size)
+    kcoords = np.meshgrid(k1, k2)
+    # Now we can compute the k vector
+    k = np.sqrt(kcoords[0]**2 + kcoords[1]**2)
+    if kps is None:
+        kps = np.linspace(0, 0.5, len(power_spectrum))
+    # And we can interpolate the PS at these positions
+    ps_map = np.interp(k.flatten(), kps, power_spectrum).reshape([size, size])
+    ps_map = ps_map
+    return ps_map
+
+
+def fourier_smoothing(kappa, sigma, resolution):
+    im = tf.signal.fft2d(tf.cast(kappa, tf.complex64))
+    kps = np.linspace(0, 0.5, resolution)
+    filter = norm(0, 1. / (2. * np.pi * sigma)).pdf(kps)
+    m = make_power_map(filter, resolution, kps=kps)
+    m /= m[0, 0]
+    im = tf.cast(tf.reshape(m, [1, resolution, resolution]), tf.complex64) * im
+    return tf.cast(tf.signal.ifft2d(im), tf.float32)
 
 
 @tf.function

### 2021-09-13 scripts/job_jac_ps.sh

@@ -6,9 +6,10 @@
 #SBATCH -t 02:00:00
 #SBATCH --mail-user=denise.lanzieri@cea.fr
 
+conda deactivate
 module load python3/3.8-anaconda-2020.11
 
-cd /global/cscratch1/sd/dlan/jacobian_ps
+cd /global/cscratch1/sd/dlan/jacobian_ps/
 
 
 python /global/homes/d/dlan/DifferentiableHOS/scripts/compute_jacobian_ps.py  --filename=res_ps_$SLURM_ARRAY_TASK_ID

### 2021-09-13 scripts/job_maps.sh

@@ -9,6 +9,6 @@
 conda deactivate
 module load python3/3.8-anaconda-2020.11
 
-cd /global/cscratch1/sd/dlan/maps_64
+cd /global/cscratch1/sd/dlan/maps/
 
 python /global/homes/d/dlan/DifferentiableHOS/scripts/compute_maps.py  --filename=res_maps_$SLURM_ARRAY_TASK_ID

### 2021-09-13 scripts/compute_maps.py
new notebook

@@ -141,6 +141,23 @@ def compute_kappa(Omega_c, sigma8, pgdparams):
     return m, lensplanes, r_center, a_center
 
 
+def desc_y1_analysis(kmap):
+    """
+  Adds noise and apply smoothing we might expect in DESC Y1 SRD setting
+  """
+    ngal = 10  # gal/arcmin **2
+    pix_scale = FLAGS.field_size / FLAGS.field_npix * 60  # arcmin
+    ngal_per_pix = ngal * pix_scale**2  # galaxies per pixels
+    sigma_e = 0.26 / np.sqrt(2 * ngal_per_pix)  # Rescaled noise sigma
+    sigma_pix = 1. / pix_scale  # Smooth at 1 arcmin
+    # Add noise
+    kmap = kmap + sigma_e * tf.random.normal(kmap.shape)
+    # Add smoothing
+    kmap = fourier_smoothing(kmap,
+                             sigma=sigma_pix,
+                             resolution=FLAGS.field_npix)
+    return kmap
+
 def main(_):
 
     # Loading PGD parameters
@@ -151,13 +168,14 @@ def main(_):
     for i in range(FLAGS.nmaps):
         t = time.time()
 
-        kmap, lensplanes, r_center, a_center = compute_kappa(
+        m, lensplanes, r_center, a_center = compute_kappa(
             tf.convert_to_tensor(FLAGS.Omega_c, dtype=tf.float32),
             tf.convert_to_tensor(FLAGS.sigma8, dtype=tf.float32), pgdparams)
-
+        kmap = desc_y1_analysis(m)
         # Saving results in requested filename
         pickle.dump({
             'kmap': kmap.numpy(),
+            'm': m.numpy(),
         }, open(FLAGS.filename + '_%d' % i, "wb"))
         print("iter", i, "took", time.time() - t)
 

### 2022-02-14 paper/paper.tex
Minor update
Updates from Overleaf

--- 2021-04-19 paper/paper.tex
@@
 \newcommand{\placeholder}[1]{\textit{PLACEHOLDER: #1}}
+
+\newcommand{\EiffL}[1]{{\color{cyan}FL: #1}}
+\newcommand{\denise}[1]{{\color{red}DL: #1}}
 
@@
 
-\section{FlowPM}
+\section{Methods}
 
-\section{Ray-tracing}
-In this section, we provide a brief overview of the lensing convergence and the basic concepts of cosmic shear.
+%We compare the sensitivity of three different map-based statistics: angular power spectra, the peak counts and the $l_{1\text{norm}}$.
+ %the calculation of the summary statistics, and the Fisher Forecast process.
+
+\subsection{{Weak lensing}}
+
 Weak gravitational lensing is a promising observational technique to infer the projected matter density distribution between an observer and a source by measuring galaxy shape correlations. 
+The effect of gravitational lensing 
+can be quantified in term of the separation vector \textbf{x} between a ray and a fiducial ray separated by the angle $\boldsymbol{\theta}$ at the observer:
+\begin{align}\label{sep}
+   & \textbf{x}(\boldsymbol{\theta},\chi) =
+    f_k(\chi)\boldsymbol{\theta} + \\
+   &- \frac{2}{c^2}
+    \int_0^{\chi}
+    \text{d}\chi'
+    f_k(\chi-\chi')
+    [ \boldsymbol{\nabla_{\bot}}\Phi( \textbf{x}(\boldsymbol{\theta},\chi'),\chi')-
+    \boldsymbol{\nabla_{\bot}}\Phi^{(0)}(\chi')
+    ],
+\end{align}
+where we denote as $\Phi$ and $\Phi^{0}$ the potential along the two light rays, and as $f_k(\chi)$ and $\chi$ the angular and radial comoving distance.
 
-In a homogeneous FLRW Universe, the geodesic equation of Light ray trajectories induced by the density fluctuations are expressed as :
-\begin{equation}\label{geod}
-    \frac{d^2\textbf{x}_{\bot}(\chi)}{d\chi^2}
-    = -2 \nabla_{\bot} \Phi(\textbf{x}_{\bot},\chi).
+The Jacobian matrix, describing the linearized lens mapping, is defined as:
+\begin{equation}
+\mathcal{A}(\boldsymbol{\theta},\chi)=
+\frac{1}{f_{k}(\chi)}
+\frac{\partial \textbf{x}}{\partial \boldsymbol{\theta}}.
 \end{equation}
-If we integrate Eq.\ref{geod} over the line of sight along $\chi'$ the solution $\textbf{x}_{\bot}$ for the radial comoving distance becomes:
+We know that the knowledge of the gravitational potential and the use of accurate solvers for light ray trajectories is computationally expensive.
+Nevertheless, the integral equation \ref{sep} can be approximated by considering the series expansion in power of $\Phi$ and truncating the series at the first term.
+With this assumptions, and considering that $\nabla_{\bot}\boldsymbol{\Phi}^0$ does not depend from $\boldsymbol{\theta}$, the Jacobian matrix can be written as:
 \begin{equation}
-    \textbf{x}(\chi)=f_k(\chi)\boldsymbol{\theta}-\frac{2}{c^2} 
-    \int_0^{\chi} d\chi'f_k(\chi-\chi')[\boldsymbol{\nabla}_{\bot}\Phi(\textbf{x},\chi')-\boldsymbol{\nabla}_{\bot}\Phi^{(0)}(\chi')]
+    \mathcal{A}_{ij}(\boldsymbol{\theta},\chi)
+     =\delta_{ij}-\frac{2}{c^2}
+    \int_0^{\chi} d\chi'
+     \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)}
+     \Phi_{ij}(f_k(\chi')\boldsymbol{\theta},\chi').
 \end{equation}
- where we indicate as $f_k(\chi)$ and $\chi$ the angular and radial comoving distance, respectively.
- In the absence of lensing the observer would see the distance \textbf{x} under an angle $\boldsymbol{\beta}$$=\textbf{x}(\chi)/f_k(\chi)$.
+Notice that this approximation, also known as Born approximation, is only valid in the limit of weak-field metric (small $\Phi$).
 
- In the presence of lensing the separation vector \textbf{x} will be seen under an angle $\boldsymbol{\alpha}$, defining as:
+If we define the 2D potential, the \textit{lensing potential} as:
 \begin{equation}
-     \boldsymbol{\alpha}=\frac{2}{c^2} \int_0^{\chi} d\chi'
-     \frac{f_k(\chi-\chi')}{f_k(\chi)}
-     [\boldsymbol{\nabla}_{\bot}\Phi(\textbf{x},\chi')-\boldsymbol{\nabla}_{\bot}\Phi^{(0)}(\chi')].
- \end{equation}
- So that, the difference between the apparent angle $\theta$ and the source position $\beta$ defines the lens equation:
- \begin{equation}
- \boldsymbol{\alpha=\theta - \beta}.
- \end{equation}
-In the next section we will infer the lensing potential  $\Phi$ by solving the Poisson equation from the three dimensional density contrast $\delta$:
-\begin{equation}\label{Poisson}
-    \nabla_{\bot}^2 \Phi(x_{\bot},\chi)=
-    \frac{3H_0^2 \Omega_m}{2c^2a(\chi)}
-    \delta(x_{\bot},\chi)
-\end{equation}
-where we indicate as $a$ the scale factor, and  as $\Omega_m$ and $H_0$ the matter density and the Hubble parameter, respectively.
-
-\subsection{The Born approximation}
-
-We know that the knowledge of the lensing potential and the use of accurate solvers for light ray trajectories could be computationally expensive.
-For this reason, in this work we implement the Born approximation, integrating the potential gradient along the unperturbed ray.
-If we consider the series expansion in powers of $\Phi$, assuming that the $\Phi$ is small and considering just the first-order approximation, the gravitational potential  can be written as:
-\begin{equation}
+    \psi(\boldsymbol{\theta},\chi) \equiv
+ -\frac{2}{c^2}
+= \int_0^{\chi} d\chi'
+   \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)f_k(\chi')}
   \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
 \end{equation}
-We can now define the Jacobian matrix \textbf{A}$=\partial\boldsymbol{\beta}/\partial\boldsymbol{\theta}$, describing the linear mapping from the lensed image to the unlensed source:
-\begin{align}
-    A_{ij}=& \frac{\partial\beta_i}{\partial\theta_j}=
-    \delta_{ij}-\frac{\partial\alpha_i}{\partial\theta_j} \\
-     & =\delta_{ij}-\frac{2}{c^2}
-    \int_0^{\chi} d\chi'
-     \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)}
-     \frac{\partial^2}{\partial x_i \partial x_j} \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
-\end{align}
-From the parametrization of the symmetrical matrix \textbf{A}, we can define the spin-two shear $\gamma=(\gamma_1,\gamma_2)$ and the scalar convergence field, $\kappa$. 
-Considering this definition the convergence and the shear are defined as second derivative of the potential:
+ the Jacobi matrix can be written as:
+\begin{equation}
+    \mathcal{A}_{ij}=\delta_{ij}-\partial_i \partial_j\psi. 
+\end{equation}
+
+From the parametrization of the symmetrical matrix $\mathcal{A}$, we can define the spin-two shear $\gamma=(\gamma_1,\gamma_2)$ and the scalar convergence field, $\kappa$. 
+Hence, the convergence and the shear are defined as second derivative of the potential:
 \begin{equation}\label{kshear}
@@
 \end{equation}
-where we define the 2D \textit{lensing potential} $\psi$,
+
+The two fields $\gamma$ and $\kappa$ describe the distortion in the shape of the image, and the change in the angular size, respectively.
+By combining the 2D Poisson equation with the Eq.\ref{kshear} the convergence $\kappa$ becomes:
 \begin{equation}
-    \psi(\boldsymbol{\theta},\chi)=
-    -\frac{2}{c^2}
-    \int_0^{\chi} d\chi'
-     \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)}
-    \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
+    \kappa_{born}(\boldsymbol{\theta})= \frac{3H_0^2 \Omega_m}{2c^2}
+    \int_0^{\chi_s} 
+    \frac{d\chi}{a(\chi)}
+    g(\chi)
+    \delta(f_k(\chi)\boldsymbol{\theta},\chi),
 \end{equation}
-The two fields $\gamma$ and $\kappa$ describe the distortion in the shape of the image, and the change in the angular size, respectively.
-Considering the Eq.\ref{Poisson} and the Eq.\ref{kshear} the convergence $\kappa$ becomes:
+where we define the \textit{lensing efficiency}
 \begin{equation}
-    \kappa_{born}(\boldsymbol{\theta},\chi_s)= \frac{3H_0^2 \Omega_m}{2c^2}
-    \int_0^{\chi_s} 
-    \frac{d\chi'}{a(\chi')}
-     \frac{f_k(\chi-\chi')}{f_k(\chi)}
-     f_k(\chi')
-    \delta(f_k(\chi')\boldsymbol{\theta},\chi').
+   g(\chi) \equiv
+   \text{d}\chi'
+   n(\chi')
+    \frac{f_k(\chi'-\chi)}{f_k(\chi')}.
 \end{equation}
 
-%\begin{equation}
-%where $n(\chi)$ is a redshift independent factor of normalization from Poisson equation.
- %   n(\chi)=(AB)(\chi^2)
-%\end{equation}
-%where $A$ is the two dimensional mesh area in $rad^2$ per pixel and $B$ is the mean 3 dimensional particle density in the all cube.
+Thus, the Born–approximated convergence can be interpreted as the integrated total matter density along the line of sight, weighted by the distance ratios and the normalised source galaxy  distribution $n(\chi)$d$\chi=n(z)$d$z$.
 
-\section{Methods}
+\subsection{Simulation}
+It's well known that an common feature of statics beyond second-order is the absence of analytical models with which to predict the observed signals.
+Hence, we need to adopt a forward modelling approach and create a suite of numerical simulations.
+In the following section we introduce the mass map simulation procedure, including a description of the simulator and of the construction of the weak lensing lightcone.
 
+\subsubsection{FLOWPM}
 Our weak lensing simulation tool is based on FlowPM (/cite Modi, Lanusse et al.
@@
 
+\subsubsection{Additional validation for our ray-tracing implementation } 
+As an additional test to validate our ray-tracing, instead of running the N-body simulation to generate the snapshots of particles for different scale factors, we create these snapshots by using a linear matter power spectrum at a given fixed redshift $z=0.52$ .
+\\
+Specifically, we estimate the initial LPT displacement given an input linear (real) field.
+
+As we said, the aim of this test is to prove the validity of our ray-tracing.
+In principle, without the N-body simulations and his possible approximations and systematics, any disagreement between the angular power spectrum computed from the final convergence map
+and the angular power spectrum we use as reference can be attributable to the ray-tracing.
+
+Fig.
+shows a comparison between the theoretical linear matter power spectrum computed using the Jax-cosmo library at the redshift $0.52$ and the matter power spectrum computed from the resulting snapshots, after applying the painting operations.
+As we can see the matter power spectrum start to lack in power for $k$(maggiore o circa uguale)1.
+This is probably due to the paint operation and is something to take into account when we will study the final power spectrum.
+
+From the full projected boxes of the simulations, we exported the lens planes, then interpolated on the light-cones.
+
+The final angular power spectrum is obtained averaging over 1000 samples.
+
+\subsubsection{Potential Gradient Descendent (PGD)}    
+Fast N-body simulations can be used as viable alternative to full N-body to model the galaxy statistics and create fast and low computational costs realizations of the large scale structures.
+Nevertheless, this kind of simulations lack resolution on small scale and can't give accurate halo matter profiles or matter power spectrum.
+
+To recover this missing accuracy, we employs the PGD scheme (\cite{Dai_2018}). 
+The main goal is to mimic the physics lost in the low resolution simulations by computing the short range force operation as an additional correction displacements in a post-processing step. \\
+The additional displacement is computed by pointing the particles towards a filtered potential minimum of the particle mesh solver.
+
+%\begin{equation}\label{displacement}
+ %   \textbf{S}=4\pi G \bar{\rho}\alpha_{PM}/H_0^2 \nabla(
+  % \hat{\textbf{O}}_l(k)
+   %  \hat{\textbf{O}}_s(k)
+    %\nabla^{-2}\delta),
+%\end{equation}
+%where $\hat{\textbf{O}}_l(k)= \exp{(\frac{k^2}{k^4_l})}$ and $\hat{\textbf{O}}_s(k)= \exp{(-\frac{k^4}{k^4_s}})$ are the low and high pass filter introduced to remove the long range force and to reduce the numerical effect induced by the mesh resolution.
+\\
+PGD introduces control parameters that can be tuned comparing the matter power spectrum to a reference power spectrum.
+
+We employ an online-PGD technique worth mentioning here: the correction involved in computing additional displacements is computed after every drift step in the N-body simulation.
+
+We find that a PGD correction computed directly at the end of the simulation fails, introducing some significant sharp clusters or changing the shape of some of the structures.
+Effectively this is equivalent to requesting a too large correction at once, which our method avoids.
+
+In practice we set it up so that it takes the power spectra at all intermediate redshift and fits the PGD parameters as to recover the \textit{Halofit} non linear power spectrum.
+
+In Figure \ref{fig:comp_dens_field} , we show the resulting density field when this operation is applied.
+We show a comparison of the density field image for a given redshift when the PGD correction is applied and when not \denise{write better this}.
+We can see that the structures are not modified but simply sharpened.
+\denise{image size and position}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\columnwidth]{paper/figures/densitymap.png}
+%     \caption{Comparison of density planes at same redshift with and without the PGD correction.}
+%     \label{fig:comp_dens_field}
+% \end{figure}
+
+Figure \ref{fig:comp_kmap} shows the same result on the convergence map.
+\denise{image size and position}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/kmap_compgd.png}
+    \caption{Comparison of the final convergence map with and without the PGD correction.}
+    \label{fig:comp_kmap}
+\end{figure}
+
+In Figure \ref{fig:ps_comp} we compare the low resolution DLL convergence power spectrum complemented by the PGD scheme to a conventional DLL simulation with the same resolution.
+Both the outputs are compared to the angular power spectrum obtained from the $\kappa$TNG only dark matter simulation.
+We can conclude that PGD scheme allows to achieve higher accuracy at the same computational cost.
+\denise{image size and position}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/ps_comp.png}
+    \caption{Comparison of the angular power spectrum from the final convergence map with and without the PGD correction against $\kappa-$TNG only Dark-matter simulations.}
+    \label{fig:ps_comp}
+\end{figure}
+
+\subsection{Summary statistics}
+In this work, in order to extract the cosmological information from the simulated $\kappa-$maps, we used tree statistics: the angular power spectrum, the peak counts and the $l_{1\text{norm}}$.
+
+We reproduce the analysis choices of the LSST Y1 data. The DESC science requirements document can be found here \cite{mandelbaum2018lsst}.
+In particular we use a $n_{\text{eff}}=10$ galaxies per $\text{arcmin}^2$ for lensing sources and a $\sigma_e=0.26$ per component.
+
+\subsubsection{Lensing Angular Power Spectrum}
+Second order statistics, both in the form of shear 2-point correlation function $\xi_{\pm}(\theta)$, or its counterpart in Fourier space, the angular power spectrum $C_{\ell}$, have been widely used to extract the cosmological information from weak lensing mass maps.
+\
+In the Limber approximation, the angular power spectrum of the convergence field can be computed as:
+\begin{equation}
+    C_{\kappa}(\ell)=\frac{9\Omega_m^2H_0^4}{4c^4}
+    \int_0^{\chi_{lim}} \text{d}\chi 
+    \frac{g^2(\chi)}{a^2(\chi)}P_{\delta}
+    	\left( k=\frac{\ell}{f_K(\chi)},\chi \right),
+\end{equation}
+where $P_{\delta}$ defines the matter power spectrum of the density contrast.
+In this paper, the angular power spectrum is computed from the noisy smoothed convergence maps: to each mock $\kappa$map we add Gaussian noise and than convolved it with a Gaussian smoothing kernel with a smoothing size $\theta=3.6$.
+We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}.
+For each map, we compute the power spectrum by using our own code implemented in the Tensorflow framework and we take the average over 2000 maps realisation.
+
+\subsubsection{Wavelet Peak Counts}
+It has been shown that it's necessary to go beyond second-order statistics to fully capture the non-Gaussian information encoded in the peak of the matter distribution.
+Several studies have proved that the  weak-lensing peak counts provide a way to capture information from non-linear structures that it is complementary to the information extracted by power spectrum.
+The peak counts identify region of weak lensing map where the density value is higher, in this way they rely to the massive structure.
+There are different ways to record the weak lensing peaks: the number of peaks as a function of either the signal-to-noise ratio or the convergence $\kappa$ of the peaks. 
+In this paper, we choose to bin the peaks as function of $\kappa$. 
+As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code and by averaging over 2000 different realizations.
+A peak is identified as the pixel of larger value than its eight neighbors in the image, convolved with a starlet filter $\mathcal{W}(\theta_{\text{ker}})$:
+\begin{equation}
+    \textbf{Peaks}=(\kappa*\mathcal{W})(\theta_{\text{ker}})
+\end{equation}
+ We consider the peak distribution for 8 linearly spaced bins within the range $\kappa=[-0.05, 0.05]$. The bins are chosen such that at least 30 peaks are recorded in each bin.
+
+\EiffL{Explain wavelets}
+
+One of the difficulties with traditional peak counting is that it relies on building
+an histogram of peak intensities, and histograms, due to the discrete nature of the bins, are not differentiable.
+However, the underlying idea of peak counting is just to build an estimate of the density distribution of number of peaks as a function of their intensity.
+Histograms are one way to build such an estimate, and have been historically preferred, but for no particular reason.
+To circumvent the non-differentiability of histograms, we prefer here to estimate this density using an alternative method: Kernel Density Estimation (KDE).
+As a continuous equivalent to an histogram, KDEs are differentiables and can just as well be used to define the peak counts statistic.
+
+\subsubsection{Wavelet $\ell_1-$norm}
+
+\EiffL{Explain what's the deal with this l1 norm}
+
+\section{Systematic effects}
+Many systematic effects can influence the outcome of cosmic shear analysis and bias cosmic shear results. 
+In this work we incorporate a treatment of the galaxy intrinsic alignment and photometric redshift uncertainty.
+In the following, we introduce an overview of these systematics and outline how we incorporate in our analysis.
+
+\subsection{Photometric redshift uncertainty}
+Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (''photo-z'') measurement are computed.
+In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
+For our analysis we considered a Smail-type galaxy distribution p(z) (Smail et al. 1994),
+\begin{equation}\label{photz}
+    p(z) \propto z^{\alpha} e^{-(\frac{z}{z_0})^{\beta}}
+\end{equation}
+
+ We adopt  $\alpha=$, $\beta =$ and fix $z_0$ such that ?'
+
+ We take into account the uncertainty of the redshift distributions by introducing  a shift of the distributions defined by Eq.\ref{photz} according to the nuisance parameters $\Delta_z$:
+ \begin{equation}
+     n'_i(z)= n_i(z-\Delta_z)
+ \end{equation}
+
+\subsection{Galaxy intrinsic alignment}
+
+The galaxy ellipticity observed by a telescope is the combination of the cosmic shear signal $\gamma$ and the intrinsic shape of the source $\epsilon_{int}$, the latter can be further decomposed into the alignment term $\epsilon_{IA}$ and the random component $\epsilon_{ran}$.
+
+Several theoretical models have been proposed to described the physics of IA, such as the Non-Linear tidal Alignment model (e.g.
+in Bridle et King 2007), the tidal torquing model (described in Hirata et Seljak 2004; Catelan et al.
+2001), or the combination of both (the Tidal Alignment and Tidal Torquing model, see Blazek et al.
+2019).
+
+The NLA model describes the IA as a linear coupling between the intrinsic galaxy shapes and the non-linear large projected tidal fields, the "non-linear" definition arises from the use of the non linear matter power spectrum in the computation.
+
+The IA signal can be decomposed into two components: 1) the intrinsic-intrinsic (II) term, describing the correlation of intrinsic ellipticities of two galaxies $i$ and $j$ and 2) intrinsic-shear coupling (GI) term, describing the correlation between the intrinsic ellipticity of one galaxy with the shear of another galaxy (\cite{kilbinger2015cosmology}).
+
+The first step to introduce the IA term in our simulation, consists in computing the projected tidal field from the three-dimensional mass over-density field $\delta(\vec{x}$
+as (\cite{harnois2021cosmic})
+\begin{equation}
+   \tilde{s}_{ij,2D}(\textbf{k}_{\bot})=
+   2 \pi 	\left [ \frac{k_ik_j}{k^2}- \frac{1}{3} \right ]
+   \tilde{\delta}_{2D}(\textbf{k}_{\bot})
+   \mathcal{G}_{2D}(\sigma_g)
+\end{equation}
+where $\sigma_g$ is the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $~$ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
+In this work we use a Gaussian kernel and set the values of $\sigma_g=(idk yet) h^{-1}$Mpc.
+First of all, we computed the Fourier transform of the projected density field from the full boxes of the simulation. 
+Then the smoothed tidal field is interpolated on the light-cone. 
+Then, we couple the tidal field $s_{ij,2D}$ with the complex intrinsic ellipticities as (\cite{harnois2021cosmic}):
+\begin{equation}
+    \epsilon_{1}^{IA}=\frac{A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} (s_{xx}-s_{yy}), \ \ 
+      \epsilon_{2}^{IA}=-\frac{2A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} s_{xy},
+\end{equation}
+(\denise{check this formula})
+and compute the observed ellipticities as:
+\begin{equation}
+    \boldsymbol{\epsilon}^{obs}=
+    \frac{\boldsymbol{\epsilon}^{int}+\textbf{g}}{1+\boldsymbol{\epsilon}^{int,*}\textbf{g}}, \ \  \text{with}  \ \
+    \boldsymbol{\epsilon}^{int}=
+    \frac{\boldsymbol{\epsilon}^{
+     IA}+\boldsymbol{\epsilon^{ran}}}
+     {1+\boldsymbol{\epsilon}^{IA,*}\boldsymbol{\epsilon^{ran}}}.
+\end{equation}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/peakcounts.png}
+    \caption{Comparison of traditional histogram-based peak counts, against our  KDE-based peak counts statistic. The two statistics are similar, but our KDE-based statistics is differentiable.}
+    \label{fig:comp_statistics}
+\end{figure}
+
+\section{Fisher Forecast}
+Fisher forecast is a widely used tool in cosmology for different purposes, e.g.
+investigate the impact of systematic sources.
+It can be thought as a tool to forecast error from a given experimental set up e quantify how much information we can extract from it.
+
+Compared to other methods, such as the Markov chain Monte Carlo method, is extremely fast, however, several issues have to be taken into account. 
+The Fisher matrix is defined as the expectation value of the Hessian matrix of the likelihood $\mathcal{L}(C(\ell);\theta)$:
+\begin{equation}
+    F_{\alpha \beta}=\left \langle 
+    \frac{\partial^2\mathcal{L}}
+    {\partial \theta_{\alpha}\partial \theta_{\beta}}
+    \right \rangle .
+\end{equation}
+
+where we indicate with $\theta$ the cosmological parameters or any systematics included in the simulation.
+If we assume a Gaussian likelihood and a Covariance matrix $C_{ij}$ independent from $\theta$, we can calculate the Fisher matrix as
+\begin{equation}\label{Fisher_matrix}
+      F_{\alpha \beta}= \sum_{ij}\frac{\partial \mu}{\partial \theta_{\alpha}} C_{ij}^{-1}
+      \frac{\partial \mu}{\partial \theta_{\beta}}
+\end{equation}
+were we indicate as $ \frac{\partial \mu}{\partial \theta_{\alpha}} $ the derivatives of the summary statistics evaluated at the fiducial parameter values.
+In this paper, to compute the covariance matrix $C_{ij}$, we use 2000 independent simulations at the fiducial cosmology. 
+We assume a parameter-independent covariance matrix computed as:
+\begin{equation}
+    C_{ij}=\sum_{r=1}^N
+    \frac{(x_i^r-\mu_i)(x_i^r-\mu_)}{N-1}
+\end{equation}
+where $N$ is the number of independent realizations and $x_i^r$ is the value of the summary statistics in the $i^{th}$ bin for a given realization $r$ and $\mu$ is the mean of the summary statistics over all the realization in a given bin.
+Furthermore, we scale the covariance matrix by the ratio $f_{\text{map}}/f_{\text{survey}}$, where $f_{\text{map}}$ is the angular extend of our $\kappa$map and $f_{\text{survey}}$ is the étendue of the \textit{Vera C.
+Rubin Observatory}.
+The derivatives of the summary statistics in the Eq.\ref{Fisher_matrix} are computed averaging over 250 independent fiducial simulations.
+
 \section{Results}
@@
 
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+\bibliography{biblio.bib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}

### 2022-02-14 paper/paper.tex

@@
 \\
-PGD introduces control parameters that can be tuned comparing the matter power spectrum to a reference power spectrum.
+PGD introduces control parameters that can be tuned by comparing the matter power spectrum to a reference power spectrum.
 
@@
 
-In Figure \ref{fig:comp_dens_field} , we show the resulting density field when this operation is applied.
-We show a comparison of the density field image for a given redshift when the PGD correction is applied and when not \denise{write better this}.
-We can see that the structures are not modified but simply sharpened.
-\denise{image size and position}
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\columnwidth]{paper/figures/densitymap.png}
-%     \caption{Comparison of density planes at same redshift with and without the PGD correction.}
-%     \label{fig:comp_dens_field}
-% \end{figure}
-
-Figure \ref{fig:comp_kmap} shows the same result on the convergence map.
-\denise{image size and position}
+Figure \ref{fig:pkhalofit_comp} shows the matter power spectrum at $z=1.69$ of our simulations before and after applying the PGD correction compared to analytic Halofit predictions (\denise{cita}(Smith et al.
+2003; Takahashi et al.
+2012)).
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/kmap_compgd.png}
-    \caption{Comparison of the final convergence map with and without the PGD correction.}
-    \label{fig:comp_kmap}
+    \includegraphics[width=\columnwidth]{paper/figures/pkhalofit_comp.png}
+    \caption{
+    Upper panel: Comparison of the matter power spectrum of FlowPM before and after the PGD correction with reference matter power spectrum \textit{Halofit} at redshift $z = 1.69$.
+Lower panel: Fractional differences between FlowPM and Halofit.
+    }
+    \label{fig:pkhalofit_comp}
 \end{figure}
 
-In Figure \ref{fig:ps_comp} we compare the low resolution DLL convergence power spectrum complemented by the PGD scheme to a conventional DLL simulation with the same resolution.
-Both the outputs are compared to the angular power spectrum obtained from the $\kappa$TNG only dark matter simulation.
+In Figure \ref{fig:comp_kmap} we show an example of our convergence map at $ z= 1.034$, as well as the same map when the PGD correction is not applied. 
+We can see that the structures are not modified but simply sharpened.
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\textwidth]{paper/figures/kmap_compgd.png}
+    \caption{ \textbf{Left panel}: An example of our convergence map at source redshift $z= 1.034$.
+    \textbf{Right panel}: Same convergence map when the PGD correction is not applied.}
+    \label{fig:comp_kmap}
+\end{figure*}
+
+In Figure \ref{fig:ps_comp} in the upper panel, we present the DLL angular power spectrum complemented by the PGD scheme to a conventional DLL simulation with the same resolution.
+Both the outputs are compared to the analytic Halofit prediction for the angular power spectrum.
+In the lower panel the fractional differences between the our maps and the analytic Halofit prediction.
+Both the power spectra and ratios are averaged over $N = 100$ realisations.
 We can conclude that PGD scheme allows to achieve higher accuracy at the same computational cost.
-\denise{image size and position}
+
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/ps_comp.png}
-    \caption{Comparison of the angular power spectrum from the final convergence map with and without the PGD correction against $\kappa-$TNG only Dark-matter simulations.}
+    \includegraphics[width=\columnwidth]{paper/figures/clshalofit_comp.png}
+    \caption{
+    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
+our DLL maps. \textbf{Lower panel}: Fractional differences between the
+DLL and Halofit power spectra for 3 source redshifts. The power spectra and ratios are means over 100 map realisations. The two vertical lines define the range of $\ell$ between $[300,3000]$.}
     \label{fig:ps_comp}
@@
 \subsection{Summary statistics}
-In this work, in order to extract the cosmological information from the simulated $\kappa-$maps, we used tree statistics: the angular power spectrum, the peak counts and the $l_{1\text{norm}}$.
+In this work, in order to extract the cosmological information from the simulated $\kappa-$maps, we use tree summary statistic for weak lensing observable: the angular power spectrum, the `starlet peak counts' and the `starlet $l_{1\text{norm}}$'.
 
@@
 where $P_{\delta}$ defines the matter power spectrum of the density contrast.
-In this paper, the angular power spectrum is computed from the noisy smoothed convergence maps: to each mock $\kappa$map we add Gaussian noise and than convolved it with a Gaussian smoothing kernel with a smoothing size $\theta=3.6$.
-We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}.
+
+In this paper, the angular power spectrum is computed from the noisy smoothed convergence maps: to each mock $\kappa$map we add Gaussian noise and than convolved it with a Gaussian smoothing kernel.
+
+To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa-TNG$ simulations. 
+ We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:ps_comp}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/clshalofit_comp.png}
+    \caption{
+    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
+our DLL maps. \textbf{Lower panel}: Fractional differences between the
+DLL and Halofit power spectra for 3 source redshifts. The power spectra and ratios are means over 100 map realisations. The two vertical lines define the range of $\ell$ between $[300,3000]$.}
+    \label{fig:ps_comp}
+\end{figure}
+% with a smoothing size $\theta=3.6$. We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}.
+
 For each map, we compute the power spectrum by using our own code implemented in the Tensorflow framework and we take the average over 2000 maps realisation.

### 2022-02-14 paper/paper.tex
Updates from Overleaf

@@
 
-To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa-TNG$ simulations. 
- We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:ps_comp}.
+To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa$TNG simulations. 
+ We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:clsratktng_comp1arc}.
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/clshalofit_comp.png}
+    \includegraphics[width=\columnwidth]{paper/figures/clsratktng_comp1arc.png}
     \caption{
-    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
-our DLL maps. \textbf{Lower panel}: Fractional differences between the
-DLL and Halofit power spectra for 3 source redshifts. The power spectra and ratios are means over 100 map realisations. The two vertical lines define the range of $\ell$ between $[300,3000]$.}
-    \label{fig:ps_comp}
+The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions for 3 source redshifts.
+ The power spectra means over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. The shaded regions represent the standard deviation from 1000 $\kappa$TNG realisations.}
+    \label{fig:clsratktng_comp1arc}
 \end{figure}

### 2022-02-17 paper/paper.tex

@@
 To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa$TNG simulations. 
- We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:clsratktng_comp1arc}.
+ We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:clsktng_comp1arc}.
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/clsratktng_comp1arc.png}
+    \includegraphics[width=\columnwidth]{paper/figures/clsktng_comp1arc.png}
     \caption{
-The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions for 3 source redshifts.
- The power spectra means over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. The shaded regions represent the standard deviation from 1000 $\kappa$TNG realisations.}
-    \label{fig:clsratktng_comp1arc}
+    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
+our DLL maps compared to the $\kappa$TNG predictions.
+ \textbf{Lower panel}
+The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions.The shaded regions represent the standard deviation from 1000 $\kappa$TNG realisations. \\
+ The power spectra mean over 100 map realisations.The maps are smoothed with a 1 arcmin Gaussian filter. }
+    \label{fig:clsktng_comp1arc}
 \end{figure}
 % with a smoothing size $\theta=3.6$. We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}. 
-
-For each map, we compute the power spectrum by using our own code implemented in the Tensorflow framework and we take the average over 2000 maps realisation.
+\denise{draw conclusions from this plot}
+For each map, we compute the power spectrum by using our own code implemented in the Tensorflow framework.
+%and we take the average over 2000 maps realisation.
 
@@
 In this paper, we choose to bin the peaks as function of $\kappa$. 
-As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code and by averaging over 2000 different realizations.
+As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code.
+%and by averaging over 2000 different realizations. 
 A peak is identified as the pixel of larger value than its eight neighbors in the image, convolved with a starlet filter $\mathcal{W}(\theta_{\text{ker}})$:
@@
 \end{equation}
- We consider the peak distribution for 8 linearly spaced bins within the range $\kappa=[-0.05, 0.05]$. The bins are chosen such that at least 30 peaks are recorded in each bin.
+Similar to the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG.
+This allow us to identify the bins to discard (bins where the distribution of peaks is not Gaussian) as well as, the wavelet scale to discard. 
+In Figure 6, we show the number counts of peaks in the upper panels, and the fractional differences between the DLL and $\kappa$TNG-Dark maps in the lower panels.
+Again we smooth the convergence maps with a 1 arcmin Gaussian filter. The peak are counted for 8 linearly spaced bins within the range $(\kappa*\mathcal{W})=[-0.2, 0.5]$. 
+%The bins are chosen such that at least 30 peaks are recorded in each bin.
+
+\ref{fig:peakktng_comp1arc}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/peakktng_comp1arc.png}
+    \caption{
+      \textbf{Upper panel}: Peak counts from our DLL map at source redshift $z_s=1.034$ compared to the $\kappa$TNG at the same redshift.
+\textbf{Lower panel}: The fractional differences between the DLL and $\kappa$TNG map.
+ The peak counts mean over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. }
+    \label{fig:peakktng_comp1arc}
+\end{figure}
 
@@
 \subsubsection{Wavelet $\ell_1-$norm}
+
+\ref{fig:l1normktng_comp1arc}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/l1normktng_comp1arc.png}
+    \caption{
+      \textbf{Upper panel}: $l_1$norm from our DLL map at source redshift $z_s=1.034$ compared to the $\kappa$TNG at the same redshift.
+\textbf{Lower panel}: The fractional differences between the DLL and $\kappa$TNG map.
+ The $l_1$norm mean over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. }
+    \label{fig:l1normktng_comp1arc}
+\end{figure}
 

### 2022-03-01 paper/paper.tex

@@
     \caption{
+    \textbf{Upper panel}: Angular power spectra for 4 different smoothing size from
+our DLL maps compared to the $\kappa$TNG predictions.
+ \textbf{Lower panel}
+The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions. \\
+ The power spectra mean over 100 map realisations.The maps are computed for a single source redshift $z=1.034$. }
+    \label{fig:clsktng_comp1arc}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/clsktng_compsmoothing.png}
+    \caption{
     \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
@@
  The power spectra mean over 100 map realisations.The maps are smoothed with a 1 arcmin Gaussian filter. }
-    \label{fig:clsktng_comp1arc}
+    \label{fig:clsktng_compsmoothing}
 \end{figure}
@@
 
+\subsubsection{The wavelet Transform }
+
+The Wavelet transform has been widely used in astronomical images analysis due to its ability to decompose astronomical data into components at different scales. 
+This multiscale approach is well-suited for the study of astronomical data since their complex hierarchical structure. 
+In this work we filter the original convergence maps with the Starlet transform, or the Isotropic Undecimated Wavelet Transform, which reconstructs an image $c_0$ as the sum of all the wavelet scales and the coarse resolution image $c_J$:
+\begin{equation}
+    c_0(x,y)=c_J(x,y)+\sum_{j=1}^{J_{max}} w_j(x,y)
+\end{equation}
+
+where $j = J_{max} + 1$ and $w_j$ is an image of the same size of the original one, whose represents the details at a given resolution scales $j$, corresponding to a spatial size of $2^j$ pixels.
+
+ In this paper we chose a $J_{max}=5$, this Starlet filter applied to our map with a pixel size of 0.29 arcmin corresponds to a decomposition of the original map in 5 maps of resolution [0.59, 1.18 , 2.34, 4.69, 7.03] arcmin and a coarse map.
+
 \subsubsection{Wavelet Peak Counts}
@@
 There are different ways to record the weak lensing peaks: the number of peaks as a function of either the signal-to-noise ratio or the convergence $\kappa$ of the peaks. 
-In this paper, we choose to bin the peaks as function of $\kappa$. 
-As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code.
+In this paper, 
+%we choose to bin the peaks as function of $\kappa$. 
+%As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code.
 %and by averaging over 2000 different realizations. 
-A peak is identified as the pixel of larger value than its eight neighbors in the image, convolved with a starlet filter $\mathcal{W}(\theta_{\text{ker}})$:
+a peak is identified as the pixel of larger value than its eight neighbors in the image, convolved with a starlet filter $\mathcal{W}(\theta_{\text{ker}})$:
 \begin{equation}
-    \textbf{Peaks}=(\kappa*\mathcal{W})(\theta_{\text{ker}})
+    \textbf{Peaks}=(\kappa*\mathcal{W})(\theta_{\text{ker}}).
 \end{equation}
@@
 
-\ref{fig:peakktng_comp1arc}.
 \begin{figure}
@@
 
-\EiffL{Explain wavelets}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/peakktng_compallarc.png}
+    \caption{
+      The fractional differences between the DLL and $\kappa$TNG peak counts at source redshift $z_s=1.034$.
+ The peak counts mean over 100 map realisations. The diferent panels show the results when the maps are smoothed with a 1, 2 and 3.6 arcmin Gaussian filter. }
+    \label{fig:peakktng_compallarc}
+\end{figure}
 
@@
 \subsubsection{Wavelet $\ell_1-$norm}
+It was shown in \cite{ajani2021starlet} that the ‘starlet $l_1$-norm’ has  several advantages compared to the standard peak and void statistics, i.e.
+1) the $l_1-$norm includes the information encoded in all pixels of the map 2) avoids defining  what a peak is and what a void is.
+The ‘starlet $l_1$-norm’ is defined as the sum of the absolute values of the starlet coefficients of the weak lensing map in a given bin \textit{i}:
+\begin{equation}
+    l_1^{j,i}=\sum_{u=1}^{\text{coef}(\mathcal{S}_{j,i})} 
+    |\mathcal{S}_{j,i}[u]|=
+    ||\mathcal{S}_{j,i}||_1
+\end{equation}
+where the index \textit{u} runs to the total number of pixels in the \textit{i}-th bin and $\mathcal{S}_{j,i}$ is the set of all the wavelet coefficient computed at a given scale \textit{j}, such that $\mathcal{S}_{j,i}=
+\left \{  w_{j,k}/B_i<w_{j,k}<B_{i+1}\right \}$, with \textit{k} the pixel index and $B_i$ and $B_{i+1}$ the bin edges.
 
-\ref{fig:l1normktng_comp1arc}.
 \begin{figure}
@@
 
-\EiffL{Explain what's the deal with this l1 norm}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/l1normktng_compallarc.png}
+    \caption{
+      The fractional differences between the DLL and $\kappa$TNG $l_{norm}$ at source redshift $z_s=1.034$.
+ The $l_{norm}$ results mean over 100 map realisations. The different panels show the results when the maps are smoothed with a 1, 2 and 3.6 arcmin Gaussian filter. }
+    \label{fig:l1normktng_compallarc}
+\end{figure}
+
+\subsection{Galaxies redshift distribution}
+Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (``photo-z'') measurement are computed.
+In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
+In our analysis, according to \cite{zhang2021transitioning}, the underlying redshift distribution is modelled via the parametrized model
+\begin{equation}\label{photz}
+    \frac{dN}{dz} \propto z^{2} \exp{[-(z/z_0)^{\alpha}]},
+\end{equation}
+
+where we adopt $\alpha=0.94$ and fix $z_0=0.26$.
+
+The redshift distributions for the fiducial source samples are shown in Figure . 
+\begin{figure}\label{photoz}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/l1normktng_compallarc.png}
+    \caption{
+   Source sample redshift distributions for each tomographic bin. The y-axis shows the normalized \textit{n(z)} distributions such that $\sum n(z)dz=1.0$}
+    \label{fig:l1normktng_compallarc}
+\end{figure}
 
@@
 \subsection{Photometric redshift uncertainty}
-Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (''photo-z'') measurement are computed.
-In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
-For our analysis we considered a Smail-type galaxy distribution p(z) (Smail et al. 1994),
-\begin{equation}\label{photz}
-    p(z) \propto z^{\alpha} e^{-(\frac{z}{z_0})^{\beta}}
-\end{equation}
-
- We adopt  $\alpha=$, $\beta =$ and fix $z_0$ such that ?'
 
@@
 
-The first step to introduce the IA term in our simulation, consists in computing the projected tidal field from the three-dimensional mass over-density field $\delta(\vec{x}$
+The first step to introduce the IA term in our simulation, consists in computing the projected tidal field from the three-dimensional mass over-density field $\delta(\vec{x})$
 as (\cite{harnois2021cosmic})
@@
    \tilde{s}_{ij,2D}(\textbf{k}_{\bot})=
-   2 \pi 	\left [ \frac{k_ik_j}{k^2}- \frac{1}{3} \right ]
+   2 \pi 	\left [ \frac{k_ik_j}{k^2}- \frac{1}{3} \delta_{ij}^k  \right ]
   \tilde{\delta}_{2D}(\textbf{k}_{\bot})
@@
 \end{equation}
-where $\sigma_g$ is the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $~$ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
+where $\sigma_g$ is the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $\sim $ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
 In this work we use a Gaussian kernel and set the values of $\sigma_g=(idk yet) h^{-1}$Mpc.
@@
 Then the smoothed tidal field is interpolated on the light-cone. 
-Then, we couple the tidal field $s_{ij,2D}$ with the complex intrinsic ellipticities as (\cite{harnois2021cosmic}):
-\begin{equation}
-    \epsilon_{1}^{IA}=\frac{A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} (s_{xx}-s_{yy}), \ \ 
-      \epsilon_{2}^{IA}=-\frac{2A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} s_{xy},
+Then, the complex intrinsic ellipticities can be computed from the the tidal field $s_{ij,2D}$ as (\cite{harnois2021cosmic}):
+\begin{equation}\label{complex_el}
+    \epsilon_{1}^{IA}=- \frac{A_{IA}\bar{C}_1\bar{\rho}(z=0)}{D(z)} (s_{xx}-s_{yy}), \ \ 
+      \epsilon_{2}^{IA}=-\frac{2A_{IA}\bar{C}_1\bar{\rho}(z=0)}{D(z)} s_{xy},
 \end{equation}
-(\denise{check this formula})
-and compute the observed ellipticities as:
+and the observed ellipticities as:
 \begin{equation}
@@
 \end{equation}
+However, it is noted that the final expression of the intrinsic ellipticities will be:
+\begin{align}
+    \tilde{ \epsilon}_{1}^{IA}(\textbf{k}_{\bot}) & \propto
+    \left ( \frac{k_x^2-k_y^2}{k^2} \right )  \tilde{\delta}_{2D}(\textbf{k}_{\bot})
+   \mathcal{G}_{2D}(\sigma_g) \\
+       \tilde{ \epsilon}_{1}^{IA}(\textbf{k}_{\bot}) & \propto
+    \left ( \frac{k_x k_y}{k^2} \right )  \tilde{\delta}_{2D}(\textbf{k}_{\bot})
+   \mathcal{G}_{2D}(\sigma_g) \nonumber
+\end{align}
+that, except for the smoothing kernel, 
+are the same filters used to produce shear maps from the convergence maps by applying the Kaiser  Squires (1993, KS hereafter) inversion.
+Therefore, instead of using the Eq.\ref{complex_el} and applying the Kaiser Squires inversion to derive the $\kappa_{IA}$, 
+we decided to implement the model on the convergence map level, i.e. calculate the intrinsic alignment as part of the convergence map: 
+\begin{equation}
+    \kappa_{IA_{i}}= 
+    - A_{IA}\bar{C}_1\bar{\rho}(z=0)
+    \int_{z_{min}}^{z_{max}} 
+    n_{i}(z) \kappa_{z_{i}}
+    \frac{ dz}{D(z)}
+\end{equation}
+where the index \textit{i} refers to the \textit{i}-th redshift bins.
+\denise{not sure the part inside the integral, because D(z) was calculated before the integral}
 

### 2022-03-15 scripts/compute_jacobian.py
scripts update

@@ -56,7 +56,8 @@ FLAGS = flags.FLAGS
 
 
 @tf.function
-def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
+def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,
+                  photoz):
     """ Computes a convergence map using ray-tracing through an N-body for a given
     set of cosmological parameters
     """
@@ -120,7 +121,7 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
         lensplanes.append((r_center[i], states[::-1][i][0], plane))
 
     # Create array of source redshifts
-    z_source = 1/a_center-1
+    z_source = 1 / a_center - 1
     m = LSST_Y1_tomog(cosmology,
                       lensplanes,
                       box_size=FLAGS.box_size,
@@ -144,8 +145,8 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
                          nbin=3,
                          use_A_ia=True,
                          Aia=FLAGS.Aia)
-    kmap_IA =tf.stack(m)-tf.stack(m_IA) 
-    return kmap_IA, states, lensplanes, r_center, a_center
+    kmap_IA = tf.stack(m) - tf.stack(m_IA)
+    return kmap_IA, lensplanes, r_center, a_center
 
 
 def desc_y1_analysis(kmap):
@@ -172,35 +173,39 @@ def rebin(a, shape):
 
 
 @tf.function
-def compute_jacobian(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
+def compute_jacobian(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,
+                     photoz):
     """ Function that actually computes the Jacobian of a given statistics
     """
     params = tf.stack([Omega_c, sigma8, Omega_b, n_s, h, w0, Aia])
     with tf.GradientTape() as tape:
         tape.watch(params)
-        kmap_IA, states, lensplanes, r_center, a_center = compute_kappa(
+        kmap_IA, lensplanes, r_center, a_center = compute_kappa(
             params[0], params[1], params[2], params[3], params[4], params[5],
-            params[6], pgdparams,photoz)
+            params[6], pgdparams, photoz)
 
         # Adds realism to convergence map
[…]

### 2022-03-15 scripts/compute_jacobian_l1norm.py

@@ -12,6 +12,7 @@ from flowpm.tfpower import linear_matter_power
 import astropy.units as u
 from itertools import cycle
 import tensorflow_addons as tfa
+from flowpm.redshift import LSST_Y1_tomog
 import time
 from scipy.stats import norm
 from flowpm.NLA_IA import k_IA
@@ -21,6 +22,10 @@ from flowpm.tfbackground import rad_comoving_distance
 flags.DEFINE_string("filename", "jac_1_20.pkl", "Output filename")
 flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
                     "PGD parameter files")
+flags.DEFINE_string(
+    "photoz", "/global/homes/d/dlan/flowpm/notebooks/dev/nz_norm.npy",
+    "Normalized Photoz distribution, where the first array is the z, the remaining n(z)"
+)
 flags.DEFINE_float("Omega_c", 0.2589, "Fiducial CDM fraction")
 flags.DEFINE_float("Omega_b", 0.04860, "Fiducial baryonic matter fraction")
 flags.DEFINE_float("sigma8", 0.8159, "Fiducial sigma_8 value")
@@ -50,7 +55,8 @@ FLAGS = flags.FLAGS
 
 
 @tf.function
-def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams):
+def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,
+                  photoz):
     """ Computes a convergence map using ray-tracing through an N-body for a given
     set of cosmological parameters
     """
@@ -112,41 +118,32 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams):
 
         fourier_smoothing(plane, sigma=1.024, resolution=2048)
         lensplanes.append((r_center[i], states[::-1][i][0], plane))
-    xgrid, ygrid = np.meshgrid(
-        np.linspace(0, FLAGS.field_size, FLAGS.field_npix,
-                    endpoint=False),  # range of X coordinates
-        np.linspace(0, FLAGS.field_size, FLAGS.field_npix,
-                    endpoint=False))  # range of Y coordinates
-
-    coords = np.stack([xgrid, ygrid], axis=0)
-    c = coords.reshape([2, -1]).T / 180. * np.pi  # convert to rad from deg
     # Create array of source redshifts
[…]

### 2022-03-15 scripts/compute_jacobian_peakcounts.py

@@ -12,6 +12,7 @@ from flowpm.tfpower import linear_matter_power
 import astropy.units as u
 from itertools import cycle
 import tensorflow_addons as tfa
+from flowpm.redshift import LSST_Y1_tomog
 from flowpm import tfpm
 import time
 from scipy.stats import norm
@@ -22,6 +23,10 @@ from flowpm.tfbackground import rad_comoving_distance
 flags.DEFINE_string("filename", "jac_1_20.pkl", "Output filename")
 flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
                     "PGD parameter files")
+flags.DEFINE_string(
+    "photoz", "/global/homes/d/dlan/flowpm/notebooks/dev/nz_norm.npy",
+    "Normalized Photoz distribution, where the first array is the z, the remaining n(z)"
+)
 flags.DEFINE_float("Omega_c", 0.2589, "Fiducial CDM fraction")
 flags.DEFINE_float("Omega_b", 0.04860, "Fiducial baryonic matter fraction")
 flags.DEFINE_float("sigma8", 0.8159, "Fiducial sigma_8 value")
@@ -51,7 +56,8 @@ FLAGS = flags.FLAGS
 
 
 @tf.function
-def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams):
+def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,
+                  photoz):
     """ Computes a convergence map using ray-tracing through an N-body for a given
     set of cosmological parameters
     """
@@ -113,41 +119,33 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams):
 
         fourier_smoothing(plane, sigma=1.024, resolution=2048)
         lensplanes.append((r_center[i], states[::-1][i][0], plane))
-    xgrid, ygrid = np.meshgrid(
-        np.linspace(0, FLAGS.field_size, FLAGS.field_npix,
-                    endpoint=False),  # range of X coordinates
-        np.linspace(0, FLAGS.field_size, FLAGS.field_npix,
-                    endpoint=False))  # range of Y coordinates
 
-    coords = np.stack([xgrid, ygrid], axis=0)
-    c = coords.reshape([2, -1]).T / 180. * np.pi  # convert to rad from deg
     # Create array of source redshifts
-    lens_source = states[::-1][11][1]
[…]

### 2022-03-15 scripts/compute_jacobian_ps.py

@@ -43,7 +43,7 @@ flags.DEFINE_float("field_size", 5., "TSize of the lensing field in degrees")
 flags.DEFINE_integer("n_lens", 11, "Number of lensplanes in the lightcone")
 flags.DEFINE_integer("batch_size", 1,
                      "Number of simulations to run in parallel")
-flags.DEFINE_integer("nmaps", 1, "Number maps to generate.")
+flags.DEFINE_integer("nmaps", 10, "Number maps to generate.")
 flags.DEFINE_float(
     "Aia", 1.,
     "The amplitude parameter A describes the strength of the tidal coupling")
@@ -55,7 +55,8 @@ FLAGS = flags.FLAGS
 
 
 @tf.function
-def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
+def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,
+                  photoz):
     """ Computes a convergence map using ray-tracing through an N-body for a given
     set of cosmological parameters
     """
@@ -118,7 +119,7 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
         fourier_smoothing(plane, sigma=1.024, resolution=2048)
         lensplanes.append((r_center[i], states[::-1][i][0], plane))
     # Create array of source redshifts
-    z_source = 1/a_center-1
+    z_source = 1 / a_center - 1
     m = LSST_Y1_tomog(cosmology,
                       lensplanes,
                       box_size=FLAGS.box_size,
@@ -142,7 +143,7 @@ def compute_kappa(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
                          nbin=3,
                          use_A_ia=True,
                          Aia=FLAGS.Aia)
-    kmap_IA =tf.stack(m)-tf.stack(m_IA) 
+    kmap_IA = tf.stack(m) - tf.stack(m_IA)
     return kmap_IA, lensplanes, r_center, a_center
 
 
@@ -169,9 +170,9 @@ def rebin(a, shape):
     return tf.math.reduce_mean(tf.reshape(a, sh), axis=-1)
 
 
-
 @tf.function
-def compute_jacobian(Omega_c, sigma8, Omega_b, n_s, h, w0, Aia, pgdparams,photoz):
[…]

### 2022-03-15 scripts/compute_maps.py

@@ -20,8 +20,9 @@ from flowpm.NLA_IA import k_IA
 from flowpm.fourier_smoothing import fourier_smoothing
 from flowpm.tfbackground import rad_comoving_distance
 
-
-flags.DEFINE_string("filename", "/pscratch/sd/d/dlan/maps/maps4/results_maps.pkl", "Output filename")
+flags.DEFINE_string("filename",
+                    "/pscratch/sd/d/dlan/maps/maps4/results_maps.pkl",
+                    "Output filename")
 flags.DEFINE_string("pgd_params", "results_fit_PGD_205_128.pkl",
                     "PGD parameter files")
 flags.DEFINE_string(
@@ -110,7 +111,7 @@ def compute_kappa(Omega_c, sigma8, Aia, pgdparams, photoz):
 
         plane = fourier_smoothing(plane, sigma=1.024, resolution=2048)
         lensplanes.append((r_center[i], states[::-1][i][0], plane))
-    z_source = 1/a_center-1
+    z_source = 1 / a_center - 1
     m = LSST_Y1_tomog(cosmology,
                       lensplanes,
                       box_size=FLAGS.box_size,
@@ -134,7 +135,7 @@ def compute_kappa(Omega_c, sigma8, Aia, pgdparams, photoz):
                          nbin=3,
                          use_A_ia=True,
                          Aia=FLAGS.Aia)
-    kmap_IA =tf.stack(m)-tf.stack(m_IA) 
+    kmap_IA = tf.stack(m) - tf.stack(m_IA)
     return kmap_IA, m, m_IA
 
 

### 2022-03-16 paper/paper.tex
Updates from Overleaf

@@
 \usepackage[figure,figure*]{hypcap}
-
-\usepackage{url}
+\usepackage{hyperref}
+% \usepackage{url}
 \urlstyle{same}
@@
 
-\subsubsection{FLOWPM}
-Our weak lensing simulation tool is based on FlowPM (/cite Modi, Lanusse et al.
-), a fast particle-mesh solver that implements the time integration for gravitational evolution starting from the Gaussian initial conditions of the Universe to the observed large scale structures through a Kick-Drift scheme.
+\subsubsection{N-body simulations}
 
-After instantiating the $\Lambda$CDM cosmology with our desired parameters, (the initial power spectrum and the evolution of the particles depend from $\sigma_8$ and $\Omega_{c}$) we created the initial condition for the N-body simulation using the normalised linear matter power spectrum as implemented by (/cite Eisenstein and Hu of '98 ) and generated the linear field at requested scale.
-After that, we implemented the N-body.
-As said before, The N-body simulation does the time integration of a given initial linear field  across a given array of scale factors implementing a series of Kick-Drift-Kick operations.
-During the \textit{Kick} operation we estimate the gravitational force experienced by every particles implementing Fast Fourier Transform and update their momentum.
-In the next state, \textit{Drift}, the particles are displaced and their positions is updated with the velocity estimated in the previous step.
-This operation is continued until the observed large scale structures at the final time-step.
-To perform the lightcone computation and extract the lens planes,  we export several intermediate state from the N-body simulation.
-From a given intermediate state we extract a slice and project it as a density plane by painting the particles on a 2D mesh.
-After creating a grid of coordinates, the lens planes are interpolated onto sky coordinates. 
+Our weak lensing simulation tool is based on the FlowPM (\cite{modi2021flowpm}) N-body code.
+FlowPM is a fast particle-mesh solver that implements the time integration of a given initial linear field  across a given array of scale factors implementing a series of Kick-Drift-Kick operations.
+We assume a flat $\Lambda$CDM universe and fix the cosmological parameters such that they match the results of Planck 2015 (\cite{ade2016planck}).
+We run simulations with $128^3$ particles in a volume of $205^3 h^{-1}$ Mpc$^3$.
+The initial condition are generated at redshift $z_{init}=9$ by using the normalised linear matter power spectrum as implemented by (\cite{eisenstein1998baryonic}) and generated the linear field at requested scale.
+The simulations are run with 4 time steps equally spaced in scale factor up to the redshift $z=0.972$, and 11 time steps equally spaced in comoving distance of $205$ $h^{-1}$Mpc (length of the box size) up to the final redshift $z=0.0$.
+\\
+We export the snapshots corresponding to the last eleven time steps, this we allow us to build the light cone necessary to construct the weak lensing mock maps.
+
+\subsection{Ray-Traced Weak Lensing simulated Maps}
+As mentioned above, to perform the lightcone computation and extract the lens planes, we export several intermediate states from the N-body simulation in a redshifts between $z= 0-0.91$. 
+In Table we summarise our light cone configuration, including the center comoving distance and redshift for each snapshot.
+
+To recover the redshift range of the lightcone, the unit box is replicated using periodic boundary conditions.
+First, we generate rotation matrices along the three axes, hence, each snapshot is rotated around each of the three axes, finally all the particles are randomly shifted along the axes.
+To obtain the final density field, each snapshot is projected in a 2D plane by estimating its density with a cloud-in-cell scheme. 
+After creating a Cartesian grid of coordinates, each slice is interpolated onto sky coordinates.
  At this point, we have constructed a ray tracer object, to compute the convergence, we directly integrate the lensing density along the unperturbed line of sight.
@@
 \subsubsection{Additional validation for our ray-tracing implementation } 
-As an additional test to validate our ray-tracing, instead of running the N-body simulation to generate the snapshots of particles for different scale factors, we create these snapshots by using a linear matter power spectrum at a given fixed redshift $z=0.52$ .
+As an additional test to validate our ray-tracing, instead of running the N-body simulation to generate the snapshots of particles for different scale factors, we create these snapshots by using a linear matter power spectrum at a given fixed redshift $z=0.2$ .
 \\
@@
 Fig.
-shows a comparison between the theoretical linear matter power spectrum computed using the Jax-cosmo library at the redshift $0.52$ and the matter power spectrum computed from the resulting snapshots, after applying the painting operations.
-As we can see the matter power spectrum start to lack in power for $k$(maggiore o circa uguale)1.
-This is probably due to the paint operation and is something to take into account when we will study the final power spectrum.
-
-From the full projected boxes of the simulations, we exported the lens planes, then interpolated on the light-cones.
-
-The final angular power spectrum is obtained averaging over 1000 samples.
+shows a comparison between the theoretical linear matter power spectrum computed using the Jax-cosmo library\footnote{\url{https://jax-cosmo.readthedocs.io/en/latest/}} at the redshift $0.2$ and the matter power spectrum computed from the resulting snapshots, after applying the painting operations.
+The results are shown after correcting the paint operation with a compensation function.
+The matter power spectrum compute from the snapshots are averaged over 50 simulations.
+\begin{figure*}
+    \centering
+    \includegraphics{paper/figures/pkhalofit_comp.png}
+    \caption{
+    Upper panel: Comparison of the matter power spectrum of FlowPM before and after the PGD correction with reference matter power spectrum \textit{Halofit} at redshift $z = 1.69$.
+Lower panel: Fractional differences between FlowPM and Halofit.
+    }
+    \label{fig:pklinear_comp}
+\end{figure*}
 
@@
 
-Figure \ref{fig:pkhalofit_comp} shows the matter power spectrum at $z=1.69$ of our simulations before and after applying the PGD correction compared to analytic Halofit predictions (\denise{cita}(Smith et al.
-2003; Takahashi et al.
-2012)).
+Figure \ref{fig:pkhalofit_comp} shows the matter power spectrum at $z=1.69$ of our simulations before and after applying the PGD correction compared to analytic Halofit predictions (\cite{smith2003stable}; \cite{takahashi2012revising}).
 \begin{figure}
@@
     \label{fig:ps_comp}
+\end{figure}
+
+\subsection{Galaxies Redshift distribution}
+In this work, we create mock data sets according to LSST Y1 data requirements.
+\denise{noise}
+
+We perform tomographic study using the redshift distributions modeled by \cite{zhang2021transitioning}, where the underlying redshift distribution is modeled via the parametrized form:
+\begin{equation}\label{photz}
+    \frac{dN}{dz} \propto z^{2} \exp{[-(z/z_0)^{\alpha}]},
+\end{equation}
+and $\alpha=0.94$ and $z_0=0.26$.
+However, we restrict our analysis up to redshift $\sim 1$, which corresponds to consider the first three redshift bins. 
+The redshift distributions for the fiducial source samples is shown in Figure \ref{photoz}.
+
+Specifically, we mock 11 source planes and for each of them, we produce 1000 independent realizations
+
+The Tab.  shows the redshift used to create the source planes.
+
+\begin{figure}\label{photoz}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/photoz_dis.png}
+    \caption{
+   Source sample redshift distributions for each tomographic bin. The y-axis shows the normalized \textit{n(z)} distributions such that $\sum n(z)dz=1.0$}
+    \label{fig:l1normktng_compallarc}
 \end{figure}
@@
 
-\subsection{Galaxies redshift distribution}
-Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (``photo-z'') measurement are computed.
-In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
-In our analysis, according to \cite{zhang2021transitioning}, the underlying redshift distribution is modelled via the parametrized model
-\begin{equation}\label{photz}
-    \frac{dN}{dz} \propto z^{2} \exp{[-(z/z_0)^{\alpha}]},
-\end{equation}
-
-where we adopt $\alpha=0.94$ and fix $z_0=0.26$.
-
-The redshift distributions for the fiducial source samples are shown in Figure . 
-\begin{figure}\label{photoz}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/l1normktng_compallarc.png}
-    \caption{
-   Source sample redshift distributions for each tomographic bin. The y-axis shows the normalized \textit{n(z)} distributions such that $\sum n(z)dz=1.0$}
-    \label{fig:l1normktng_compallarc}
-\end{figure}
-
 \section{Systematic effects}
@@
 \subsection{Photometric redshift uncertainty}
-
+Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (``photo-z'') measurement are computed.
+In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
  We take into account the uncertainty of the redshift distributions by introducing  a shift of the distributions defined by Eq.\ref{photz} according to the nuisance parameters $\Delta_z$:

### 2023-03-16 paper/authors.tex
Added a new section
revisited after 1 review

@@
 % paper leads
-\author{Denize Lanzieri}
-\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}
+\author{Denise Lanzieri}
+\affiliation{Université Paris Cité, Université Paris-Saclay, CEA, CNRS, AIM, F-91191, Gif-sur-Yvette, France}
 
 \author[0000-0001-7956-0542]{Fran\c{c}ois Lanusse}
-\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}
+\affiliation{Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France; }
 
-%main partticipants and text contributors  (alphabetical)
+%First Tier authors (alphabetical)
 \author{Chirag Modi}
-\noaffiliation
+\affiliation{Center for Computational Astrophysics,
+Center for Computational Mathematics,
+Flatiron Institute, New York, NY 10010, USA}
+% \noaffiliation
 
-% minor contributions and/or text writers (alphabetical)
+\author{Benjamin Horowitz}
+\affiliation{Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, 94720, CA, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
+
+\author{Joachim Harnois-Déraps}
+\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU Newcastle-upon-Tyne, UK}
+% Second Tier authors (alphabetical)
+\author{Jean-Luc Starck}
+\affiliation{Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France; }

### 2023-03-16 paper/paper.tex

--- 2022-02-17 paper/paper.tex
@@
 \usepackage[figure,figure*]{hypcap}
-
+\usepackage{hyperref}
 \usepackage{url}
 \urlstyle{same}
-
 \usepackage{lineno}
@@
 
+\newcommand{\jl}[1]{{\color{orange}JL: #1}}
 \newcommand{\EiffL}[1]{{\color{cyan}FL: #1}}
 \newcommand{\denise}[1]{{\color{red}DL: #1}}
-
+\usepackage{microtype}
+\usepackage{graphicx}
+\usepackage{fontawesome}
+\newcommand{\github}{\href{https://github.com/DifferentiableUniverseInitiative/flowpm/tree/master}{\faGithub}}
+\newcommand{\nblink}[1]{\href{https://github.com/DifferentiableUniverseInitiative/flowpm/tree/nbody_ode/notebooks/#1.ipynb}{\faFileCodeO}}
 % header settings
@@
 \begin{abstract}
-In this project we investigate the relative constraining power of various map-based higher order weak lensing statistics in an LSST setting.
-Such comparisons are typically very costly as they require a large number of simulations, and become intractable for more than 3 or 4 cosmological parameters.
-Instead we propose a new methodology based on the TensorFlow framework for automatic differentiation, and more specifically the public FlowPM N-body simulation code.
-By implementing ray-tracing in this framework, we will be able to simulate lensing lightcones, and compute Higher Order lensing statistics on the resulting maps.
-These statistics can then be differentiated with respect to cosmology, or any systematics included in the simulations, thus allowing, for exact Fisher forecasts.
+We present the Differentiable Lensing Lightcone (DLL), a fully differentiable physical model designed for being used as a forward model in Bayesian inference algorithms requiring access to derivatives of lensing observables with respect to cosmological parameters.
+We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones \denise{and implementing the Born approximation} in the Tensorflow framework.
+Furthermore, DLL is aimed at achieving high accuracy with low computational costs.
+As such, it integrates a novel Hybrid Physical-Neural parameterisation able to compensate for the small-scale approximations resulting from particle-mesh schemes for cosmological N-body simulations.
+We validate our simulations in an LSST setting against high-resolution $\kappa$TNG simulations by comparing both the lensing angular power spectrum and multiscale peak counts.
+We demonstrate an ability to recover lensing $C_\ell$ up to a 10\% accuracy at $\ell=1000$ for sources at redshift 1, with as few as $\sim 0.6$ particles per Mpc/h.
+As a first use case, we use this tool to investigate the relative constraining power of the angular power spectrum and peak counts statistic in an LSST setting.
+Such comparisons are typically very costly as they require a large number of simulations, and do not scale well with the increasing number of cosmological parameters.  
+As opposed to forecasts based on finite differences, these statistics can be analytically differentiated with respect to cosmology, or any systematics included in the simulations at the same computational cost of the forward simulation.
+We find that the peak counts outperform the power spectrum on the cold dark matter parameter $\Omega_c$, on the amplitude of density fluctuations $\sigma_8$, and on the
+amplitude of the intrinsic alignment signal $A_{IA}$.
 \end{abstract}
@@
 \section{Introduction}
+Weak gravitational lensing by Large Scale Structures (LSS) is one of the key probes to test cosmological models and gain insight into constituents of the Universe.
+The upcoming stage-IV surveys, such as the Legacy Survey of Space and Time (LSST) of the Vera C.
+Rubin Observatory \citep{ivezic2019lsst}, the Nancy Grace Roman Space Telescope \citep{spergel2015wide}, and  the Euclid Mission \citep{laureijs2011euclid}, will provide measurements of billions of galaxy shapes with unprecedented accuracy, which in turn will lead to tight constraints on dark energy models \citep[e.g.][]{mandelbaum2018lsst}.
 
-\section{Methods}
+With the increased statistical power of these surveys comes the question of their optimal analysis.
+Traditional cosmological analysis rely on measurements of the two-point statistics, either the shear two-point correlation functions or its Fourier transform, the lensing power spectrum.
+However, the two-point statistics are only optimal for Gaussian fields, and do not fully capture the non-Gaussian information imprinted in the lensing signal at the scales that future surveys will be able to access (e.g.
+information encoded in the peaks and in the filamentary features of the matter distribution).
 
-%We compare the sensitivity of three different map-based statistics: angular power spectra, the peak counts and the $l_{1\text{norm}}$.
- %the calculation of the summary statistics, and the Fisher Forecast process.
+ This has led to the introduction of a number of  higher-order statistics to access the non-Gaussian information from weak lensing data: 
+the weak lensing one point PDF \citep{liu2019constraining, uhlemann2020fisher, boyle2021nuw}, lensing peak counts \citep{liu2015cosmology, liu2015cosmological, lin2015new, kacprzak2016cosmology, peel2017cosmological, shan2018kids, martinet2018kids, ajani2020constraining, harnois2021cosmic, zurcher2022dark}, Minkowski functionals \citep{kratochvil2012probing, petri2013cosmology}, moments of mass maps \citep{gatti2021dark}, wavelet and scattering transforms \citep{ajani2021starlet, cheng2021weak},, and 3 point statistics \citep{takada2004cosmological, semboloni2011weak, rizzato2019tomographic, halder2021integrated}.
 
-\subsection{{Weak lensing}}
+Recently, machine learning-based methods that broadly fall in the category of Simulation-Based Inference (SBI) \citep{fluri2019cosmological, kacprzak2022deeplss, fluri2021cosmological, jeffrey2021likelihood, fluri2022full}, and Bayesian forward-modeling frameworks \citep{porqueres2021bayesian, sarma2022map} have also been introduced to attempt to fully account for the non-Gaussian content in the weak lensing signal.
+Unlike the methods described above, these approaches are designed to access the full field-level information content.
+Even though these techniques are asymptotically theoretically optimal in terms of information recovery, they still suffer from significant limitations.
 
-Weak gravitational lensing is a promising observational technique to infer the projected matter density distribution between an observer and a source by measuring galaxy shape correlations. 
+SBI methods are characterized by the absence of an analytical model to describe the observed signal and instead rely on learning a likelihood from simulations.
+Modern approaches employ deep learning-based density estimation methods to model the likelihood without the need to make any Gaussianity assumptions, and as such have
+drawn the attention of the community \citep{alsing2018massive, jeffrey2021likelihood}.
+
+A key element common to most of these methodologies is their ability to benefit from gradient information. 
+For example, \cite{porqueres2021bayesian} present a Bayesian hierarchical approach to infer the cosmic matter density field simultaneously with cosmological parameters using the Hamiltonian Monte Carlo (HMC) algorithm to explore the full high-dimensional parameter space.
+The HMC algorithm exploits the information encoded in the gradients of the joint likelihood function to inform each update step and hence requires the derivatives of the forward model.
+
+ As a different class of examples, \cite{makinen2021lossless} demonstrate that the full information content of a cosmological field can be represented by optimal summaries, allowing for likelihood-free and near-exact posteriors for cosmological parameters.
+In particular, they use neural networks trained on simulations to maximise the Fisher information, which requires having access to derivatives of the simulation model to compute a Fisher matrix.
+
+One possible way of evaluating these gradients with respect to cosmological parameters is by using numerical differentiation, e.g.
+computing a finite difference of a given statistic by varying the simulation fiducial values by a small amount.
+However, numerical differentiation is expensive in terms of computational resources and simulation time, and also requires hyperparameter tuning for the step size used in the finite difference scheme.
+An alternative option consists in computing the gradient analytically.
+Both these solutions are faced with limitations: the first approach gets computationally intractable in high dimensions, while the analytic gradients are sometimes impossible to estimate.
+All of these new techniques for cosmological analyses make the development of fast and differentiable simulations necessary.
+
+\cite{bohm2021madlens} developed MADLens, a CPU-based python package for producing non-Gaussian lensing convergence maps.
+These maps are differentiable with respect to the initial conditions of the underlying numerical simulations and to the cosmological parameters $\Omega_m$ and $\sigma_8$.
+In this paper,  we aim to efficiently compute gradients that benefit the development of new inference algorithms for weak lensing surveys.
+To do this we extend the framework of the FlowPM package \cite{modi2021flowpm} by implementing the Born approximation and simulating lensing lightcones in the Tensorflow framework.
+TensorFlow is a tensor library that includes the ability to perform automatic differentiation.
+Automatic differentiation enables us to compute gradients exactly as opposed to finite differences, which only provide approximate gradients.
+Specifically, TensorFlow implements the backpropagation algorithm to compute gradients, i.e.
+first it creates a graph (e.g.
+data structures representing units of computation), then it works backward through the graph by applying the chain rule at each node.
+\denise{Unlike MADlens, our tool is GPU-based and provides derivatives with respect to all the cosmological parameters.
+There are also differences in the implementation of various functions to improve accuracy and speed.}
+
+We validate our simulations against the cosmological N-body simulations $\kappa$TNG \citep{osato2021kappatng} by comparing both the lensing angular power spectrum and multiscale peak counts.
+
+In particular, as a first application, we show how the differentiability of numerical simulations can be exploited to evaluate the Fisher Matrix.
+Then, we compare the constraining power of two map-based weak lensing statistics: the lensing power spectrum and peak counts and investigate the degeneracy in high dimensional cosmological and nuisance parameter space through Fisher forecasts.
+
+This paper is structured as follows: in \autoref{weak_lesning_modeling} we briefly review the weak lensing modeling including the theoretical framework and the summary statistics used in this work.
+In \autoref{Fast_and_Differentiable_Lensing_Simulations} we introduce the numerical simulations illustrating the numerical methods used to generate mock WL maps.
+In \autoref{Validating_simulations_for_LSST_Y} we validate the simulations by comparing the statistics from our simulations and $\kappa$TNG-Dark ones.
+The Fisher forecast formalism and the survey and noise setting are shown in \autoref{Application_Fisher_forecast_for_HOS}.
+We finally discuss our results and present our conclusions afterward, in \autoref{Discussion} and \autoref{Conclusions}.
+
+\section{Weak Lensing Modeling}\label{weak_lesning_modeling}
+\subsection{{Cosmic shear}}
+Weak gravitational lensing is a powerful probe to infer the projected matter density distribution between an observer and a source.
 The effect of gravitational lensing 
-can be quantified in term of the separation vector \textbf{x} between a ray and a fiducial ray separated by the angle $\boldsymbol{\theta}$ at the observer:
+can be quantified in term of the separation vector \textbf{x} between two light rays separated by an angle $\boldsymbol{\theta}$:
 \begin{align}\label{sep}
@@
     f_k(\chi)\boldsymbol{\theta} + \\
-   &- \frac{2}{c^2}
+   - \frac{2}{c^2}
    \int_0^{\chi}
-    \text{d}\chi'
+    &  \text{d}\chi'
     f_k(\chi-\chi')
@@
 \end{align}
-where we denote as $\Phi$ and $\Phi^{0}$ the potential along the two light rays, and as $f_k(\chi)$ and $\chi$ the angular and radial comoving distance.
+with $\Phi$ and $\Phi^{0}$ the gravitational potential along the two light rays, $f_k(\chi)$ and $\chi$ the angular and radial comoving distance.
 
-The Jacobian matrix, describing the linearized lens mapping, is defined as:
+Formally, the effect of the linearized lens mapping is described by the Jacobian matrix:
 \begin{equation}
@@
 \end{equation}
-We know that the knowledge of the gravitational potential and the use of accurate solvers for light ray trajectories is computationally expensive.
-Nevertheless, the integral equation \ref{sep} can be approximated by considering the series expansion in power of $\Phi$ and truncating the series at the first term.
-With this assumptions, and considering that $\nabla_{\bot}\boldsymbol{\Phi}^0$ does not depend from $\boldsymbol{\theta}$, the Jacobian matrix can be written as:
+In the limit of weak-field metric (small $\Phi$), the integral in \autoref{sep} can be approximated by considering the series expansion in power of $\Phi$ and truncating the series at the first term.
+With this assumptions, given that $\nabla_{\bot}\boldsymbol{\Phi}^0$ not dependent from $\boldsymbol{\theta}$, the Jacobian matrix can be written as:
 \begin{equation}
@@
 \end{equation}
-Notice that this approximation, also known as Born approximation, is only valid in the limit of weak-field metric (small $\Phi$).
-
+This, also known as Born approximation, corresponds to integrating the potential gradient along the unperturbed ray.
 If we define the 2D potential, the \textit{lensing potential} as:
@@
    \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)f_k(\chi')}
-  \Phi(f_k(\chi')\boldsymbol{\theta},\chi').
+  \Phi(f_k(\chi')\boldsymbol{\theta},\chi')
 \end{equation}
@@
 From the parametrization of the symmetrical matrix $\mathcal{A}$, we can define the spin-two shear $\gamma=(\gamma_1,\gamma_2)$ and the scalar convergence field, $\kappa$. 
-Hence, the convergence and the shear are defined as second derivative of the potential:
+Hence, the convergence and the shear are defined as the second derivative of the potential:
 \begin{equation}\label{kshear}
-    \kappa=\frac{1}{2}(\partial_1\partial_1+\partial_2\partial_2)\psi; \ \gamma_1=\frac{1}{2}(\partial_1\partial_1-\partial_2\partial_2)\psi; \ 
+    \kappa=\frac{1}{2}(\partial_1\partial_1+\partial_2\partial_2)\psi;  
+\end{equation}
+\begin{equation}
+ \gamma_1=\frac{1}{2}(\partial_1\partial_1-\partial_2\partial_2)\psi; \  \  \
  \gamma_2=\partial_1\partial_2\psi;   
 \end{equation}
-
-The two fields $\gamma$ and $\kappa$ describe the distortion in the shape of the image, and the change in the angular size, respectively.
-By combining the 2D Poisson equation with the Eq.\ref{kshear} the convergence $\kappa$ becomes:
-\begin{equation}
+the two fields $\gamma$ and $\kappa$ describe the distortion in the shape of the image, and the change in the angular size, respectively.
+By combining the 2D Poisson equation with the \autoref{kshear}, the convergence $\kappa$ becomes:
+\begin{equation}\label{born_approx}
     \kappa_{born}(\boldsymbol{\theta})= \frac{3H_0^2 \Omega_m}{2c^2}
@@
 \end{equation}
-where we define the \textit{lensing efficiency}
+where we define the \textit{lensing efficiency}:
 \begin{equation}
    g(\chi) \equiv
-   \text{d}\chi'
+  \int_{\chi}^{\chi_{lim}} \text{d}\chi'
    n(\chi')
@@
 
-\subsection{Simulation}
-It's well known that an common feature of statics beyond second-order is the absence of analytical models with which to predict the observed signals.
-Hence, we need to adopt a forward modelling approach and create a suite of numerical simulations.
-In the following section we introduce the mass map simulation procedure, including a description of the simulator and of the construction of the weak lensing lightcone.
+\subsubsection{Intrinsic alignments (NLA)}
 
-\subsubsection{FLOWPM}
-Our weak lensing simulation tool is based on FlowPM (/cite Modi, Lanusse et al.
-), a fast particle-mesh solver that implements the time integration for gravitational evolution starting from the Gaussian initial conditions of the Universe to the observed large scale structures through a Kick-Drift scheme.
+The galaxy ellipticity observed by a telescope can be decomposed in the cosmic shear signal $\gamma$ and the intrinsic ellipticity of the source $\epsilon^{int}$, where the latter is the combination of the alignment term $\epsilon^{IA}$ and the random component $\epsilon^{ran}$.
 
-After instantiating the $\Lambda$CDM cosmology with our desired parameters, (the initial power spectrum and the evolution of the particles depend from $\sigma_8$ and $\Omega_{c}$) we created the initial condition for the N-body simulation using the normalised linear matter power spectrum as implemented by (/cite Eisenstein and Hu of '98 ) and generated the linear field at requested scale.
-After that, we implemented the N-body.
-As said before, The N-body simulation does the time integration of a given initial linear field  across a given array of scale factors implementing a series of Kick-Drift-Kick operations.
-During the \textit{Kick} operation we estimate the gravitational force experienced by every particles implementing Fast Fourier Transform and update their momentum.
-In the next state, \textit{Drift}, the particles are displaced and their positions is updated with the velocity estimated in the previous step.
-This operation is continued until the observed large scale structures at the final time-step.
-To perform the lightcone computation and extract the lens planes,  we export several intermediate state from the N-body simulation.
-From a given intermediate state we extract a slice and project it as a density plane by painting the particles on a 2D mesh.
-After creating a grid of coordinates, the lens planes are interpolated onto sky coordinates. 
- At this point, we have constructed a ray tracer object, to compute the convergence, we directly integrate the lensing density along the unperturbed line of sight.
+Different theoretical models have been proposed to describe the physics of Intrinsic Alignments (IA), such as the Non-Linear tidal Alignment model (NLA) (e.g.
+in \citet{Bridle_2007}), the tidal torquing model \citep{PhysRevD.70.063526, 10.1046/j.1365-8711.2001.04105.x}, or the combination of both the Tidal Alignment and Tidal Torquing model (TATT)  \citep{PhysRevD.100.103506}.
+We model the IA effect using the NLA description \citep{harnois2021cosmic}, i.e. assuming a linear coupling between the intrinsic galaxy shapes and the non-linear projected tidal fields $s_{ij}$:
+\begin{equation}\label{complex_e}
+    \epsilon_{1}^{IA}=- \frac{A_{IA}\bar{C}_1\bar{\rho}(z=0)}{D(z)} (s_{xx}-s_{yy}), \ \ 
+      \epsilon_{2}^{IA}=-\frac{2A_{IA}\bar{C}_1\bar{\rho}(z=0)}{D(z)} s_{xy},
+\end{equation}
+from which the observed ellipticities are computed as:
+ \begin{equation}
+    \boldsymbol{\epsilon}^{obs}=
+    \frac{\boldsymbol{\epsilon}^{int}+\textbf{g}}{1+\boldsymbol{\epsilon}^{int,*}\textbf{g}}, \ \  \text{with}  \ \
+    \boldsymbol{\epsilon}^{int}=
+    \frac{\boldsymbol{\epsilon}^{
+     IA}+\boldsymbol{\epsilon^{ran}}}
+     {1+\boldsymbol{\epsilon}^{IA,*}\boldsymbol{\epsilon^{ran}}}.
+\end{equation}
+The $A_{IA}$ term in \autoref{complex_e} defines the strength of the tidal coupling, $\bar{C}_1$ is a constant
+calibrated in \citet{brown2002measurement}, $D(z)$ is the linear growth function and $\bar{\rho}$ is the matter density.
 
-\subsubsection{Additional validation for our ray-tracing implementation } 
-As an additional test to validate our ray-tracing, instead of running the N-body simulation to generate the snapshots of particles for different scale factors, we create these snapshots by using a linear matter power spectrum at a given fixed redshift $z=0.52$ .
-\\
-Specifically, we estimate the initial LPT displacement given an input linear (real) field.
+\subsection{Lensing Summary Statistics }\label{stat}
+To extract the cosmological information from the simulated $\kappa-$maps, we use two summary statistics for weak lensing observable: the angular power spectrum and the starlet peak counts \citep{lin2016new}.
 
-As we said, the aim of this test is to prove the validity of our ray-tracing.
-In principle, without the N-body simulations and his possible approximations and systematics, any disagreement between the angular power spectrum computed from the final convergence map
-and the angular power spectrum we use as reference can be attributable to the ray-tracing.
-
-Fig.
-shows a comparison between the theoretical linear matter power spectrum computed using the Jax-cosmo library at the redshift $0.52$ and the matter power spectrum computed from the resulting snapshots, after applying the painting operations.
-As we can see the matter power spectrum start to lack in power for $k$(maggiore o circa uguale)1.
-This is probably due to the paint operation and is something to take into account when we will study the final power spectrum.
-
-From the full projected boxes of the simulations, we exported the lens planes, then interpolated on the light-cones.
-
-The final angular power spectrum is obtained averaging over 1000 samples.
-
-\subsubsection{Potential Gradient Descendent (PGD)}    
-Fast N-body simulations can be used as viable alternative to full N-body to model the galaxy statistics and create fast and low computational costs realizations of the large scale structures.
-Nevertheless, this kind of simulations lack resolution on small scale and can't give accurate halo matter profiles or matter power spectrum.
-
-To recover this missing accuracy, we employs the PGD scheme (\cite{Dai_2018}). 
-The main goal is to mimic the physics lost in the low resolution simulations by computing the short range force operation as an additional correction displacements in a post-processing step. \\
-The additional displacement is computed by pointing the particles towards a filtered potential minimum of the particle mesh solver.
-
-%\begin{equation}\label{displacement}
- %   \textbf{S}=4\pi G \bar{\rho}\alpha_{PM}/H_0^2 \nabla(
-  % \hat{\textbf{O}}_l(k)
-   %  \hat{\textbf{O}}_s(k)
-    %\nabla^{-2}\delta),
-%\end{equation}
-%where $\hat{\textbf{O}}_l(k)= \exp{(\frac{k^2}{k^4_l})}$ and $\hat{\textbf{O}}_s(k)= \exp{(-\frac{k^4}{k^4_s}})$ are the low and high pass filter introduced to remove the long range force and to reduce the numerical effect induced by the mesh resolution.
-\\
-PGD introduces control parameters that can be tuned by comparing the matter power spectrum to a reference power spectrum.
-
-We employ an online-PGD technique worth mentioning here: the correction involved in computing additional displacements is computed after every drift step in the N-body simulation.
-
-We find that a PGD correction computed directly at the end of the simulation fails, introducing some significant sharp clusters or changing the shape of some of the structures.
-Effectively this is equivalent to requesting a too large correction at once, which our method avoids.
-
-In practice we set it up so that it takes the power spectra at all intermediate redshift and fits the PGD parameters as to recover the \textit{Halofit} non linear power spectrum.
-
-Figure \ref{fig:pkhalofit_comp} shows the matter power spectrum at $z=1.69$ of our simulations before and after applying the PGD correction compared to analytic Halofit predictions (\denise{cita}(Smith et al.
-2003; Takahashi et al.
-2012)).
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/pkhalofit_comp.png}
-    \caption{
-    Upper panel: Comparison of the matter power spectrum of FlowPM before and after the PGD correction with reference matter power spectrum \textit{Halofit} at redshift $z = 1.69$.
-Lower panel: Fractional differences between FlowPM and Halofit.
+\subsubsection{Angular Cls
 }
-    \label{fig:pkhalofit_comp}
-\end{figure}
-
-In Figure \ref{fig:comp_kmap} we show an example of our convergence map at $ z= 1.034$, as well as the same map when the PGD correction is not applied. 
-We can see that the structures are not modified but simply sharpened.
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.9\textwidth]{paper/figures/kmap_compgd.png}
-    \caption{ \textbf{Left panel}: An example of our convergence map at source redshift $z= 1.034$.
-    \textbf{Right panel}: Same convergence map when the PGD correction is not applied.}
-    \label{fig:comp_kmap}
-\end{figure*}
-
-In Figure \ref{fig:ps_comp} in the upper panel, we present the DLL angular power spectrum complemented by the PGD scheme to a conventional DLL simulation with the same resolution.
-Both the outputs are compared to the analytic Halofit prediction for the angular power spectrum.
-In the lower panel the fractional differences between the our maps and the analytic Halofit prediction.
-Both the power spectra and ratios are averaged over $N = 100$ realisations.
-We can conclude that PGD scheme allows to achieve higher accuracy at the same computational cost.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/clshalofit_comp.png}
-    \caption{
-    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
-our DLL maps. \textbf{Lower panel}: Fractional differences between the
-DLL and Halofit power spectra for 3 source redshifts. The power spectra and ratios are means over 100 map realisations. The two vertical lines define the range of $\ell$ between $[300,3000]$.}
-    \label{fig:ps_comp}
-\end{figure}
-
-\subsection{Summary statistics}
-In this work, in order to extract the cosmological information from the simulated $\kappa-$maps, we use tree summary statistic for weak lensing observable: the angular power spectrum, the `starlet peak counts' and the `starlet $l_{1\text{norm}}$'.
-
-We reproduce the analysis choices of the LSST Y1 data. The DESC science requirements document can be found here \cite{mandelbaum2018lsst}.
-In particular we use a $n_{\text{eff}}=10$ galaxies per $\text{arcmin}^2$ for lensing sources and a $\sigma_e=0.26$ per component.
-
-\subsubsection{Lensing Angular Power Spectrum}
-Second order statistics, both in the form of shear 2-point correlation function $\xi_{\pm}(\theta)$, or its counterpart in Fourier space, the angular power spectrum $C_{\ell}$, have been widely used to extract the cosmological information from weak lensing mass maps.
+Second-order statistics, both in the form of shear 2-point correlation function $\xi_{\pm}(\theta)$, or its counterpart in Fourier space, the angular power spectrum $C_{\ell}$, have been widely used to extract the cosmological information from weak lensing surveys.
 \
-In the Limber approximation, the angular power spectrum of the convergence field can be computed as:
+In the Limber approximation, the angular power spectrum of the convergence field for a given tomographic bin can be computed as:
 \begin{equation}
@@
 
-In this paper, the angular power spectrum is computed from the noisy smoothed convergence maps: to each mock $\kappa$map we add Gaussian noise and than convolved it with a Gaussian smoothing kernel.
+The Intrinsic Alignment (IA) signal adds an excess correlation to the two-point shear correlation function (also known as cosmic shear GG or shear-shear correlation) with two terms: 1) the intrinsic-intrinsic (II) term, tracing the correlation of the intrinsic shape of two galaxies  and 2) and the intrinsic-shear coupling (GI) term, describing the correlation between the intrinsic ellipticity of one galaxy with the shear of another galaxy \citep{kilbinger2015cosmology}.
+% In the Limber approximation, the $C_{\ell}^{II}$ and $C_{\ell}^{GI}$ contributes can be computed from the matter power spectra:
+The matter power spectra for the IA terms are defined as:
+\begin{align}
+    P_{II}(k,z)=& \left ( \frac{A_{IA}\bar{C}_1\bar{\rho}(z)}{\bar{D}(z)} \right)^2 a^{4}(z)P_{\delta}(k,z) 
+    \\
+    P_{GI}(k,z)=&  \frac{A_{IA}\bar{C}_1\bar{\rho}(z)}{\bar{D}(z)} a^{2}(z)P_{\delta}(k,z),
+\end{align}
+where $\bar{D}(z) \equiv D(1+z)$ \citep{harnois2021cosmic}.
+\denise{Under the Limber
+approximation the projected angular power spectra for the IA terms become:
+\begin{align}
+    C_{II}=& \int_0^{\chi_{lim}} \text{d}\chi 
+    \frac{n^2(\chi)}{a^2(\chi)}P_{II}(k,\chi), \\
+    C_{GI}= \frac{3\Omega_m H_0^2}{2c^2} & \int_0^{\chi_{lim}} \text{d}\chi 
+    \frac{g(\chi)n(\chi)}{a(\chi)}P_{GI}(k,\chi).
+\end{align}
+}
 
-To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa$TNG simulations. 
- We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:clsktng_comp1arc}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/clsktng_comp1arc.png}
-    \caption{
-    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
-our DLL maps compared to the $\kappa$TNG predictions.
- \textbf{Lower panel}
-The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions.The shaded regions represent the standard deviation from 1000 $\kappa$TNG realisations. \\
- The power spectra mean over 100 map realisations.The maps are smoothed with a 1 arcmin Gaussian filter. }
-    \label{fig:clsktng_comp1arc}
-\end{figure}
-% with a smoothing size $\theta=3.6$. We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}. 
-\denise{draw conclusions from this plot}
-For each map, we compute the power spectrum by using our own code implemented in the Tensorflow framework.
-%and we take the average over 2000 maps realisation.
+\subsubsection{Wavelet peak counts}
+\paragraph{Wavelet Transform} The wavelet transform has been widely used in analysing astronomical images due to its ability to decompose astronomical data into components at different scales. 
+This multiscale approach is well-suited for the study of astronomical data since their complex hierarchical structure.
+\denise{A wavelet function $\psi(x)$ is a function that satisfies the admissibility condition:
+\begin{equation}
+    \int_{\mathbb{R}^{+}} |\hat{\psi}(k)|^2 \frac{dk}{k}<\infty,
+\end{equation}
+where we indicate with $\hat{\psi}(k)$ the Fourier transform of $\psi(x)$, with $\int\psi(x)dx=0$ in order to satisfy the admissibility condition. 
+A given signal is decomposed in a family of scaled and translated functions:
+\begin{equation}
+    \psi_{a,b}(x)=\frac{1}{\sqrt{a}}\psi \left( \frac{x-b}{a}\right),
+\end{equation}
 
-\subsubsection{Wavelet Peak Counts}
-It has been shown that it's necessary to go beyond second-order statistics to fully capture the non-Gaussian information encoded in the peak of the matter distribution.
-Several studies have proved that the  weak-lensing peak counts provide a way to capture information from non-linear structures that it is complementary to the information extracted by power spectrum.
-The peak counts identify region of weak lensing map where the density value is higher, in this way they rely to the massive structure.
-There are different ways to record the weak lensing peaks: the number of peaks as a function of either the signal-to-noise ratio or the convergence $\kappa$ of the peaks. 
-In this paper, we choose to bin the peaks as function of $\kappa$. 
-As for the angular power spectrum, the weak lensing peaks are detected from the noise and smoothed simulated maps by using our own code.
-%and by averaging over 2000 different realizations. 
-A peak is identified as the pixel of larger value than its eight neighbors in the image, convolved with a starlet filter $\mathcal{W}(\theta_{\text{ker}})$:
+where $\psi_{a,b}$ is the so-called \textit{daughter wavelets}, scaled and translated version of the \textit{mother} wavelet, with $a$ and $b$ scaling and translation parameters.
+The continuous wavelets transform is defined from the projections of a function $f \in L_2(\mathbb{R})$ onto the family of daughter wavelets.
+The coefficients of this projection represent the wavelet coefficient, obtained by :
 \begin{equation}
-    \textbf{Peaks}=(\kappa*\mathcal{W})(\theta_{\text{ker}})
+    W_f(a,b)=\int_{\mathbb{R}} f(x)\psi^{*}_{a,b}(x)dx=\frac{a}{\sqrt{a}}\int_{\mathbb{R}}f(x)\psi^{*}\left( \frac{x-b}{a}\right)dx ,
 \end{equation}
-Similar to the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG.
-This allow us to identify the bins to discard (bins where the distribution of peaks is not Gaussian) as well as, the wavelet scale to discard. 
-In Figure 6, we show the number counts of peaks in the upper panels, and the fractional differences between the DLL and $\kappa$TNG-Dark maps in the lower panels.
-Again we smooth the convergence maps with a 1 arcmin Gaussian filter. The peak are counted for 8 linearly spaced bins within the range $(\kappa*\mathcal{W})=[-0.2, 0.5]$. 
-%The bins are chosen such that at least 30 peaks are recorded in each bin.
+with $\psi^{*}$ the complex conjugate of $\psi$, and $ \forall a \in \mathbb{R}^{+}$, $ b \in \mathbb{R.}$  }
+In this work, we filter the original convergence maps with the starlet transform, an isotropic and undecimated (i.e.
+not down-sampled)  wavelet transform, suited for astronomical applications where objects are mostly more or less isotropic \citep{4060954}.
 
-\ref{fig:peakktng_comp1arc}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/peakktng_comp1arc.png}
-    \caption{
-      \textbf{Upper panel}: Peak counts from our DLL map at source redshift $z_s=1.034$ compared to the $\kappa$TNG at the same redshift.
-\textbf{Lower panel}: The fractional differences between the DLL and $\kappa$TNG map.
- The peak counts mean over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. }
-    \label{fig:peakktng_comp1arc}
-\end{figure}
+It decomposes an image $c_0$ as the sum of all the wavelet scales and the coarse resolution image $c_J$:
+\begin{equation}\label{wav_des}
+    c_0(x,y)=c_J(x,y)+\sum_{j=1}^{J_{max}} w_j(x,y)
+\end{equation}
+where $J_{max}$ is the maximum number of scales and $w_j$ is the wavelet images showing the details of the original image at dyadic scales with a spatial size of $2^j$ pixels and $j = J_{max} + 1$.
 
-\EiffL{Explain wavelets}
+The starlet wavelet function is a specific translational invariant wavelet transform:
+\begin{equation}
+   \frac{1}{4} \Psi \left ( \frac{x_1}{2}, \frac{x_2}{2} \right )=
+    \phi (x_1,x_2)- \frac{1}{4} \phi  \left ( \frac{x_1}{2},  \frac{x_2}{2} \right )
+\end{equation}
+specified by an isotropic scaling function $\phi$, that,  for astronomical application, can be defined as a B-spline of order 3:
+\begin{equation}
+\phi_{1D}(x)= \frac{1}{12} (|x-2|^3-4|x-1|^3+6|x|^3-4|x+1|^3+|x+2|^3 ).
+\end{equation}
+\denise{
+The N-dimensional scaling functions can be built starting from the separable product of N $\phi_{1D}$: $\phi(x_1,x_2)=\phi_{1D}(x_1)\phi_{1D}(x_2)$. }
+Each set of wavelet coefficients $w_j$ is obtained as the convolution of the input map with the corresponding wavelet kernel.
+For a full description of the starlet transform function, see \citet{4060954} and \citet{10.5555/1830428}.
 
-One of the difficulties with traditional peak counting is that it relies on building
+\paragraph{Peak counts}It has been shown that it is necessary to go beyond second-order statistics to fully capture the non-Gaussian information encoded in the peaks of the matter distribution 
+\citep{1997A&A...322....1B, 1997ApJ...484..560J,1999A&A...342...15V,2003A&A...397..809S}.
+Several studies have shown that the weak-lensing peak counts provide a way to capture information from non-linear structures that is complementary to the information extracted by power spectrum \citep{lin2015new, peel2017cosmological, ajani2020constraining, harnois2021cosmic, zurcher2022dark}.
+The peaks identify regions of weak lensing map where the density value is higher, in this way they are particularly sensitive to massive structures.
+There are two different ways to record weak lensing peaks: as 1) local maxima of the signal-to-noise field or 2) local maxima of the convergence field.
+In both cases, they are defined as pixels of larger value than their eight neighbors in the image.
+
+\section{Fast and Differentiable Lensing Simulations}\label{Fast_and_Differentiable_Lensing_Simulations}
+Analytical models with which to predict the observed signals do not exist for most higher-order summary statistics. 
+To circumvent this issue, one approach is to rely on generating a suite of numerical simulations.
+In the following section, we introduce our weak lensing map simulation procedure, including a description of the N-body simulator and the \denise{lightcone construction}.
+
+\subsection{Differentiable Particle-Mesh N-body simulations}
+\subsubsection{FastPM/FlowPM}
+
+Numerical simulations provide a practical way to model the highly nonlinear universe and extract cosmological information from observation at different scales.
+
+However, collision-less N-body simulations typically require significant computational effort in terms of time and CPU/GPU power, in particular, computing the gravitational interactions between the particles is typically the most time-consuming aspect and where most of the approximations are done.
+For that reason, several quasi N-body schemes have been developed to reduce the simulation time and the computational cost of full numerical simulations. 
+Our weak lensing simulation tool is mainly based on the FastPM algorithm \citep{2019ascl.soft05010F} and its FlowPM \citep{modi2021flowpm} implementation which provides a fast Particle-Mesh (PM) solver estimating the gravitational forces by computing Fast Fourier Transforms on a 3D grid.
+
+\subsection{Automatic differentiation through black-box ODE solvers}\label{Backpropagation_of_ODE_solutions}
+In this work, we extend the FlowPM approach by implementing the time integration of the Ordinary Differential Equations
+(ODEs) that describe the gravitational evolution of the particles in the simulation using a black-box ODE integrator.
+This is in contrast to the leapfrog integration method used in FastPM.
+One reason for this change is that adaptive ODE solvers are able to automatically adjust the time step of the simulation based on the desired accuracy for the result.
+Another reason for this approach is that modern automatic differentiation frameworks like TensorFlow provide automatically differentiable solvers which significantly reduce the memory footprint of the simulation when computing the gradients, as will be described below.
+
+We begin by describing the set of equations used in the simulation:
+\begin{equation}
+    \left\{ \begin{array}{ll}
+        \frac{d \mathbf{x}}{d a} & = \frac{1}{a^3 E(a)} \mathbf{v} \\
+        \frac{d \mathbf{v}}{d a} & =  \frac{1}{a^2 E(a)} F(\mathbf{x}, a), \\
+    \end{array} \right.
+\end{equation}
+with $\mathbf{x}$ and $\mathbf{v}$ the position and the velocity of the particles, \denise{\textit{a} the cosmological scale factor, $E(a)$ the ratio between the Hubble expansion rate and the Hubble parameter and $\mathbf{F}$ the gravitational force experienced by the dark matter particles in the mesh.}
+
+To evaluate the gradients of the solution with respect to input cosmological parameters, it is therefore necessary to  back-propagate through the ODE solver.
+Very recently the adjoint sensitivity method \cite{chen2018neural, pontryaginmathematical} has gained a lot of attention in the field of deep learning, as it allows to compute these gradients by solving a second ODE backward in time and treat the ODE solver as a black box.
+
+Consider an $\text{ODESolve}(\textbf{z}(t_0),f,t_0,t_1, \theta)$, 
+ where $z(t)$ is the state variable, $f$ the function modeling the dynamics, $t_0$ the start time, $t_1$ the stop time and $\theta$ the dynamic parameter. The function  $\mathcal{F}$ of its output
+ \begin{equation}
+     \mathcal{F}(\textbf{z}(t_1))=   \mathcal{F} (\text{ODESolve}(\textbf{z}(t_0),f,t_0,t_1, \theta)).
+ \end{equation}
+can be differentiated with respect to the input $\theta$.
+ First, we need to compute the \textit{adjoint} $\textbf{a}(t)=\partial \mathcal{F}/ \partial \textbf{z}(t)$, i.e. the gradient of $\mathcal{F}$ respect to the hidden state $\textbf{z}(t)$.  
+ Then, we can determine the dynamics of the adjoint through:
+ \begin{equation}
+     \frac{d \textbf{a}(t)}{dt}=-\textbf{a}(t)^{ \mathsf{T}}\frac{\partial f (\textbf{z}(t),t,\theta)}{\partial \textbf{z}}.
+ \end{equation}
+ Finally, we compute the gradients with respect to the parameters $\theta$ evaluating a third integral:
+ \begin{equation}
+     \frac{d\mathcal{F}}{d\theta}=
+     \int_{t_1}^{t_0} \textbf{a}(t)^{ \mathsf{T}}
+     \frac{\partial f (\textbf{z}(t),t,\theta)}{\partial \theta } dt.
+ \end{equation}
+All the integrals are evaluated in a single call to the ODE solver, and the Jacobian is computed by automatic differentiation.
+
+The choice to extend the FlowPM code with the ODE implementation is motivated by the fact that to compute the gradient of the forward model, the original algorithm needs to store all the intermediate steps of the simulations.
+This induces a memory overhead that scales with the number of time steps in the simulation.
+In the adjoint ODE approach, this is instead replaced by solving another ODE backward in time when evaluating the gradient.
+We illustrate the potential of differentiating through ODE solvers, highlighting the fact that the simulations and the gradients presented in this paper are computing using one single GPU for $128^3$ particles.
+
+\subsubsection{ Hybrid Physical-Neural ODE}\label{N_body_des}    
+PM simulations can be used as a viable alternative to full N-body to model the galaxy statistics and create fast realizations of large-scale structures at lower computational cost.
+Nevertheless, these kinds of simulations lack resolution on small scales and are not able to resolve structures with scales smaller than the mesh resolution.
+To compensate for
+the small-scale approximations and recover the missing power, we adopt an Hybrid Physical-Neural (HPN) approach presented in \citet{lanzieri2022hybrid}. 
+The correction scheme we implement consists in computing the short-range interaction as an additional force parameterized by a Fourier-space Neural Network.
+This residual force is modeled by applying a learned isotropic Fourier filter acting
+on the PM-estimated gravitational potential $\phi_{PM}$:
+\begin{equation}\label{hybrid_model}
+    F_\theta(\mathbf{x}, a) = \frac{3 \Omega_m}{2}  \nabla \left[ \phi_{PM} (\mathbf{x}) \ast \mathcal{F}^{-1}(1 + f_\theta(a,|\mathbf{k}|)) \right],
+\end{equation}
+where $\mathcal{F}^{-1}$ is the inverse Fourier transform and $f_\theta(a,|\mathbf{k}|)$ is a B-spline function whose coefficients are the output of the Neural Network of parameters $\theta$ trained using the CAMELS simulations \citep{villaescusa2021camels}.
+In particular,  we use a \textit{single} CAMELS N-body simulation at the fiducial cosmology of $h=0.6711$, $n_s =0.9624$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.30$, $\sigma_8= 0.8$.
+
+We adopt a loss function penalizing both the positions
+of the particles and the overall matter power spectrum at
+different snapshot times s:
+\begin{equation}\label{loss2}
+    \mathcal{L} =  \sum_{s} || \mathbf{x}^{Camels}_s - \mathbf{x}_s ||_2^2  + \lambda || \frac{P_s(k)}{P_s^{Camels}(k)} -1 ||_2^2 \; ,
+\end{equation}
+where $\lambda$ is an hyper-parameter balancing the
+contributions of the two terms.
+\denise{By comparing the results obtained from different values of $\lambda$ in the fiducial setting and outside the training regime, we find that $\lambda= 0.1$ provided the optimal balance in terms of overall correction and overfit.
+}
+
+In \citet{lanzieri2022hybrid} we tested the robustness of the HPN correction scheme to changes in resolution and cosmological parameters, i.e.
+we applied the correction parameters found with the setting described above to simulations of larger volume or different $\Omega_m$ and $\sigma_8$.
+We observed that most of the missing power that characterizes the matter power spectrum in the PM approximation is still recovered when the HPN correction is applied to simulations different from the ones used to train the Neural Network.
+So, from these tests, we can conclude that the HPN is still robust to differences among simulation settings.
+
+\subsection{Differentiable Lensing Simulations}
+To extract the lens planes and construct the lightcone, we export 11 intermediate states from the N-body simulation of a fixed interval of 205 $h^{-1}$ Mpc in a redshift range between $z=0.03-0.91$. 
+To recover the redshift range of the lightcone, one unit box is replicated using periodic boundary conditions.
+First, we generate rotation matrices along the three axes, hence, each snapshot is rotated around each of the three axes, finally, all the particles are randomly shifted along the axes.
+To obtain the final density field, each snapshot is projected in a 2D plane by estimating its density with a  cloud-in-cell (CiC) interpolation scheme \citep{hockney1988computer}.
+After creating a Cartesian grid of coordinates, each slice is interpolated onto sky coordinates.
+\denise{.
+This procedure differs from the one implemented in the MADLens package \citep{bohm2021madlens}.
+In MADLens the lightcone is built by translating the redshift of the particles into distances, then the particles are projected onto the convergence map at the proper evolution step corresponding to that distance.}
+
+\subsubsection{Implementation of Born lensing}
+We generate the convergence map by integrating the lensing density along the unperturbed line of sight, i.e.
+applying the Born approximation \citep{schneider2006weak}.
+In particular we discretize the \autoref{born_approx} such that it becomes:
+\begin{equation} 
+    \kappa_{born}= \frac{3H_0^2 \Omega_m}{2c^2}
+    \sum_i 
+    \bar{\delta_i} \left ( 1-\frac{\chi_i}{\chi_s}\right)
+    \left (  \frac{\chi_i}{a_i}\right)
+     \Delta \chi
+\end{equation}
+where the $i$ index runs over the different lens planes, the $\bar{\delta_i}$ indicates the matter overdensity projected into the lightcone, $\chi_s$ defines the comoving distance of the source and $\Delta \chi$ is the  width of the lens plane.
+
+\subsubsection{Implementation of IA with NLA }
+We model the effect of IA on the convergence map level following the model proposed by  \citet{fluri2019cosmological}.
+This allows us to create pure IA convergence maps to combine with shear convergence maps in order to generate a contaminated signal.
+Following \cite{harnois2021cosmic}, the Fourier transform of the intrinsic ellipticities can be phrased as: 
+\begin{align}\label{trans_ell}
+    \tilde{ \epsilon}_{1}^{IA}(\textbf{k}_{\bot}) & \propto
+    \left ( \frac{k_x^2-k_y^2}{k^2} \right )  \tilde{\delta}_{2D}(\textbf{k}_{\bot})
+   \mathcal{G}_{2D}(\sigma_g) \\
+       \tilde{ \epsilon}_{1}^{IA}(\textbf{k}_{\bot}) & \propto
+    \left ( \frac{k_x k_y}{k^2} \right )  \tilde{\delta}_{2D}(\textbf{k}_{\bot})
+   \mathcal{G}_{2D}(\sigma_g), \nonumber
+\end{align}
+where $\sigma_g$ defines the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $\sim $ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
+Combing \autoref{complex_e} and \autoref{trans_ell} we can calculate the intrinsic alignment as part of the convergence map:
+\begin{equation}\label{IA_maps}
+    \kappa_{IA_{i}}= 
+    - A_{IA}\bar{C}_1\rho_c \Omega_m
+    \int_{z_{min}}^{z_{max}} 
+    n_{i}(z) \delta_{s_{i}}
+    \frac{ dz}{D(z)}
+\end{equation}
+where the index \textit{i} refers to the \textit{i}-th redshift bins.
+
+\subsubsection{Differentiable Peak Counts}
+One of the difficulties in estimating derivatives of traditional peak count statistics is that it relies on building
 an histogram of peak intensities, and histograms, due to the discrete nature of the bins, are not differentiable.
@@
 As a continuous equivalent to an histogram, KDEs are differentiables and can just as well be used to define the peak counts statistic.
+We define the KDE for the peak counts as:
+\begin{equation}
+   \text{KDE}= \frac{1}{ b_w \sqrt{2\pi}} \exp{\left ( -\frac{(X-x)^2}{2 b_w^2} \right )}
+\end{equation}
+where $b_w$ is the smoothing bandwidth parameter, \textit{X} is the number of peaks in a given bin, and \textit{x} is the center of each bin.
 
-\subsubsection{Wavelet $\ell_1-$norm}
+This procedure yields a peak count statistic that is smoothly differentiable with respect to the input map and thus can be used for applications such as Fisher forecasting as discussed later in this paper.
 
-\ref{fig:l1normktng_comp1arc}.
+\section{Validating simulations for LSST}\label{Validating_simulations_for_LSST_Y}
+In this section, we compare the results from our simulation to other works, including the analytic models for the matter power spectrum \textit{Halofit} \citep{smith2003stable,takahashi2012revising} and the cosmological N-body simulations, $\kappa$TNG \citep{osato2021kappatng}.
+
+The $\kappa$TNG simulations is a suite of publicly available weak lensing mock maps based on the cosmological hydrodynamical simulations IllustrisTNG, generated with the moving mesh code AREPO \citep{2010MNRAS.401..791S}.
+In particular, we use the $\kappa$TNG-Dark suit of maps based on the corresponding dark matter-only TNG simulations. 
+The simulations have a side length of the box equal to 205 Mpc/h and $2500^3$ CDM particles.
+To model the propagation of light rays and simulate the weak lensing maps, a multiple-lens plane approximation is employed. 
+The simulation configuration consists of a map size of $5\times5$ deg$^2$, $1024\times 1024$ pixels and a resolution of 0.29 arcmin/pixel. 
+For a complete description of the implementation see \cite{osato2021kappatng}.
+
+To produce our simulations, we follow the evolution of $128^3$ dark matter particles in a periodic box of comoving volume equal to $205^3$ ($h^{-1}$ Mpc)$^3$, with initial conditions generated at z=6 using the linear matter power spectrum as implemented by \cite{eisenstein1998baryonic}.
+In particular, we implement the  Eisenstein-Hu transfer function in the Tensorflow framework, in order to compute its gradients automatically.
+
+We assume the following cosmological parameters: $h=0.6774$, $n_s =0.9667$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.3075$, $\sigma_8= 0.8159$, such that they match the results of Planck 2015 \citep{ade2016planck}.
+We reproduce the same configuration of $\kappa$TNG, i.e. each map is on a regular grid of $1024^2$ pixels and $5\times 5$ deg$^2$.
+
+The actual choice of bins to include in the forecasting is made following the DESC data requirement for the angular power spectra \citep{mandelbaum2018lsst}, i.e.
+adopting $\ell_{max,shear} = 3000$ and  $\ell_{min,shear} = 300$.
+
+\subsection{HPN validation }
+To compensate for the small-scale approximations resulting from PM, we applied the HPN approach presented in \autoref{N_body_des}. 
+We show on \autoref{fig:pkhalofit_comp} the power spectrum  and the fractional power spectrum of PM simulations before and after the HPN correction compared to analytic Halofit predictions \citep{smith2003stable, takahashi2012revising} for redshift $z=0.03$ and $z=0.91$.
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/l1normktng_comp1arc.png}
+    \includegraphics[width=\columnwidth]{paper/figures/residual_pk_z0_zoom.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/residual_pk_z1_zoom.pdf}
     \caption{
-      \textbf{Upper panel}: $l_1$norm from our DLL map at source redshift $z_s=1.034$ compared to the $\kappa$TNG at the same redshift.
-\textbf{Lower panel}: The fractional differences between the DLL and $\kappa$TNG map.
- The $l_1$norm mean over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. }
-    \label{fig:l1normktng_comp1arc}
+     Matter power spectrum and fractional matter power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the theoretical halofit model for redshift z=0.03 (upper panel) and redshift z=0.91 (lower panel).
+The power
+spectra and ratios are means over 100 independent map realisations. The shaded regions represent the standard deviation from 100 independent DLL realisations.
+    }
+    \label{fig:pkhalofit_comp}
 \end{figure}
+ We observe a bias between our measured power spectrum and the theoretical prediction at low $k$.
+This reduced power is explained by the small box size of our simulation and the associated reduced number of large-scale modes.
+At redshift $z=0.91$ most of the missing
+power is recovered by the HPN correction up to $k \sim 1$, after which the method overemphasizes the small-scale power.
+\denise{In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.}
 
-\EiffL{Explain what's the deal with this l1 norm}
+At redshift $z=0.03$, the correction model does not improve significantly the results.
 
-\section{Systematic effects}
-Many systematic effects can influence the outcome of cosmic shear analysis and bias cosmic shear results. 
-In this work we incorporate a treatment of the galaxy intrinsic alignment and photometric redshift uncertainty.
-In the following, we introduce an overview of these systematics and outline how we incorporate in our analysis.
-
-\subsection{Photometric redshift uncertainty}
-Cosmic shear measurement require a large number of images, for such quantities, determining the redshift of the galaxies spectroscopically is not possible, for this reason, photometric redshift (''photo-z'') measurement are computed.
-In this paper we use the Fisher formalism to investigate its impact on cosmological parameter estimation.
-For our analysis we considered a Smail-type galaxy distribution p(z) (Smail et al. 1994),
-\begin{equation}\label{photz}
-    p(z) \propto z^{\alpha} e^{-(\frac{z}{z_0})^{\beta}}
-\end{equation}
-
- We adopt  $\alpha=$, $\beta =$ and fix $z_0$ such that ?'
-
- We take into account the uncertainty of the redshift distributions by introducing  a shift of the distributions defined by Eq.\ref{photz} according to the nuisance parameters $\Delta_z$:
- \begin{equation}
-     n'_i(z)= n_i(z-\Delta_z)
- \end{equation}
-
-\subsection{Galaxy intrinsic alignment}
-
-The galaxy ellipticity observed by a telescope is the combination of the cosmic shear signal $\gamma$ and the intrinsic shape of the source $\epsilon_{int}$, the latter can be further decomposed into the alignment term $\epsilon_{IA}$ and the random component $\epsilon_{ran}$.
-
-Several theoretical models have been proposed to described the physics of IA, such as the Non-Linear tidal Alignment model (e.g.
-in Bridle et King 2007), the tidal torquing model (described in Hirata et Seljak 2004; Catelan et al.
-2001), or the combination of both (the Tidal Alignment and Tidal Torquing model, see Blazek et al.
-2019).
-
-The NLA model describes the IA as a linear coupling between the intrinsic galaxy shapes and the non-linear large projected tidal fields, the "non-linear" definition arises from the use of the non linear matter power spectrum in the computation.
-
-The IA signal can be decomposed into two components: 1) the intrinsic-intrinsic (II) term, describing the correlation of intrinsic ellipticities of two galaxies $i$ and $j$ and 2) intrinsic-shear coupling (GI) term, describing the correlation between the intrinsic ellipticity of one galaxy with the shear of another galaxy (\cite{kilbinger2015cosmology}).
-
-The first step to introduce the IA term in our simulation, consists in computing the projected tidal field from the three-dimensional mass over-density field $\delta(\vec{x}$
-as (\cite{harnois2021cosmic})
-\begin{equation}
-   \tilde{s}_{ij,2D}(\textbf{k}_{\bot})=
-   2 \pi 	\left [ \frac{k_ik_j}{k^2}- \frac{1}{3} \right ]
-   \tilde{\delta}_{2D}(\textbf{k}_{\bot})
-   \mathcal{G}_{2D}(\sigma_g)
-\end{equation}
-where $\sigma_g$ is the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $~$ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
-In this work we use a Gaussian kernel and set the values of $\sigma_g=(idk yet) h^{-1}$Mpc.
-First of all, we computed the Fourier transform of the projected density field from the full boxes of the simulation. 
-Then the smoothed tidal field is interpolated on the light-cone. 
-Then, we couple the tidal field $s_{ij,2D}$ with the complex intrinsic ellipticities as (\cite{harnois2021cosmic}):
-\begin{equation}
-    \epsilon_{1}^{IA}=\frac{A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} (s_{xx}-s_{yy}), \ \ 
-      \epsilon_{2}^{IA}=-\frac{2A_{IA\bar{C}_1\bar{\rho}(z)}}{D{z}} s_{xy},
-\end{equation}
-(\denise{check this formula})
-and compute the observed ellipticities as:
-\begin{equation}
-    \boldsymbol{\epsilon}^{obs}=
-    \frac{\boldsymbol{\epsilon}^{int}+\textbf{g}}{1+\boldsymbol{\epsilon}^{int,*}\textbf{g}}, \ \  \text{with}  \ \
-    \boldsymbol{\epsilon}^{int}=
-    \frac{\boldsymbol{\epsilon}^{
-     IA}+\boldsymbol{\epsilon^{ran}}}
-     {1+\boldsymbol{\epsilon}^{IA,*}\boldsymbol{\epsilon^{ran}}}.
-\end{equation}
+In \autoref{fig:comp_kmap} we show an example of our convergence map at $ z= 0.91$, from pure PM simulation (first panel) and the HPN corrected simulation (second panel).
+The HPN model sharpens structures in the lensing field without introducing any artifacts.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{paper/figures/kmap_dll_vs_hpn.pdf}
+    \caption{ \textbf{Left panel}: Convergence map at source redshift $z= 0.91$ from DLL, PM only.
+    \textbf{Right panel}: Same convergence map when the HPN correction is applied. 
+    }
+    \label{fig:comp_kmap}
+\end{figure*}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/peakcounts.png}
-    \caption{Comparison of traditional histogram-based peak counts, against our  KDE-based peak counts statistic. The two statistics are similar, but our KDE-based statistics is differentiable.}
-    \label{fig:comp_statistics}
+    \includegraphics[width=0.95\columnwidth]{paper/figures/cls_DLL_vs_ktng_hpn.pdf}
+        \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_hpn.pdf}
+    \caption{
+    \textbf{Upper panel}: Angular power spectra of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model compared to the $\kappa$TNG prediction.
+\textbf{Lower panel}: fractional angular power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the $\kappa$TNG prediction.
+The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the standard deviation from 100 DLL realisations.
+The spectra are computed for the source redshift $z_s=0.91$.
+}
+    \label{fig:ps_comp}
 \end{figure}
 
-\section{Fisher Forecast}
+In the upper panel of \autoref{fig:ps_comp}, we present the angular power spectrum computed from our Differentiable Lensing Lightcone (DLL hereafter) complemented by the HPN scheme and a conventional DLL simulation with the same resolution.
+Both the outputs are compared to the $\kappa$TNG prediction.
+In the lower panel  of \autoref{fig:ps_comp} the fractional differences between the convergence power spectra from the two maps and the $\kappa$TNG are shown.
+Both the power spectra and ratios are averaged over $N = 100$ realisations.
+We can see that the HPN  model reduces the relative deviations of the angular power spectra to within 30\%. 
+We also observe a perfect match at large scales, since the $\kappa$TNG and the DLL simulations have the same box size of 205 Mpc/h$^3$.
+
+\subsection{IA validation}
+In the upper panel of  \autoref{fig:ia_validation}, we present the $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes from our DLL simulations compared to theoretical Halofit predictions \citep{smith2003stable}.
+In the lower panel of the same figure, we show the fractional differences between the mentioned contributions.
+To validate the IA infusion, only for this experiment, we run simulations keeping the term $A_{IA}=1$. 
+As we can see, the fractional difference for the $C_{\ell}^{II}$ term features uncertainty consistent with $C_{\ell}^{GG}$ term, validating our infusion process. 
+The signal is computed for the source redshift $z_s=0.91$ and is averaged over 100 realizations.
+ The theoretical predictions are computed using the public \href{https://ccl.readthedocs.io/en/latest/}{Core Cosmological Library} (CCL, \citet{chisari2019core}). 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{paper/figures/IA_validation.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/IA_validation_res.pdf}
+    \caption{ \textbf{Upper panel}: The $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributions from theoretical predictions (dashed line) and DLL simulations. \\
+     \textbf{Lower panel}: The fractional difference between the theoretical and simulated $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes.
+     We can see that we measure a reduced power spectrum at low $\ell$ compared to the theoretical predictions.
+This can be explained by the small volume of our simulation and the related low number of large-scale modes.
+     The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the standard deviation from 100 realisations.}
+    \label{fig:ia_validation}
+\end{figure}
+
+\subsection{Lensing $C_\ell$}
+To quantify the accuracy of the simulations we aim to reproduce the summary statistics from the Dark Matter Only $\kappa$TNG simulations. 
+We compare the results from the angular power spectrum for different source redshift, just investigating how well we can recover the power spectrum for a given source plane.
+The results of the angular power spectrum from the sources redshift z=[0.25,0.46,0.65,0.91,1.30] are shown in the upper panel of \autoref{fig:clsktng_comp}, as well as the fractional differences between the $\kappa$TNG and DLL maps in the lower panel.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{paper/figures/cls_DLL_vs_ktng.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng.pdf}
+    \caption{
+    \textbf{Upper panel}: Angular power spectra for 5 source redshift from
+our DLL maps compared to the $\kappa$TNG predictions.
+ \textbf{Lower panel:} Fractional angular power spectra of DLL simulations and $\kappa$TNG simulations for different source redshift.
+  The power spectra mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
+     \label{fig:clsktng_comp}
+\end{figure}
+We observe that the differences for $z_s=0.91$ and  $z_s=1.30$ curves are within $10\%$ of accuracy for scales larger than $\ell=1000$, within $25\%$  for scales $1000<\ell<2000$ and  within $25\%$ and $45\%$ for scales $2000<\ell<3000$.
+For lower source redshifts the deficit of power in our simulations becomes worse.
+This can be explained considering that a given value of $\ell$ at lower redshift corresponds to smaller scales, some of those below the resolution of our simulations.
+We conclude that, if for z=0.91 and z=1.30 we have a general agreement with $\kappa$TNG, with this specific setting of the model, we can not model correctly cases with sources redshift lower than z=0.91.
+
+ We want to highlight that the results shown are produced keeping the resolution of the simulations extremely low, and we do not aspect to get the same precision as $\kappa$TNG.
+The purpose of these tests, and the overall goal of the paper, is to present a proof of concept of the DLL package and its potential.
+In practice, we will not work at this resolution.
+
+Nevertheless, note that the simulations presented here already achieve a similar resolution of the MassiveNus simulations \citep{liu2018massivenus}, despite being generated using one single GPU.
+
+\subsection{Peak counts}\label{peak_sec}
+We compute the starlet peak counts as wavelet coefficients with values higher than their eight neighbors. 
+We define $J_{max}=7$ in \autoref{wav_des}, this starlet filter applied to our map with a pixel size of 0.29 arcmin, corresponds to a decomposition in 7 maps of resolution [0.59, 1.17, 2.34, 4.68, 9.33, 18.79, 37.38] arcmin and a coarse map.
+To satisfy the survey requirement and keep the analysis centred in the range $\ell=[300, 3000]$, we consider only the scales corresponding to [9.33, 18.79, 37.38] arcmin.
+The peaks are counted for 8 linearly spaced bins within the range $(\kappa*\mathcal{W})=[-0.1, 1.]$.
+
+As for the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different redshift bins.
+We present the results in \autoref{peaks_z}.
+These results are shown in terms of S/N, where the signal to noise is defined as the ratio between the amplitude of wavelet coefficients over the standard deviation of the noise expected for our survey choice in each wavelet band.
+At wavelet scale $\theta=9.33$ arcmin the differences for the $z_s=0.91$ curves are within the $20\%$ up to $S/N=3$, for $S/N>3$ the accuracy is between the $20\%$ and the $50\%$.
+At larger scale, $\theta=18.79$ arcmin the accuracy is within the $20\%$.
+Finally, at $\theta=37.38$ arcmin the accuracy is within the $15\%$, except $S/N<1$ where the accuracy decreases up to $28\%$.
+The results slightly improve for z=1.30, showing an accuracy within the $35\%$ for scale $\theta=9.33$ arcmin,  within the $10\%$ for $\theta=18.79$ arcmin and $25\%$ for $\theta=37.38$ arcmin.
+ As for the power spectrum case, we observe higher discrepancies at lower redshift, hence we can conclude that, with the current setting of our simulation, we can not model correctly such redshift.
+
+\begin{figure}\label{peaks_z}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/res_peak_DLL_vs_ktng.pdf}
+    \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations for different sources redshift.
+The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmins (lower panel).
+  The results mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
+\end{figure}
+
+\section{Application: Fisher forecast
+}\label{Application_Fisher_forecast_for_HOS}
+As an example of application of differentiable simulations, we aim to investigate the degeneracy between the cosmological parameters in high dimensional space and when systematics, such as the intrinsic alignment, are included in the analysis.
+Thanks to automatic differentiation,
+taking the derivative through the simulation with respect to the initial cosmological and nuisance parameters is now possible, thus allowing, among other things, for Fisher forecasts.
+In this section, we briefly introduce the Fisher forecast formalism. We also describe in detail the specific choices for the analysis we use throughout.
+
+\subsection{Forecast formalism}
 Fisher forecast is a widely used tool in cosmology for different purposes, e.g.
-investigate the impact of systematic sources.
-It can be thought as a tool to forecast error from a given experimental set up e quantify how much information we can extract from it.
-
-Compared to other methods, such as the Markov chain Monte Carlo method, is extremely fast, however, several issues have to be taken into account. 
-The Fisher matrix is defined as the expectation value of the Hessian matrix of the likelihood $\mathcal{L}(C(\ell);\theta)$:
+investigate the impact of systematic sources or forecast the expected constraining power of the analysis \citep{tegmark1997karhunen}.
+It can be thought as a tool to forecast error from a given experimental setup e quantify how much information we can extract from it.
+The Fisher matrix is defined as the expectation value of the Hessian matrix of the negative log-likelihood $\mathcal{L}(C(\ell);\theta)$:
 \begin{equation}
@@
     {\partial \theta_{\alpha}\partial \theta_{\beta}}
-    \right \rangle .
+    \right \rangle \;,
 \end{equation}
-
 where we indicate with $\theta$ the cosmological parameters or any systematics included in the simulation.
@@
 \end{equation}
-were we indicate as $ \frac{\partial \mu}{\partial \theta_{\alpha}} $ the derivatives of the summary statistics evaluated at the fiducial parameter values.
-In this paper, to compute the covariance matrix $C_{ij}$, we use 2000 independent simulations at the fiducial cosmology. 
+were we indicate as $ \frac{\partial \mu}{\partial \theta_{\alpha}} $ the derivatives of the summary statistics w.r.t the cosmological or nuisance parameters evaluated at the fiducial values.
+So, under the assumption of Gaussian likelihood, the Fisher information matrix provides a lower bound on the expected errors on cosmological parameters.
+
+\subsection{Analysis choices} \label{Analysis_choices}
+
+To perform our study we use a single source redshift at z=0.91. Specifically, we generate 5000 independent map realisations to which we add Gaussian noise with mean zero and variance:
+ \begin{equation}
+     \sigma^2_n= \frac{\sigma_e^2}{A_{pix}n_{gal}},
+ \end{equation}
+where we set the shape noise $\sigma_e = 0.26$, the pixel area \denise{$A_{pix}=0.29$ arcmin$^2$ and the galaxy number density $n_{gal}=20$ arcmin$^{-2}$. } 
 We assume a parameter-independent covariance matrix computed as:
+\begin{equation}\label{covariance_matrix}
+    C_{ij}=\sum_{r=1}^N
+    \frac{(x_i^r-\mu_i)(x_j^r-\mu_j)}{N-1}
+\end{equation}
+where $N$ is the number of independent realizations, $x_i^r$ is the value of the summary statistics in the $i^{th}$ bin for a given realization $r$, and $\mu$ is the mean of the summary statistics over all the realization in a given bin.
+In addition, we adopt the estimator introduced by \cite{hartlap2007your} to take into account the loss of information caused by the finite numbers of bins and realizations, i.e.
+we compute the inverse of the covariance matrix as :
 \begin{equation}
-    C_{ij}=\sum_{r=1}^N
-    \frac{(x_i^r-\mu_i)(x_i^r-\mu_)}{N-1}
+    C^{-1}=\frac{N-n_{bins}-2}{N-1}C_{*}^{-1},
 \end{equation}
-where $N$ is the number of independent realizations and $x_i^r$ is the value of the summary statistics in the $i^{th}$ bin for a given realization $r$ and $\mu$ is the mean of the summary statistics over all the realization in a given bin.
-Furthermore, we scale the covariance matrix by the ratio $f_{\text{map}}/f_{\text{survey}}$, where $f_{\text{map}}$ is the angular extend of our $\kappa$map and $f_{\text{survey}}$ is the étendue of the \textit{Vera C.
-Rubin Observatory}.
-The derivatives of the summary statistics in the Eq.\ref{Fisher_matrix} are computed averaging over 250 independent fiducial simulations.
+where $C_{*}$ is the covariance matrix defined in \autoref{covariance_matrix}. 
+As mentioned before, we want to focus on a fair comparison between the power spectrum and the peak counts method.
+To be sure we are considering the same scales for both statistics, we apply a wavelet pass-band filter to the maps to isolate particular scales before measuring the power spectrum.
+We use the same scales used for the Peak counts, i.e.
+we decompose the noisy convergence map in seven images, we sum back only the three maps corresponding to [9.33, 18.79, 37.38] arcmin and compute the angular $C_{\ell}$ on the resulting image.
+An example of the $C_{\ell}$ computed for each individual starlet scale image and for the summed image is depicted in \autoref{window}.
 
-\section{Results}
+For each map, we compute the angular power spectrum and the peak counts by using our own differentiable code implemented in the TensorFlow framework. \footnote{
+Code publicly available at: \\ \href{https://github.com/LSSTDESC/DifferentiableHOS/tree/main/DifferentiableHOS/statistics}{https://github.com/LSSTDESC/DifferentiableHOS/statistics}  }
+\begin{figure}\label{window}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{paper/figures/window.pdf}
+    \caption{Example of the filtered $C_{\ell}$ used for the analysis.
+The colored lines show the $C_{\ell}$ computed on maps with a different resolution of the starlet decomposition.
+Specifically: the blue line (multiscale map) corresponds to $C_{\ell}$ computed on the summed image, the black dashed line (Original map) corresponds to the standard $C_{\ell}$ computed from a non-filtered map.
+}
+     \label{fig:window}
+\end{figure}
 
-\section{Discussion}
+The derivatives with respect to all parameters are evaluated at the fiducial cosmology as the mean of 1500 and 2600 independent measurements for the peak counts and the $C_{\ell}$ respectively.
+Indeed, while the peak counts reach the convergence with $\sim$ 1500 simulations, the $C_{\ell}$ proves to be more sensitive to noise and thus, requires more realizations to convergence.
+In \autoref{fig:Fisher_stab} in appendix B we test the stability of the Fisher contours by changing the number of simulated maps used to compute the jacobian.
 
-\subsection{Future directions}
+The priors used in the forecast process, are listed in \autoref{tab:prior} following \citet{zhang2022transitioning}.
+To take into account the partial coverage of the sky, we scale the Fisher matrix by the ratio $f_{\text{map}}/f_{\text{survey}}$, where $f_{\text{map}}$ is the angular extend of our $\kappa$map $f_{\text{map}}=25$ deg$^2$ and $f_{\text{survey}}$ corresponds to the size of the convergence maps for Stage IV-like survey $f_{\text{survey}}=15000$ deg$^2$.
 
-\section{Conclusions}
+\subsection{Results} 
+We now compare the relative constraining power of the two statistics described in \autoref{stat} using the Fisher matrix formalism. 
+As mentioned before, our interest is to investigate the sensitivity of the two weak-lensing statistics when systematic, such as the intrinsic alignment, and more cosmological parameters are included in the forecast.
+The results presented here are obtained from one single source redshift at z=0.91, assuming the fiducial cosmology and survey requirement presented in \autoref{Validating_simulations_for_LSST_Y} and \autoref{Analysis_choices}.
+The fiducial and priors ranges of the parameters are listed in \autoref{tab:prior}.
 
+\autoref{fig:Fisher_result} shows the $2\sigma$ contours on the full $\Lambda$CDM parameter space and intrinsic alignment term considered for the two analyses. 
+The contours obtained by the angular $C_{\ell}$ analysis are plotted in grey, the ones for the peak counts in yellow. 
+We find that in constraining $\Omega_c$, $\sigma_8$ and $A_{IA}$ peak counts outperform the power spectrum, while $h$, $n_s$ and $\Omega_b$ parameters, within the limit of our setting, are not constrained by either and are prior dominated.
+
+This is an interesting result, confirming the higher constraining power of weak-lensing peak counts as found in \cite{ajani2020constraining}, especially considering that the two studies differ in multiple aspects.
+The most important difference between these two analyses is the parameters they include.
+Whereas \cite{ajani2020constraining} derive constraints on the sum of neutrino masses $M_{\nu}$, the total matter density $\Omega_m$, and the primordial power spectrum normalization $A_s$, we include the five cosmological parameters of the $\Lambda$CDM model and intrinsic alignment amplitude.
+The constraining power of the peak count statistic keeps being higher even in high dimensional cosmological parameter space and when the intrinsic alignment is included.
+
+The chosen angular scales differ as well.
+\cite{ajani2020constraining} consider angular scales in the range $l = [300,5000]$, while we focus, for both multiscale peak counts and $C_{\ell}$, on scale approximately corresponding to the range $l = [300,3000]$.
+Despite we are neglecting scales $\ell>3000$, containing a larger amounts of
+non-Gaussian information, we find that for mildly non-linear scales we are considering, the peak counts statistic still constrains the cosmological parameters the most.
+
+\begin{table}
+	\centering
+	\caption{ Prior and fiducial values used for the forecasting.}
+	\begin{tabular}{lcc} 
+		\hline \hline
+		Parameter  & Prior & Fiducial value \\
+		$\Omega_c$ & $\mathcal{N}$ (0.2589,0.2) & 0.2589 \\
+		$\Omega_b$ & $\mathcal{N}$ (0.0486,0.006) & 0.0486 \\
+		$\sigma_8$ & $\mathcal{N}$ (0.8159,0.14) & 0.8159 \\
+		h & $\mathcal{N}$ (0.6774,0.063) & 0.6774\\
+		$n_s$ & $\mathcal{N}$ (0.9667,0.08) & 0.9667 \\
+		$A_{IA}$ &  $\mathcal{N}$ (0,3) &  0.0 \\
+		\hline
+	\end{tabular}
+	\label{tab:prior}
+\end{table}
+Finally, we find that the contours on the galaxy intrinsic alignment are significantly better constrained by the peak counts.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{paper/figures/Fisher_n.pdf}
+    \caption{$2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
+The constraints are obtained by applying the starlet Peak counts (yellow contours) computed on noisy maps filtered using a starlet kernel of [$9.33, 18.70, 37.38$] arcmin together and the wavelet pass-band filter for the $C_{\ell}$ statistics (grey contours) as described in \autoref{Validating_simulations_for_LSST_Y}.
+The dashed black lines are located at the fiducial parameter values.}
+     \label{fig:Fisher_result}
+\end{figure*}
+
+\section{Discussion}\label{Discussion}
+In this section, we discuss the limitations of the methodology and results obtained in this paper highlighting in particular strategies for future extensions and  applications.
+
+In this work, we only used a single source plane in our Fisher forecast analysis, which does not allow us to evaluate the full impact that IA would have in a tomographic analysis.
+In particular, we do not have a contribution from the GI term.
+Many studies have demonstrated that the tomographic analysis can significantly improve constraints on cosmological and IA parameters.
+\citep{king2003separating, heymans2004weak, troxel2015intrinsic}.
+Although it is straightforward to generalize all the results shown in this paper to the tomographic case, this will require increasing the resolution of the simulation at lower redshifts (as illustrated by \autoref{fig:clsktng_comp}) in order to model correctly low redshift bins.
+\denise{Since the maximum number of particles we can adopt in a simulation is closely limited to the GPU memory, we are building a distributed implementation of DLL, which will allow us to increase the resolutions of the simulations to the point of modeling correctly even the smaller scales at the lower redshifts.
+}
+
+Another direction for further development is the ray tracing methodology.
+In our method, we construct the weak lensing maps assuming the Born approximation.
+However, \cite{petri2017validity} shows that for an LSST-like survey, while the Born approximation leads to negligible parameter bias for the power spectrum, it can lead to significant parameter bias for higher-order statistics.
+Hence, the natural next step will be to implement a ray-tracing algorithm beyond the Born approximation in our pipeline.
+\denise{ We aim to adopt the multiple-lens-plane approximation \citep{1986ApJ...310..568B, Stella_Seitz_1994, jain2000ray, Vale_2003, refId0}, i.e.
+by introducing lens planes perpendicular to the line-of-sight, the deflection experienced by the light rays due to the matter inhomogeneities will be approximated through multiple deflections at the lens planes.
+More specifically, we will implement the memory-efficient ray-tracing scheme proposed by \cite{refId0} in the Tensorflow framework.}
+
+On the theoretical modeling side, we studied the impact of the intrinsic alignment of galaxies assuming a linear coupling between the intrinsic galaxy shapes and the non-linear projected tidal fields, i.e.
+adopting the NLA model.
+This physical description for the IA is only an approximation since it does not take into account the tidal torque field.
+In future work, we aim to extend the NLA model by implementing the extended $\delta$NLA model, described by \cite{harnois2021cosmic}.
+
+Finally, we presented a tool based on only Dark matter simulations.
+We note that this would force us to perform conservative scale cuts in the inference analysis to not include scales affected by baryonic effects.
+ A future prospect is to include baryonic effects in the analysis.
+One possible way applicable to our methodology  could be to extend the Hybrid Physical Neural ODE approach and apply more sophisticated models to learn the physics that controls the hydrodynamics simulations.
+
+We expect that the methods illustrated in this paper will be extended to different relevant use-cases.
+A particularly suitable example is related to the application of algorithms such as the Variational Inference and the Hamiltonian Monte Carlo that are widely used in the Bayesian inference context and were until now excluded due to the lack of derivatives.
+A further example is provided by \cite{zeghal2022neural}, which demonstrates that having access to the gradients of the forward model is beneficial to constrain the posterior density estimates.
+
+\section{Conclusions}\label{Conclusions}
+In this paper, we have presented the Differentiable Lensing Lightcone (DLL) model, a fast lensing lightcone simulator providing access to the gradient. 
+We extended the public FlowPM N-body code, implementing the Born approximation in the Tensorflow framework to create non-Gaussian convergence maps of weak gravitational lensing.
+To allow DLL to run at low resolution without affecting significantly the accuracy, we complement the FlowPM N-body code with the Hybrid-Physical Neural scheme, a new correction scheme for quasi N-body PM solver, based on Neural Network implemented as a Fourier-space filter.
+We validate our tool by comparing the $C_{\ell}$ and peak counts statistics against predictions from $\kappa$TNG simulations. 
+To do this, we run simulations following the evolution of $128^3$ particles and we produce weak lensing convergence maps for several redshift sources. 
+We show that, despite being generated at low computation costs, we recover a good match for redshift equal or higher than $z=0.91$. 
+To demonstrate the potential of our tool, as a first use case, we exploit the automatic differentiability of the simulations to do Fisher forecast. 
+Thanks to back-propagation, accessing the derivative through the simulations w.r.t.
+the cosmological parameters and $A_{IA}$ parameter is possible at the same computational cost of the forward simulation.
+Assuming an LSST-like setting, we simulate weak lensing convergence maps for a single source redshift $z=0.91$ and angular extend of 5$^\circ$, based on a periodic box of
+comoving volume equal to  $205$ $h^{-1}$Mpc.
+We compute the constraints on the resulting convergence maps
+with the starlet peak counts and use a wavelet-filtered lensing power spectrum as a benchmark for the comparison.
+ Within the limits of the analysis choices made in this study, we obtain the following results:
+\begin{itemize}
+    \item  We confirm that the peak count statistics outperform the two-point statistics as found in \cite{ajani2020constraining},
+ even in high dimensional cosmological and nuisance parameter space.
+    \item We find the peak counts to provide the most stringent constraints on the galaxy intrinsic alignment amplitude $A_{IA}$. 
+\end{itemize}
+
+To conclude, the framework outlined here can provide many advantages in the context of cosmological parameter inference:  it is the first step in the development of fully differentiable inference pipelines for weak lensing, it is a fast tool to further explore the sensitivity of higher-order statistics to systematics.
+
+\section*{Acknowledgments}
+BH is supported by the AI Accelerator program of the Schmidt Futures Foundation.
+The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
+Department of Energy under Contract No.
+DEAC02-05CH11231;
 %=====================
@@
 %=====================
+
+%%%%%%%%%%%%%%%%%%%%%  APPENDIX %%%%%%%%%%%%%%%%%%
+\appendix
+
+\section{Validation against a theory prediction}
+We show the $2\sigma$ constraints obtained from our Fisher analysis of standard $C_{\ell}$ (orange) and the theoretical prediction from halofit (blue contours) in \autoref{fig:Fisher_result_theory}.
+The dashed black contours define the prior used for the forecasting.
+The analysis is performed for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
+
+The constraints from the theoretical predictions
+are compatible with the ones obtained from the mock DLL maps for all cosmological parameters, except $n_s$.
+\denise{Indeed, despite sharing the same direction of the degeneracy, the theoretical contours for $n_s$ are narrower compared to the ones obtained in our analysis.
+In general, this translates into an increased uncertainty in constraining $n_s$, most likely due to the deficit in power observed for the $C_{\ell}$ at small scales.
+}
+
+The theoretical predictions are computed using the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}. 
+We want to highlight that both the theoretical Fisher matrices and the ones from our analysis are obtained by automatic differentiation.
+
+\renewcommand{\thefigure}{A\arabic{figure}}
+\setcounter{figure}{0}
+ \begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{paper/figures/Fisher_IA_theory_n.pdf}
+    \caption{ $2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
+    We compare the Fisher matrix constraints on cosmological parameters and $A_{IA}$ amplitude obtained with the $C_{\ell}$ from our mock maps (orange) and the theoretical $C_{\ell}$ (blue) obtained from the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}.
+    In both cases, the constraints are obtained by applying  the wavelet pass-band filter for the $C_{\ell}$ as described in \autoref{Validating_simulations_for_LSST_Y}.
+The dashed black contours are the prior used for the forecasting.}
+     \label{fig:Fisher_result_theory}
+\end{figure*}
+
+\section{Validate the stability of the Fisher contours}
+To ensure that the shape of the ellipses and the direction of the degeneracies are not the results of stochasticity, we prove the stability of the Fisher analysis results by testing the convergence of the jacobians.
+In \autoref{fig:Fisher_stab} we present the results for Fisher constraints obtained when varying the number of independent simulations used to compute the jacobians.
+As we can see, the convergence seems to be reached for the peak counts with, at least, 1500 realizations.
+On the other hand, the angular $C_{\ell}$ proves to be more sensitive to noise, and thus requires at least 2600 realizations.
+
+\renewcommand{\thefigure}{B\arabic{figure}}
+\setcounter{figure}{0}
+ \begin{figure*}
+    \centering
+        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_ps_new.pdf}
+        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_peak_1sigma_new.pdf}
+    \caption{ $1\sigma$ Fisher contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y} for the $C_{\ell}$ (upper panel) and the Peak counts (lower panel).
+The different colors refer to the number of independent realizations used to mean the Jacobian in the \autoref{Fisher_matrix}.
+The dashed black lines are located at the fiducial parameter values.}
+     \label{fig:Fisher_stab}
+\end{figure*}
+\denise{
+\section{Validation with higher resolutions simulations}
+In \autoref{Validating_simulations_for_LSST_Y}, we presented a validation of our simulations by comparing the statistics from DLL and $\kappa$TNG-Dark.
+In particular, we have seen a discrepancy on small scales for both the $C_{\ell}$ and the peak counts.
+We have attributed this bias to the low resolution of the simulations.
+Therefore, to justify this assumption, we simulate convergence maps of higher resolution, i.e, we raise the number of particles but keep the same box of 205$^3$($h^{-1}$Mpc$)^3$ in the simulation.
+In the left panel of  \autoref{fig:ps_comp_high}, we present the angular power spectrum computed from our DLL with the original number count of particles ($128^3$) and the power spectrum computed from higher resolutions DLL simulations ($212^3$).
+The two outputs are compared to the $\kappa$TNG predictions.
+In the right panel  of \autoref{fig:ps_comp_high} the fractional differences between the convergence power spectra from the two maps and the $\kappa$TNG are shown.
+We can see that, by increasing the number of particles, we can improve the accuracy of the lensing $C_{\ell}$ up to $~20\%$.
+As for the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different resolutions.
+We use the same wavelet decomposition presented in \autoref{peak_sec}.
+As for the power spectrum, we note the same tendency to recover better accuracy when the resolution is increased.
+
+Finally, we reproduce the results of the Fisher analysis for the intrinsic alignment parameter $A_{IA}$ with higher-resolution simulations.
+We adopt the same Forecast criteria presented in \autoref{Application_Fisher_forecast_for_HOS}.
+However, for this specific test, we compute the derivatives numerically using the finite differences.
+The step sizes used for these variations are $\Delta x_{IA}=0.15$ for the $C_{\ell}$ and $\Delta x_{IA}=1.2$ for the peak counts.
+% These step sizes have been tested by comparing the Fisher results obtained from those to the ones obtained from different step sizes. 
+In order to check the reliability of the numerical derivatives, we investigate the stability of the Fisher forecast against different step sizes used to compute them.
+The derivatives are computed as the mean of 3000 independent realizations for both $C_{\ell}$ and peak counts.
+
+ We confirm the peak counts provide the most stringent constraints on the galaxy intrinsic alignment amplitude $A_{IA}$.
+As for the full analysis, we tested the stability of the Fisher forecast by varying the number of simulated maps used to compute the derivatives.
+In \autoref{tuning_high} we present the $1\sigma$ error on $A_{IA}$ when varying the number of independent realizations used to compute the derivatives.
+It is interesting to note, that, even in this case, the derivatives of the $C_{\ell}$ can not be considered fully converged.
+However, as can be noted from the stability plots of \autoref{tuning_high}, the noise in the derivatives leads to tighter constraints in the Fisher forecast.
+Hence, the fully converged derivatives of the $C_{\ell}$ would result in even broader constraints, without changing the results we found.
+
+\renewcommand{\thefigure}{C\arabic{figure}}
+\setcounter{figure}{0}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/cls_DLL_vs_ktng_high.pdf}
+        \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_high.pdf}
+    \caption{
+    \textbf{Left panel}: Angular power spectra of PM simulations with original resolution (number count 128$^3$, blue line) and higher resolution (number count 212$^3$, red line) compared to the $\kappa$TNG prediction.
+\textbf{Right panel}: fractional angular power spectrum of PM simulations with original and higher resolution and the $\kappa$TNG prediction.
+The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the error on the mean.
+The spectra are computed for the source redshift $z_s=0.91$.
+}
+    \label{fig:ps_comp_high}
+\end{figure*}
+
+\renewcommand{\thefigure}{C\arabic{figure}}
+\setcounter{figure}{1}
+\begin{figure*}\label{peaks_high}
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/res_peak_DLL_vs_ktng_high.pdf}
+    \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations.
+The results are shown for the number counts $128^3$ (blue lines) and $212^3$ (orange lines).
+The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmins (lower panel).
+  The results mean over 100 independent map realisations, the shaded regions represent the error on the mean. The statistics are computed for the source redshift $z_s=0.91$. }
+\end{figure*}
+
+\renewcommand{\thefigure}{C\arabic{figure}}
+\setcounter{figure}{2}
+\begin{figure*}\label{tuning_high}
+    \centering
+     \includegraphics[width=\columnwidth]{paper/figures/tuning_snsim_cls.pdf}
+        \includegraphics[width=\columnwidth]{paper/figures/tuning_snsim_peaks.pdf}
+    \caption{
+    $1\sigma$ error on $A_{IA}$ derived for one single source redshift at z=0.91 for different numbers of independent realizations used to mean the Jacobian in the \autoref{Fisher_matrix}.
+The results are shown for the $C_{\ell}$ (left panel) and the peak counts (right panel).
+}
+\end{figure*}
+
+\renewcommand{\thefigure}{C\arabic{figure}}
+\setcounter{figure}{3}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{paper/figures/Fisher_IA.pdf}
+    \caption{$1\sigma$ error on $A_{IA}$ for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}, from mock simulations with $212^3$ particles.
+The results are obtained by applying the starlet Peak counts (yellow contours) computed on noisy maps filtered using a starlet kernel of [$9.33, 18.70, 37.38$] arcmin together and the wavelet pass-band filter for the $C_{\ell}$ statistics (grey contours) as described in \autoref{Validating_simulations_for_LSST_Y}.
+}
+     \label{fig:Fisher_result_ia}
+\end{figure*}
+}
 

### 2023-03-16 paper/submitted.tex

--- 2023-03-16 paper/paper.tex
@@
 We present the Differentiable Lensing Lightcone (DLL), a fully differentiable physical model designed for being used as a forward model in Bayesian inference algorithms requiring access to derivatives of lensing observables with respect to cosmological parameters.
-We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones \denise{and implementing the Born approximation} in the Tensorflow framework.
+We extend the public FlowPM N-body code, a particle-mesh N-body solver, implementing
+ray-tracing and simulating lensing lightcones in the Tensorflow framework.
 Furthermore, DLL is aimed at achieving high accuracy with low computational costs.
@@
 As a first use case, we use this tool to investigate the relative constraining power of the angular power spectrum and peak counts statistic in an LSST setting.
-Such comparisons are typically very costly as they require a large number of simulations, and do not scale well with the increasing number of cosmological parameters.  
+Such comparison are typically very costly as they require a large number of simulations, and do not scale well with the increasing number of cosmological parameters.  
 As opposed to forecasts based on finite differences, these statistics can be analytically differentiated with respect to cosmology, or any systematics included in the simulations at the same computational cost of the forward simulation.
-We find that the peak counts outperform the power spectrum on the cold dark matter parameter $\Omega_c$, on the amplitude of density fluctuations $\sigma_8$, and on the
-amplitude of the intrinsic alignment signal $A_{IA}$.
+We find that the peak counts outperform the power spectrum on $\Omega_c$, $\sigma_8$ and $A_{IA}$.
+% , while $h$, $n_s$, and $\Omega_b$ are unconstrained by weak lensing cosmic shear. 
 \end{abstract}
@@
 With the increased statistical power of these surveys comes the question of their optimal analysis.
-Traditional cosmological analysis rely on measurements of the two-point statistics, either the shear two-point correlation functions or its Fourier transform, the lensing power spectrum.
-However, the two-point statistics are only optimal for Gaussian fields, and do not fully capture the non-Gaussian information imprinted in the lensing signal at the scales that future surveys will be able to access (e.g.
+Traditional cosmological analysis rely on measurements of the two point statistics, either the shear two-point correlation functions or its Fourier transform, the lensing power spectrum.
+However, the two point statistics are only optimal for Gaussian fields, and do not fully capture the non-Gaussian information imprinted in the lensing signal at the scales that future surveys will be able to access (e.g.
 information encoded in the peaks and in the filamentary features of the matter distribution).
 
- This has led to the introduction of a number of  higher-order statistics to access the non-Gaussian information from weak lensing data: 
-the weak lensing one point PDF \citep{liu2019constraining, uhlemann2020fisher, boyle2021nuw}, lensing peak counts \citep{liu2015cosmology, liu2015cosmological, lin2015new, kacprzak2016cosmology, peel2017cosmological, shan2018kids, martinet2018kids, ajani2020constraining, harnois2021cosmic, zurcher2022dark}, Minkowski functionals \citep{kratochvil2012probing, petri2013cosmology}, moments of mass maps \citep{gatti2021dark}, wavelet and scattering transforms \citep{ajani2021starlet, cheng2021weak},, and 3 point statistics \citep{takada2004cosmological, semboloni2011weak, rizzato2019tomographic, halder2021integrated}.
+ This has led to the introduction of a number of  higher-order statistic to access the non-Gaussian information from weak lensing data: 
+the weak lensing one point PDF (\cite{liu2019constraining}, \cite{uhlemann2020fisher}, \cite{boyle2021nuw}), lensing peak counts (\cite{lin2015new}, \cite{peel2017cosmological}, \cite{ajani2020constraining}, \cite{harnois2021cosmic}, \cite{zurcher2022dark} ), Minkowski functionals (\cite{kratochvil2012probing}, \cite{petri2013cosmology}), moments of mass maps (\cite{gatti2021dark}), wavelet and scattering transforms (\cite{ajani2021starlet}, \cite{cheng2021weak}), and 3 point statistics (\cite{takada2004cosmological}, \cite{semboloni2011weak}, \cite{rizzato2019tomographic},  \cite{halder2021integrated}).
 
-Recently, machine learning-based methods that broadly fall in the category of Simulation-Based Inference (SBI) \citep{fluri2019cosmological, kacprzak2022deeplss, fluri2021cosmological, jeffrey2021likelihood, fluri2022full}, and Bayesian forward-modeling frameworks \citep{porqueres2021bayesian, sarma2022map} have also been introduced to attempt to fully account for the non-Gaussian content in the weak lensing signal.
-Unlike the methods described above, these approaches are designed to access the full field-level information content.
+Recently, machine learning-based methods that broadly fall in the category of Simulation-Based Inference (SBI) (\cite{fluri2019cosmological}, \cite{kacprzak2022deeplss}, \cite{fluri2021cosmological}, \cite{jeffrey2021likelihood}, \cite{fluri2022full}) and Bayesian forward-modelling frameworks (\cite{porqueres2021bayesian}, \cite{sarma2022map}) have also been introduced to attempt to fully account for the non-Gaussian content in the weak lensing signal.
+Contrary to the methods described above, these approaches are designed to access the full field-level information content.
 Even though these techniques are asymptotically theoretically optimal in terms of information recovery, they still suffer from significant limitations.
@@
 Modern approaches employ deep learning-based density estimation methods to model the likelihood without the need to make any Gaussianity assumptions, and as such have
-drawn the attention of the community \citep{alsing2018massive, jeffrey2021likelihood}.
+%One possible way to circumvent the absence on analytical expression consists in calibrating the cosmology inference from weak lensing simulations.
+But even in the scenario in which we are able to simulate very precise mock data, we are faced with a new bottleneck: writing down a tractable likelihood function is not a given.
+%The current cosmological analysis are based on the assumption of Gaussian likelihood, however in many situations the calculation of the likelihood is intractable or impractical.
+%This is the reason why Likelihood Free Inference (LFI) approaches, aimed to perform Bayesian inference without numerical evaluation of the likelihood function have 
+drawn the attention of the community (\cite{alsing2018massive}, \cite{jeffrey2021likelihood}).
 
-A key element common to most of these methodologies is their ability to benefit from gradient information. 
+A key element common to most of the aforementioned methodologies is their ability to benefit from gradient information. 
 For example, \cite{porqueres2021bayesian} present a Bayesian hierarchical approach to infer the cosmic matter density field simultaneously with cosmological parameters using the Hamiltonian Monte Carlo (HMC) algorithm to explore the full high-dimensional parameter space.
-The HMC algorithm exploits the information encoded in the gradients of the joint likelihood function to inform each update step and hence requires the derivatives of the forward model.
+The HMC algorithm exploits the information encoded in the gradients of the joint likelihood function and hence requires the derivatives of the forward model.
 
@@
 One possible way of evaluating these gradients with respect to cosmological parameters is by using numerical differentiation, e.g.
-computing a finite difference of a given statistic by varying the simulation fiducial values by a small amount.
+computing a finite difference of a given statistics by varying the simulation fiducial values by a small amount.
 However, numerical differentiation is expensive in terms of computational resources and simulation time, and also requires hyperparameter tuning for the step size used in the finite difference scheme.
 An alternative option consists in computing the gradient analytically.
-Both these solutions are faced with limitations: the first approach gets computationally intractable in high dimensions, while the analytic gradients are sometimes impossible to estimate.
+Nevertheless, both these solutions are faced with limitations: the first approach gets computationally intractable in high dimensions, while the analytic gradients are sometimes impossible to estimate.
 All of these new techniques for cosmological analyses make the development of fast and differentiable simulations necessary.
@@
 In this paper,  we aim to efficiently compute gradients that benefit the development of new inference algorithms for weak lensing surveys.
-To do this we extend the framework of the FlowPM package \cite{modi2021flowpm} by implementing the Born approximation and simulating lensing lightcones in the Tensorflow framework.
-TensorFlow is a tensor library that includes the ability to perform automatic differentiation.
-Automatic differentiation enables us to compute gradients exactly as opposed to finite differences, which only provide approximate gradients.
+To do this we extend the framework of the FlowPM package \cite{modi2021flowpm} by implementing ray-tracing and simulating lensing lightcones in the Tensorflow framework.
+TensorFlow is a tensor library that include the ability to perform automatic differentiation.
+Automatic differentiation enables us to compute gradients exactly as opposed to finite differences, which only provides approximate gradients.
 Specifically, TensorFlow implements the backpropagation algorithm to compute gradients, i.e.
 first it creates a graph (e.g.
-data structures representing units of computation), then it works backward through the graph by applying the chain rule at each node.
-\denise{Unlike MADlens, our tool is GPU-based and provides derivatives with respect to all the cosmological parameters.
-There are also differences in the implementation of various functions to improve accuracy and speed.}
+data structures representing units of computation), then it works backwards through the graph by applying the chain rule at each node.
+Contrary to MADlens, our tool provides derivatives with respect to all the cosmological parameters.
 
-We validate our simulations against the cosmological N-body simulations $\kappa$TNG \citep{osato2021kappatng} by comparing both the lensing angular power spectrum and multiscale peak counts.
+We validate our simulations against the cosmological Nbody simulations $\kappa$TNG \citep{osato2021kappatng} by comparing both the lensing angular power spectrum and multiscale peak counts.
 
-In particular, as a first application, we show how the differentiability of numerical simulations can be exploited to evaluate the Fisher Matrix.
+In particular, as first application, we show how the differentiability of numerical simulations can be exploited to evaluate the Fisher Matrix.
 Then, we compare the constraining power of two map-based weak lensing statistics: the lensing power spectrum and peak counts and investigate the degeneracy in high dimensional cosmological and nuisance parameter space through Fisher forecasts.
 
-This paper is structured as follows: in \autoref{weak_lesning_modeling} we briefly review the weak lensing modeling including the theoretical framework and the summary statistics used in this work.
+This paper is structured as follow: in \autoref{weak_lesning_modeling} we first briefly review the weak lensing modeling including the theoretical framework and the summary statistics used in this work.
 In \autoref{Fast_and_Differentiable_Lensing_Simulations} we introduce the numerical simulations illustrating the numerical methods used to generate mock WL maps.
@@
 The Fisher forecast formalism and the survey and noise setting are shown in \autoref{Application_Fisher_forecast_for_HOS}.
-We finally discuss our results and present our conclusions afterward, in \autoref{Discussion} and \autoref{Conclusions}.
+We finally discuss our results and present our conclusions afterwards, in \autoref{Discussion} and \autoref{Conclusions}.
 
@@
 \subsection{{Cosmic shear}}
-Weak gravitational lensing is a powerful probe to infer the projected matter density distribution between an observer and a source.
+Weak gravitational lensing is a powerful technique to infer the projected matter density distribution between an observer and a source.
 The effect of gravitational lensing 
@@
 From the parametrization of the symmetrical matrix $\mathcal{A}$, we can define the spin-two shear $\gamma=(\gamma_1,\gamma_2)$ and the scalar convergence field, $\kappa$. 
-Hence, the convergence and the shear are defined as the second derivative of the potential:
+Hence, the convergence and the shear are defined as second derivative of the potential:
 \begin{equation}\label{kshear}
@@
 
-Different theoretical models have been proposed to describe the physics of Intrinsic Alignments (IA), such as the Non-Linear tidal Alignment model (NLA) (e.g.
-in \citet{Bridle_2007}), the tidal torquing model \citep{PhysRevD.70.063526, 10.1046/j.1365-8711.2001.04105.x}, or the combination of both the Tidal Alignment and Tidal Torquing model (TATT)  \citep{PhysRevD.100.103506}.
+Different theoretical models have been proposed to described the physics of Intrinsic Alignments (IA), such as the Non-Linear tidal Alignment model (NLA) (e.g.
+in \citet{Bridle_2007}), the tidal torquing model (\citet{PhysRevD.70.063526}; \citet{10.1046/j.1365-8711.2001.04105.x}), or the combination of both the Tidal Alignment and Tidal Torquing model (TATT)  (\cite{PhysRevD.100.103506}).
 We model the IA effect using the NLA description \citep{harnois2021cosmic}, i.e. assuming a linear coupling between the intrinsic galaxy shapes and the non-linear projected tidal fields $s_{ij}$:
@@
 \subsection{Lensing Summary Statistics }\label{stat}
-To extract the cosmological information from the simulated $\kappa-$maps, we use two summary statistics for weak lensing observable: the angular power spectrum and the starlet peak counts \citep{lin2016new}.
+To extract the cosmological information from the simulated $\kappa-$maps, we use two summary statistic for weak lensing observable: the angular power spectrum and the Starlet peak counts \citep{lin2016new}.
 
@@
 }
-Second-order statistics, both in the form of shear 2-point correlation function $\xi_{\pm}(\theta)$, or its counterpart in Fourier space, the angular power spectrum $C_{\ell}$, have been widely used to extract the cosmological information from weak lensing surveys.
+Second order statistics, both in the form of shear 2-point correlation function $\xi_{\pm}(\theta)$, or its counterpart in Fourier space, the angular power spectrum $C_{\ell}$, have been widely used to extract the cosmological information from weak lensing surveys.
 \
@@
 
-The Intrinsic Alignment (IA) signal adds an excess correlation to the two-point shear correlation function (also known as cosmic shear GG or shear-shear correlation) with two terms: 1) the intrinsic-intrinsic (II) term, tracing the correlation of the intrinsic shape of two galaxies  and 2) and the intrinsic-shear coupling (GI) term, describing the correlation between the intrinsic ellipticity of one galaxy with the shear of another galaxy \citep{kilbinger2015cosmology}.
-% In the Limber approximation, the $C_{\ell}^{II}$ and $C_{\ell}^{GI}$ contributes can be computed from the matter power spectra:
-The matter power spectra for the IA terms are defined as:
+The Intrinsic Alignment (IA) signal adds an excess correlation to the two-point shear correlation function (also known as cosmic shear GG or shear-shear correlation) with two term: 1) the intrinsic-intrinsic (II) term, tracing the correlation of intrinsic shape of two galaxies  and 2) and the intrinsic-shear coupling (GI) term, describing the correlation between the intrinsic ellipticity of one galaxy with the shear of another galaxy (\cite{kilbinger2015cosmology}).
+In the Limber approximation, the $C_{\ell}^{II}$ and $C_{\ell}^{GI}$ contributes can be computed from the matter power spectra:
 \begin{align}
-    P_{II}(k,z)=& \left ( \frac{A_{IA}\bar{C}_1\bar{\rho}(z)}{\bar{D}(z)} \right)^2 a^{4}(z)P_{\delta}(k,z) 
+    P_{II}(k,z)=& \left ( \frac{A_{IA}\bar{C}_1\bar{\rho}(z)}{\bar{D}(z)} \right)^2 a^{4}(z)P_{\delta}(k,z) \\
     \\
@@
 where $\bar{D}(z) \equiv D(1+z)$ \citep{harnois2021cosmic}.
-\denise{Under the Limber
-approximation the projected angular power spectra for the IA terms become:
-\begin{align}
-    C_{II}=& \int_0^{\chi_{lim}} \text{d}\chi 
-    \frac{n^2(\chi)}{a^2(\chi)}P_{II}(k,\chi), \\
-    C_{GI}= \frac{3\Omega_m H_0^2}{2c^2} & \int_0^{\chi_{lim}} \text{d}\chi 
-    \frac{g(\chi)n(\chi)}{a(\chi)}P_{GI}(k,\chi).
-\end{align}
-}
 
@@
 This multiscale approach is well-suited for the study of astronomical data since their complex hierarchical structure. 
-\denise{A wavelet function $\psi(x)$ is a function that satisfies the admissibility condition:
-\begin{equation}
-    \int_{\mathbb{R}^{+}} |\hat{\psi}(k)|^2 \frac{dk}{k}<\infty,
-\end{equation}
-where we indicate with $\hat{\psi}(k)$ the Fourier transform of $\psi(x)$, with $\int\psi(x)dx=0$ in order to satisfy the admissibility condition. 
-A given signal is decomposed in a family of scaled and translated functions:
-\begin{equation}
-    \psi_{a,b}(x)=\frac{1}{\sqrt{a}}\psi \left( \frac{x-b}{a}\right),
-\end{equation}
-
-where $\psi_{a,b}$ is the so-called \textit{daughter wavelets}, scaled and translated version of the \textit{mother} wavelet, with $a$ and $b$ scaling and translation parameters.
-The continuous wavelets transform is defined from the projections of a function $f \in L_2(\mathbb{R})$ onto the family of daughter wavelets.
-The coefficients of this projection represent the wavelet coefficient, obtained by :
-\begin{equation}
-    W_f(a,b)=\int_{\mathbb{R}} f(x)\psi^{*}_{a,b}(x)dx=\frac{a}{\sqrt{a}}\int_{\mathbb{R}}f(x)\psi^{*}\left( \frac{x-b}{a}\right)dx ,
-\end{equation}
-with $\psi^{*}$ the complex conjugate of $\psi$, and $ \forall a \in \mathbb{R}^{+}$, $ b \in \mathbb{R.}$  }
-In this work, we filter the original convergence maps with the starlet transform, an isotropic and undecimated (i.e.
-not down-sampled)  wavelet transform, suited for astronomical applications where objects are mostly more or less isotropic \citep{4060954}.
+In this work we filter the original convergence maps with the Starlet transform, an isotropic and undecimated  wavelet transform, suited for astronomical application where objects are mostly more or less isotropic (\citet{4060954}).
 
@@
 \begin{equation}
-\phi_{1D}(x)= \frac{1}{12} (|x-2|^3-4|x-1|^3+6|x|^3-4|x+1|^3+|x+2|^3 ).
+\phi (x)= \frac{1}{12} (|x-2|^3-4|x-1|^3+6|x|^3-4|x+1|^3+|x+2|^3 ).
 \end{equation}
-\denise{
-The N-dimensional scaling functions can be built starting from the separable product of N $\phi_{1D}$: $\phi(x_1,x_2)=\phi_{1D}(x_1)\phi_{1D}(x_2)$. }
-Each set of wavelet coefficients $w_j$ is obtained as the convolution of the input map with the corresponding wavelet kernel.
+Each set of wavelet coefficients $w_j$ are obtained as the convolution of the input map with the corresponding wavelet kernel.
 For a full description of the starlet transform function, see \citet{4060954} and \citet{10.5555/1830428}.
 
-\paragraph{Peak counts}It has been shown that it is necessary to go beyond second-order statistics to fully capture the non-Gaussian information encoded in the peaks of the matter distribution 
-\citep{1997A&A...322....1B, 1997ApJ...484..560J,1999A&A...342...15V,2003A&A...397..809S}.
-Several studies have shown that the weak-lensing peak counts provide a way to capture information from non-linear structures that is complementary to the information extracted by power spectrum \citep{lin2015new, peel2017cosmological, ajani2020constraining, harnois2021cosmic, zurcher2022dark}.
-The peaks identify regions of weak lensing map where the density value is higher, in this way they are particularly sensitive to massive structures.
+\paragraph{Peak counts}It has been shown that it is necessary to go beyond second-order statistics to fully capture the non-Gaussian information encoded in the peaks of the matter distribution (\citet{1997A&A...322....1B}, \citet{1997ApJ...484..560J}, \citet{1999A&A...342...15V}, \citet{2003A&A...397..809S}).
+Several studies have shown that the weak-lensing peak counts provide a way to capture information from non-linear structures that is complementary to the information extracted by power spectrum (\cite{lin2015new}, \cite{peel2017cosmological}, \cite{ajani2020constraining}, \cite{harnois2021cosmic}, \cite{zurcher2022dark} ).
+The peak identify regions of weak lensing map where the density value is higher, in this way they are particularly sensitive to the massive structures.
 There are two different ways to record weak lensing peaks: as 1) local maxima of the signal-to-noise field or 2) local maxima of the convergence field.
-In both cases, they are defined as pixels of larger value than their eight neighbors in the image.
+In both cases, they are defined as pixels of larger value than its eight neighbours in the image.
 
 \section{Fast and Differentiable Lensing Simulations}\label{Fast_and_Differentiable_Lensing_Simulations}
-Analytical models with which to predict the observed signals do not exist for most higher-order summary statistics. 
+Analytical models with which to predict the observed signals do not exist for most Higher-Order  summary statistics. 
 To circumvent this issue, one approach is to rely on generating a suite of numerical simulations.
-In the following section, we introduce our weak lensing map simulation procedure, including a description of the N-body simulator and the \denise{lightcone construction}.
+In the following section we introduce our weak lensing map simulation procedure, including a description of the N-body simulator and of the ray-tracing scheme.
 
@@
 
-However, collision-less N-body simulations typically require significant computational effort in terms of time and CPU/GPU power, in particular, computing the gravitational interactions between the particles is typically the most time-consuming aspect and where most of the approximations are done.
-For that reason, several quasi N-body schemes have been developed to reduce the simulation time and the computational cost of full numerical simulations. 
-Our weak lensing simulation tool is mainly based on the FastPM algorithm \citep{2019ascl.soft05010F} and its FlowPM \citep{modi2021flowpm} implementation which provides a fast Particle-Mesh (PM) solver estimating the gravitational forces by computing Fast Fourier Transforms on a 3D grid.
+However, they typically require significant computational effort in terms of time and CPU/GPU power, in particular, computing the gravitational interactions between the particles is typically the most time-consuming aspect and where most of the approximations are done.
+For that reason, several Quasi N-body schemes have been developed to reduce the simulation time and the computational cost of full numerical simulations. 
+Our weak lensing simulation tool is mainly based on the FastPM algorithm (\citet{2019ascl.soft05010F}) and its FlowPM (\cite{modi2021flowpm}) implementation which provides a fast Particle-Mesh (PM) solver estimating the gravitational forces by computing Fast Fourier Transforms on a 3D grid.
 
@@
 In this work, we extend the FlowPM approach by implementing the time integration of the Ordinary Differential Equations
-(ODEs) that describe the gravitational evolution of the particles in the simulation using a black-box ODE integrator.
+(ODE) that describe the gravitational evolution of the particles in the simulation using a black-box ODE integrator.
 This is in contrast to the leapfrog integration method used in FastPM.
-One reason for this change is that adaptive ODE solvers are able to automatically adjust the time step of the simulation based on the desired accuracy for the result.
+One reason for this change is that adaptive ODE solvers are able to automatically adjust the time stepping of the simulation based on a desired accuracy for the result.
 Another reason for this approach is that modern automatic differentiation frameworks like TensorFlow provide automatically differentiable solvers which significantly reduce the memory footprint of the simulation when computing the gradients, as will be described below.
@@
         \frac{d \mathbf{x}}{d a} & = \frac{1}{a^3 E(a)} \mathbf{v} \\
-        \frac{d \mathbf{v}}{d a} & =  \frac{1}{a^2 E(a)} F(\mathbf{x}, a), \\
+        \frac{d \mathbf{v}}{d a} & =  \frac{1}{a^2 E(a)} F_\theta(\mathbf{x}, a), \\
     \end{array} \right.
 \end{equation}
-with $\mathbf{x}$ and $\mathbf{v}$ the position and the velocity of the particles, \denise{\textit{a} the cosmological scale factor, $E(a)$ the ratio between the Hubble expansion rate and the Hubble parameter and $\mathbf{F}$ the gravitational force experienced by the dark matter particles in the mesh.}
+with $\mathbf{x}$ and $\mathbf{v}$ the position and the velocity of the particles and \textit{a} the cosmological scale factor.
 
 To evaluate the gradients of the solution with respect to input cosmological parameters, it is therefore necessary to  back-propagate through the ODE solver.
-Very recently the adjoint sensitivity method \cite{chen2018neural, pontryaginmathematical} has gained a lot of attention in the field of deep learning, as it allows to compute these gradients by solving a second ODE backward in time and treat the ODE solver as a black box.
+Very recently the adjoint sensitivity method \cite{chen2018neural, pontryaginmathematical} has gained a lot of attention in the field of deep learning, as it allows to compute these gradients by solve a second ODE backwards in time, and treat the ODE solver as a black box.
 
@@
  \end{equation}
-All the integrals are evaluated in a single call to the ODE solver, and the Jacobian is computed by automatic differentiation.
+All the integrals are evaluated in a single call to the ODE solver, and the Jacobian are computed by automatic differentiation.
 
@@
 This induces a memory overhead that scales with the number of time steps in the simulation.
-In the adjoint ODE approach, this is instead replaced by solving another ODE backward in time when evaluating the gradient.
+In the adjoint ODE approach, this is instead replaced by solving another ODE backwards in time when evaluating gradient.
 We illustrate the potential of differentiating through ODE solvers, highlighting the fact that the simulations and the gradients presented in this paper are computing using one single GPU for $128^3$ particles.
@@
 \subsubsection{ Hybrid Physical-Neural ODE}\label{N_body_des}    
-PM simulations can be used as a viable alternative to full N-body to model the galaxy statistics and create fast realizations of large-scale structures at lower computational cost.
-Nevertheless, these kinds of simulations lack resolution on small scales and are not able to resolve structures with scales smaller than the mesh resolution.
+PM simulations can be used as viable alternative to full N-body to model the galaxy statistics and create fast realizations of the large scale structures at lower computational cost.
+Nevertheless, this kind of simulations lack resolution on small scales and are not able to resolve structures with scales smaller than the mesh resolution.
 To compensate for
-the small-scale approximations and recover the missing power, we adopt an Hybrid Physical-Neural (HPN) approach presented in \citet{lanzieri2022hybrid}. 
-The correction scheme we implement consists in computing the short-range interaction as an additional force parameterized by a Fourier-space Neural Network.
-This residual force is modeled by applying a learned isotropic Fourier filter acting
+the small-scales approximations and recover the missing power, we adopt an Hybrid Physical-Neural approach presented in \citet{lanzieri2022hybrid}. 
+The correction scheme we implement consists in computing the short range interaction as an additional force parameterized by a Fourier-space Neural Network.
+This residual force is modelled by applying a learned isotropic Fourier filter acting
 on the PM-estimated gravitational potential $\phi_{PM}$:
@@
 \end{equation}
-where $\mathcal{F}^{-1}$ is the inverse Fourier transform and $f_\theta(a,|\mathbf{k}|)$ is a B-spline function whose coefficients are the output of the Neural Network of parameters $\theta$ trained using the CAMELS simulations \citep{villaescusa2021camels}.
+where $\mathcal{F}^{-1}$ is the inverse Fourier transform and $f_\theta(a,|\mathbf{k}|)$ is a B-spline functions whose coefficients are the output of the Neural Network of parameters $\theta$ trained using the CAMELS simulations (\cite{villaescusa2021camels}).
+
 In particular,  we use a \textit{single} CAMELS N-body simulation at the fiducial cosmology of $h=0.6711$, $n_s =0.9624$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.30$, $\sigma_8= 0.8$.
@@
 where $\lambda$ is an hyper-parameter balancing the
-contributions of the two terms.
-\denise{By comparing the results obtained from different values of $\lambda$ in the fiducial setting and outside the training regime, we find that $\lambda= 0.1$ provided the optimal balance in terms of overall correction and overfit.
-}
+contributions of the two terms. We empirically find $\lambda = 0.1$ provides good results.
 
@@
 we applied the correction parameters found with the setting described above to simulations of larger volume or different $\Omega_m$ and $\sigma_8$.
-We observed that most of the missing power that characterizes the matter power spectrum in the PM approximation is still recovered when the HPN correction is applied to simulations different from the ones used to train the Neural Network.
-So, from these tests, we can conclude that the HPN is still robust to differences among simulation settings.
+We observed that most of the missing power that characterizes the matter power spectrum in the PM approximation is still recovered when the HPN correction is applied to simulations different to the ones used to train the Neural Network.
+So, from these tests we can conclude that the HPN is still robust to differences among simulation setting.
 
@@
 To recover the redshift range of the lightcone, one unit box is replicated using periodic boundary conditions.
-First, we generate rotation matrices along the three axes, hence, each snapshot is rotated around each of the three axes, finally, all the particles are randomly shifted along the axes.
-To obtain the final density field, each snapshot is projected in a 2D plane by estimating its density with a  cloud-in-cell (CiC) interpolation scheme \citep{hockney1988computer}.
+First, we generate rotation matrices along the three axes, hence, each snapshot is rotated around each of the three axes, finally all the particles are randomly shifted along the axes.
+To obtain the final density field, each snapshot is projected in a 2D plane by estimating its density with a  cloud-in-cell (CiC) interpolation scheme \cite{hockney1988computer}.
 After creating a Cartesian grid of coordinates, each slice is interpolated onto sky coordinates.
-\denise{.
-This procedure differs from the one implemented in the MADLens package \citep{bohm2021madlens}.
-In MADLens the lightcone is built by translating the redshift of the particles into distances, then the particles are projected onto the convergence map at the proper evolution step corresponding to that distance.}
+% The Cartesian grid correspond to a regular grid of $1024^2$ pixels and $5\times 5$ deg$^2$.
 
@@
 We generate the convergence map by integrating the lensing density along the unperturbed line of sight, i.e.
-applying the Born approximation \citep{schneider2006weak}.
+applying the Born approximation (\citet{schneider2006weak}).
 In particular we discretize the \autoref{born_approx} such that it becomes:
@@
 We model the effect of IA on the convergence map level following the model proposed by  \citet{fluri2019cosmological}.
-This allows us to create pure IA convergence maps to combine with shear convergence maps in order to generate a contaminated signal.
+This allow us to create pure IA convergence maps to combine with shear convergence map in order to generate a contaminated signal.
 Following \cite{harnois2021cosmic}, the Fourier transform of the intrinsic ellipticities can be phrased as: 
@@
 \subsubsection{Differentiable Peak Counts}
-One of the difficulties in estimating derivatives of traditional peak count statistics is that it relies on building
+One of the difficulties for estimating derivatives of traditional peak count statistics is that it relies on building
 an histogram of peak intensities, and histograms, due to the discrete nature of the bins, are not differentiable.
@@
 
-This procedure yields a peak count statistic that is smoothly differentiable with respect to the input map and thus can be used for applications such as Fisher forecasting as discussed later in this paper.
+This procedure yields a peak count statistic which is smoothly differentiable with respect to the input map, and thus can be used for applications such as Fisher forecasting as discussed later in this paper.
 
 \section{Validating simulations for LSST}\label{Validating_simulations_for_LSST_Y}
-In this section, we compare the results from our simulation to other works, including the analytic models for the matter power spectrum \textit{Halofit} \citep{smith2003stable,takahashi2012revising} and the cosmological N-body simulations, $\kappa$TNG \citep{osato2021kappatng}.
+In this section, we compare the results from our simulation to other works, including the analytic models for the matter power spectrum \textit{Halofit} \citep{smith2003stable,takahashi2012revising} and the cosmological Nbody simulations, $\kappa$TNG \citep{osato2021kappatng}.
 
-The $\kappa$TNG simulations is a suite of publicly available weak lensing mock maps based on the cosmological hydrodynamical simulations IllustrisTNG, generated with the moving mesh code AREPO \citep{2010MNRAS.401..791S}.
+The $\kappa$TNG simulations,  is a suite of publicly available weak lensing mock maps based on the cosmological hydrodynamical simulations IllustrisTNG, generated with the moving mesh code AREPO \citep{2010MNRAS.401..791S}.
 In particular, we use the $\kappa$TNG-Dark suit of maps based on the corresponding dark matter-only TNG simulations. 
-The simulations have a side length of the box equal to 205 Mpc/h and $2500^3$ CDM particles.
-To model the propagation of light rays and simulate the weak lensing maps, a multiple-lens plane approximation is employed. 
-The simulation configuration consists of a map size of $5\times5$ deg$^2$, $1024\times 1024$ pixels and a resolution of 0.29 arcmin/pixel. 
+The simulations have a side length of simulation box equal to 205 Mpc/h and $2500^3$ CDM particles.
+To model the propagation of light rays and simulate the weak lensing maps, a multiple lens plane approximation is employed. 
+The simulations configuration consists in a map size of $5\times5$ deg$^2$, $1024\times 1024$ pixels and resolution of 0.29 arcmin/pixel. 
 For a complete description of the implementation see \cite{osato2021kappatng}.
@@
 
-We assume the following cosmological parameters: $h=0.6774$, $n_s =0.9667$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.3075$, $\sigma_8= 0.8159$, such that they match the results of Planck 2015 \citep{ade2016planck}.
+We assume the following cosmological parameters: $h=0.6774$, $n_s =0.9667$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.3075$, $\sigma_8= 0.8159$, such that they match the results of Planck 2015 (\cite{ade2016planck}).
 We reproduce the same configuration of $\kappa$TNG, i.e. each map is on a regular grid of $1024^2$ pixels and $5\times 5$ deg$^2$.
 
-The actual choice of bins to include in the forecasting is made following the DESC data requirement for the angular power spectra \citep{mandelbaum2018lsst}, i.e.
+The actual choice of bins to include in the forecasting is made following the DESC data requirement for the angular power spectra (\cite{mandelbaum2018lsst}), i.e.
 adopting $\ell_{max,shear} = 3000$ and  $\ell_{min,shear} = 300$.
@@
 \subsection{HPN validation }
-To compensate for the small-scale approximations resulting from PM, we applied the HPN approach presented in \autoref{N_body_des}. 
-We show on \autoref{fig:pkhalofit_comp} the power spectrum  and the fractional power spectrum of PM simulations before and after the HPN correction compared to analytic Halofit predictions \citep{smith2003stable, takahashi2012revising} for redshift $z=0.03$ and $z=0.91$.
+To compensate for the small-scales approximations resulting from PM, we applied the HPN approach presented in \autoref{N_body_des}. 
+We show on \autoref{fig:pkhalofit_comp} the power spectrum  and the fractional power spectrum of PM simulations before and after the HPN correction compared to analytic Halofit predictions (\cite{smith2003stable} \cite{takahashi2012revising}) for redshift $z=0.03$ and $z=0.91$.
 \begin{figure}
@@
      Matter power spectrum and fractional matter power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the theoretical halofit model for redshift z=0.03 (upper panel) and redshift z=0.91 (lower panel).
-The power
-spectra and ratios are means over 100 independent map realisations. The shaded regions represent the standard deviation from 100 independent DLL realisations.
     }
@@
 \end{figure}
- We observe a bias between our measured power spectrum and the theoretical prediction at low $k$.
+ We observer a bias between our measured power spectrum and the theoretical prediction at low $k$.
 This reduced power is explained by the small box size of our simulation and the associated reduced number of large-scale modes.
 At redshift $z=0.91$ most of the missing
-power is recovered by the HPN correction up to $k \sim 1$, after which the method overemphasizes the small-scale power.
-\denise{In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.}
-
+power is recovered by the HPN correction up to $k \sim 1$, after which the method overemphasizes the small scale power.
 At redshift $z=0.03$, the correction model does not improve significantly the results.
@@
     \textbf{Upper panel}: Angular power spectra of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model compared to the $\kappa$TNG prediction.
-\textbf{Lower panel}: fractional angular power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the $\kappa$TNG prediction.
-The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the standard deviation from 100 DLL realisations.
+\textbf{Lower panel}: fractional matter power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the $\kappa$TNG prediction.
+The power spectra and ratios are means over 100 map realisations.
 The spectra are computed for the source redshift $z_s=0.91$.
@@
 \subsection{IA validation}
-In the upper panel of  \autoref{fig:ia_validation}, we present the $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes from our DLL simulations compared to theoretical Halofit predictions \citep{smith2003stable}.
-In the lower panel of the same figure, we show the fractional differences between the mentioned contributions.
+In the upper panel of  \autoref{fig:ia_validation}, we present the $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes from our DLL simulations compared to theoretical Halofit predictions (\citet{smith2003stable}).
+In the lower panel of the same figure, we show the fractional differences between the mentioned contributes.
 To validate the IA infusion, only for this experiment, we run simulations keeping the term $A_{IA}=1$. 
 As we can see, the fractional difference for the $C_{\ell}^{II}$ term features uncertainty consistent with $C_{\ell}^{GG}$ term, validating our infusion process. 
-The signal is computed for the source redshift $z_s=0.91$ and is averaged over 100 realizations.
+The signal is computed for the source redshift $z_s=0.91$ and are averaged over 100 realizations.
  The theoretical predictions are computed using the public \href{https://ccl.readthedocs.io/en/latest/}{Core Cosmological Library} (CCL, \citet{chisari2019core}). 
@@
     \includegraphics[width=\columnwidth]{paper/figures/IA_validation_res.pdf}
-    \caption{ \textbf{Upper panel}: The $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributions from theoretical predictions (dashed line) and DLL simulations. \\
+    \caption{ \textbf{Upper panel}: The $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes from theoretical predictions (dashed line) and DLL simulations. \\
      \textbf{Lower panel}: The fractional difference between the theoretical and simulated $C_{\ell}^{II}$ and $C_{\ell}^{GG}$ contributes.
      We can see that we measure a reduced power spectrum at low $\ell$ compared to the theoretical predictions.
-This can be explained by the small volume of our simulation and the related low number of large-scale modes.
-     The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the standard deviation from 100 realisations.}
+This can be explained by the small volume of our simulation and the related low number of large-scale modes.}
     \label{fig:ia_validation}
@@
  \textbf{Lower panel:} Fractional angular power spectra of DLL simulations and $\kappa$TNG simulations for different source redshift.
-  The power spectra mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
+  The power spectra mean over 100 map realisations.}
      \label{fig:clsktng_comp}
@@
 
-Nevertheless, note that the simulations presented here already achieve a similar resolution of the MassiveNus simulations \citep{liu2018massivenus}, despite being generated using one single GPU.
+Nevertheless, note that the simulations presented here already achieve similar resolution of the MassiveNus simulations (\citet{liu2018massivenus}), despite being generated using one single GPU.
 
-\subsection{Peak counts}\label{peak_sec}
-We compute the starlet peak counts as wavelet coefficients with values higher than their eight neighbors. 
-We define $J_{max}=7$ in \autoref{wav_des}, this starlet filter applied to our map with a pixel size of 0.29 arcmin, corresponds to a decomposition in 7 maps of resolution [0.59, 1.17, 2.34, 4.68, 9.33, 18.79, 37.38] arcmin and a coarse map.
-To satisfy the survey requirement and keep the analysis centred in the range $\ell=[300, 3000]$, we consider only the scales corresponding to [9.33, 18.79, 37.38] arcmin.
+\subsection{Peak counts}
+We compute the Starlet peak counts as wavelet coefficients with values higher than their eight neighbours. 
+We define $J_{max}=7$ in \autoref{wav_des}, this Starlet filter applied to our map with a pixel size of 0.29 arcmin, corresponds to a decomposition in 7 maps of resolution [0.59, 1.17 , 2.34, 4.68, 9.33, 18,79, 37,38] arcmin and a coarse map.
+To satisfy the survey requirement and keep the analysis centred in the range $\ell=[300, 3000]$, we consider only the scales corresponding to [9.33, 18,79, 37,38] arcmin.
 The peaks are counted for 8 linearly spaced bins within the range $(\kappa*\mathcal{W})=[-0.1, 1.]$.
@@
 These results are shown in terms of S/N, where the signal to noise is defined as the ratio between the amplitude of wavelet coefficients over the standard deviation of the noise expected for our survey choice in each wavelet band.
-At wavelet scale $\theta=9.33$ arcmin the differences for the $z_s=0.91$ curves are within the $20\%$ up to $S/N=3$, for $S/N>3$ the accuracy is between the $20\%$ and the $50\%$.
-At larger scale, $\theta=18.79$ arcmin the accuracy is within the $20\%$.
-Finally, at $\theta=37.38$ arcmin the accuracy is within the $15\%$, except $S/N<1$ where the accuracy decreases up to $28\%$.
-The results slightly improve for z=1.30, showing an accuracy within the $35\%$ for scale $\theta=9.33$ arcmin,  within the $10\%$ for $\theta=18.79$ arcmin and $25\%$ for $\theta=37.38$ arcmin.
+At wavelet scale $\theta=9.2$ arcmin the differences for the $z_s=0.91$ curves are within the $20\%$ up to $S/N=3$, for $S/N>3$ the accuracy is between the $20\%$ and the $50\%$.
+At larger scale, $\theta=18.7$ arcmin the accuracy is within the $20\%$.
+Finally, at $\theta=37.4$ arcmin the accuracy is within the $15\%$, except $S/N<1$ where the accuracy decreases up to $28\%$.
+The results slightly improve for z=1.30, showing an accuracy within the $35\%$ for scale $\theta=9.2$ arcmin,  within the $10\%$ for $\theta=18.7$ arcmin and $25\%$ for $\theta=37.4$ arcmin.
  As for the power spectrum case, we observe higher discrepancies at lower redshift, hence we can conclude that, with the current setting of our simulation, we can not model correctly such redshift.
@@
     \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations for different sources redshift.
-The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmins (lower panel).
-  The results mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
+The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmin (lower panel).
+  The results mean over 100 map realisations.}
 \end{figure}
@@
 Fisher forecast is a widely used tool in cosmology for different purposes, e.g.
-investigate the impact of systematic sources or forecast the expected constraining power of the analysis \citep{tegmark1997karhunen}.
-It can be thought as a tool to forecast error from a given experimental setup e quantify how much information we can extract from it.
-The Fisher matrix is defined as the expectation value of the Hessian matrix of the negative log-likelihood $\mathcal{L}(C(\ell);\theta)$:
+investigate the impact of systematic sources or forecast the expected constraining power of the analysis (\citet{tegmark1997karhunen}).
+It can be thought as a tool to forecast error from a given experimental set up e quantify how much information we can extract from it.
+The Fisher matrix is defined as the expectation value of the Hessian matrix of the negative log likelihood $\mathcal{L}(C(\ell);\theta)$:
 \begin{equation}
@@
 So, under the assumption of Gaussian likelihood, the Fisher information matrix provides a lower bound on the expected errors on cosmological parameters.
+% We use 5000 independent simulations at the fiducial cosmology to compute the covariance matrix $C_{ij}$.
 
@@
  \begin{equation}
-     \sigma^2_n= \frac{\sigma_e^2}{A_{pix}n_{gal}},
+     \sigma^2_n= \frac{\sigma_e^2}{A_{pix}^2n_{gal}},
  \end{equation}
-where we set the shape noise $\sigma_e = 0.26$, the pixel area \denise{$A_{pix}=0.29$ arcmin$^2$ and the galaxy number density $n_{gal}=20$ arcmin$^{-2}$. } 
+where we set the shape noise $\sigma_e = 0.26$, the pixel area $A_{pix}=0.29$ and the galaxy number density $n_{gal}=20$. 
 We assume a parameter-independent covariance matrix computed as:
@@
     C_{ij}=\sum_{r=1}^N
-    \frac{(x_i^r-\mu_i)(x_j^r-\mu_j)}{N-1}
+    \frac{(x_i^r-\mu_i)(x_i^r-\mu_)}{N-1}
 \end{equation}
@@
 As mentioned before, we want to focus on a fair comparison between the power spectrum and the peak counts method.
-To be sure we are considering the same scales for both statistics, we apply a wavelet pass-band filter to the maps to isolate particular scales before measuring the power spectrum.
+To be sure we are considering the same scales for both the statistics, we apply a wavelet pass-band filter to the maps to isolate particular scales before measuring the power spectrum.
 We use the same scales used for the Peak counts, i.e.
-we decompose the noisy convergence map in seven images, we sum back only the three maps corresponding to [9.33, 18.79, 37.38] arcmin and compute the angular $C_{\ell}$ on the resulting image.
+we decompose the noisy convergence map in seven images, we sum back only the three maps corresponding to [9.33, 18,79, 37,38] arcmin and compute the angular $C_{\ell}$ on the resulting image.
 An example of the $C_{\ell}$ computed for each individual starlet scale image and for the summed image is depicted in \autoref{window}.
 
-For each map, we compute the angular power spectrum and the peak counts by using our own differentiable code implemented in the TensorFlow framework. \footnote{
+For each map, we compute the angular power spectrum and the peak counts by using our own differentiable code implemented in the Tensorflow framework. \footnote{
 Code publicly available at: \\ \href{https://github.com/LSSTDESC/DifferentiableHOS/tree/main/DifferentiableHOS/statistics}{https://github.com/LSSTDESC/DifferentiableHOS/statistics}  }
@@
     \caption{Example of the filtered $C_{\ell}$ used for the analysis.
-The colored lines show the $C_{\ell}$ computed on maps with a different resolution of the starlet decomposition.
+The coloured lines show the $C_{\ell}$ computed on maps with different resolution of the starlet decomposition.
 Specifically: the blue line (multiscale map) corresponds to $C_{\ell}$ computed on the summed image, the black dashed line (Original map) corresponds to the standard $C_{\ell}$ computed from a non-filtered map.
@@
 
+% As mentioned in the introduction, computing the jacobian doesn't require using the finite difference methods and varying  individual parameter values.
+On the contrary, we exploit the automatic differentiation mechanism of \href{https://www.tensorflow.org/}{\texttt{Tensorflow}}, automatically constructing a procedure able to take a function and compute the derivatives of that function.
 The derivatives with respect to all parameters are evaluated at the fiducial cosmology as the mean of 1500 and 2600 independent measurements for the peak counts and the $C_{\ell}$ respectively.
 Indeed, while the peak counts reach the convergence with $\sim$ 1500 simulations, the $C_{\ell}$ proves to be more sensitive to noise and thus, requires more realizations to convergence.
-In \autoref{fig:Fisher_stab} in appendix B we test the stability of the Fisher contours by changing the number of simulated maps used to compute the jacobian.
+In \autoref{fig:Fisher_stab} in the appendix B we test the stability of the Fisher contours by changing the number of simulated maps used to compute the jacobian.
 
@@
 The contours obtained by the angular $C_{\ell}$ analysis are plotted in grey, the ones for the peak counts in yellow. 
-We find that in constraining $\Omega_c$, $\sigma_8$ and $A_{IA}$ peak counts outperform the power spectrum, while $h$, $n_s$ and $\Omega_b$ parameters, within the limit of our setting, are not constrained by either and are prior dominated.
+We find that in constraining $\Omega_c$, $\sigma_8$ and $A_{IA}$ peak counts outperform power spectrum, while $h$, $n_s$ and $\Omega_b$ parameters, within the limit of our setting, are not constrained by either and are prior dominated.
 
@@
 The most important difference between these two analyses is the parameters they include.
-Whereas \cite{ajani2020constraining} derive constraints on the sum of neutrino masses $M_{\nu}$, the total matter density $\Omega_m$, and the primordial power spectrum normalization $A_s$, we include the five cosmological parameters of the $\Lambda$CDM model and intrinsic alignment amplitude.
+Whereas \cite{ajani2020constraining} derive constraints on the sum of neutrino masses $M_{\nu}$ , the total matter density $\Omega_m$, and the primordial power spectrum normalization $A_s$, we include the five cosmological parameters of the $\Lambda$CDM model and intrinsic alignment amplitude.
 The constraining power of the peak count statistic keeps being higher even in high dimensional cosmological parameter space and when the intrinsic alignment is included.
@@
 non-Gaussian information, we find that for mildly non-linear scales we are considering, the peak counts statistic still constrains the cosmological parameters the most.
+
+% It is interesting look at the combination of the two statistics (green contours), obtained concatenating the power spectrum and the peak counts as observable, since different statistics can respond in a different way to noise and systematics.
+We find that the combined statistics does not add any extra relevant information compared to only peak counts case, this leads us to conclude that, with the specific conditions of the analysis here presented, the peak count statistic alone is a sufficient tool to constrain the cosmological parameters.
 
@@
 		$n_s$ & $\mathcal{N}$ (0.9667,0.08) & 0.9667 \\
+		$w_0$ & $\mathcal{N}$ (-1,0.8) & -1 \\
 		$A_{IA}$ &  $\mathcal{N}$ (0,3) &  0.0 \\
@@
 Finally, we find that the contours on the galaxy intrinsic alignment are significantly better constrained by the peak counts. 
+% Again, the combined statistics does not lead to tighter constraints, confirming that most of the information is provided by the peak counts alone.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/figures/Fisher_n.pdf}
+    \includegraphics[width=\textwidth]{paper/figures/Fisher.pdf}
     \caption{$2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
-The constraints are obtained by applying the starlet Peak counts (yellow contours) computed on noisy maps filtered using a starlet kernel of [$9.33, 18.70, 37.38$] arcmin together and the wavelet pass-band filter for the $C_{\ell}$ statistics (grey contours) as described in \autoref{Validating_simulations_for_LSST_Y}.
+The constraints are obtained applying the Starlet Peak counts (yellow contours) computed on noisy maps filtered using a Starlet kernel of [$9.33, 18.70, 37.38$] arcmin together and the wavelet pass-band filter for the $C_{\ell}$ statistics (grey contours) as described in \autoref{Validating_simulations_for_LSST_Y}.
 The dashed black lines are located at the fiducial parameter values.}
@@
 \section{Discussion}\label{Discussion}
-In this section, we discuss the limitations of the methodology and results obtained in this paper highlighting in particular strategies for future extensions and  applications.
+In this section, we propose to discuss the limitations of the methodology and results obtained in this paper highlighting in particular strategies for future extensions and  applications. 
+%We presented a methodology that allows us to implement a fully differentiable inference analysis for weak cosmic shear,  from cosmological parameters to simulated lensing  maps.
+%The work here presented is only the first step to achieve the requirement of LSST, additional improvement will be integrated in future works.
 
-In this work, we only used a single source plane in our Fisher forecast analysis, which does not allow us to evaluate the full impact that IA would have in a tomographic analysis.
-In particular, we do not have a contribution from the GI term.
+In this work we only used a single source plane in our Fisher forecast analysis, which does not allow us to evaluate the full impact that IA would have in a tomographic analysis.
+In particular, we do not have a contribution of the GI term.
 Many studies have demonstrated that the tomographic analysis can significantly improve constraints on cosmological and IA parameters.
-\citep{king2003separating, heymans2004weak, troxel2015intrinsic}.
-Although it is straightforward to generalize all the results shown in this paper to the tomographic case, this will require increasing the resolution of the simulation at lower redshifts (as illustrated by \autoref{fig:clsktng_comp}) in order to model correctly low redshift bins.
-\denise{Since the maximum number of particles we can adopt in a simulation is closely limited to the GPU memory, we are building a distributed implementation of DLL, which will allow us to increase the resolutions of the simulations to the point of modeling correctly even the smaller scales at the lower redshifts.
-}
+(\citet{king2003separating}, \citet{heymans2004weak}, \citet{troxel2015intrinsic}).
+Although it is straightforward to generalize all the results shown in this paper to the tomographic case, this will require increasing the resolution of the simulation at lower redshifts (as illustrated by \autoref{fig:clsktng_comp})in order to model correctly low redshift bins.
 
 Another direction for further development is the ray tracing methodology.
-In our method, we construct the weak lensing maps assuming the Born approximation.
-However, \cite{petri2017validity} shows that for an LSST-like survey, while the Born approximation leads to negligible parameter bias for the power spectrum, it can lead to significant parameter bias for higher-order statistics.
-Hence, the natural next step will be to implement a ray-tracing algorithm beyond the Born approximation in our pipeline.
-\denise{ We aim to adopt the multiple-lens-plane approximation \citep{1986ApJ...310..568B, Stella_Seitz_1994, jain2000ray, Vale_2003, refId0}, i.e.
-by introducing lens planes perpendicular to the line-of-sight, the deflection experienced by the light rays due to the matter inhomogeneities will be approximated through multiple deflections at the lens planes.
-More specifically, we will implement the memory-efficient ray-tracing scheme proposed by \cite{refId0} in the Tensorflow framework.}
+In our method we constructs the weak lensing maps assuming the Born approximation.
+However \cite{petri2017validity} shows that for an LSST-like survey, while the Born approximation leads to negligible parameter bias for the power spectrum, it can lead to significant parameter bias for higher order statistics.
+Hence, the natural next step will be implement a full ray-tracing algorithm in our pipeline.
 
@@
 adopting the NLA model.
-This physical description for the IA is only an approximation since it does not take into account the tidal torque field.
-In future work, we aim to extend the NLA model by implementing the extended $\delta$NLA model, described by \cite{harnois2021cosmic}.
+We know that such physical description for the IA is only an approximation, since is does not take into account the tidal torque field.
+In future work, we aim to extend the NLA model implementing the extended $\delta$NLA model, described by \cite{harnois2021cosmic}.
 
@@
 We note that this would force us to perform conservative scale cuts in the inference analysis to not include scales affected by baryonic effects.
- A future prospect is to include baryonic effects in the analysis.
-One possible way applicable to our methodology  could be to extend the Hybrid Physical Neural ODE approach and apply more sophisticated models to learn the physics that controls the hydrodynamics simulations.
+ A future prospect is to include baryonic effects into the analysis.
+One possible way applicable to our methodology  could be extend the Hybrid Physical Neural ODE approach and apply more sophisticated models to learn the physics that controls the hydrodynamics simulations.
 
-We expect that the methods illustrated in this paper will be extended to different relevant use-cases.
+We expect that methods illustrated in this paper will be extended in different relevant use-cases.
 A particularly suitable example is related to the application of algorithms such as the Variational Inference and the Hamiltonian Monte Carlo that are widely used in the Bayesian inference context and were until now excluded due to the lack of derivatives.
-A further example is provided by \cite{zeghal2022neural}, which demonstrates that having access to the gradients of the forward model is beneficial to constrain the posterior density estimates.
+A further example is provided by \cite{zeghal2022neural}, which demonstrate that having access to the gradients of the forward model is beneficial to constrain the posterior density estimates.
 
 \section{Conclusions}\label{Conclusions}
-In this paper, we have presented the Differentiable Lensing Lightcone (DLL) model, a fast lensing lightcone simulator providing access to the gradient. 
-We extended the public FlowPM N-body code, implementing the Born approximation in the Tensorflow framework to create non-Gaussian convergence maps of weak gravitational lensing.
+In this paper, we have presented the Differentiable Lensing Lightcone (DLL) model, a  fast lensing lightcone simulator providing having access to the gradient. 
+We extended the public FlowPM N-body code, implementing ray-tracing in the Tensorflow framework to create non-Gaussian convergence maps of weak gravitational lensing.
 To allow DLL to run at low resolution without affecting significantly the accuracy, we complement the FlowPM N-body code with the Hybrid-Physical Neural scheme, a new correction scheme for quasi N-body PM solver, based on Neural Network implemented as a Fourier-space filter.
@@
 To do this, we run simulations following the evolution of $128^3$ particles and we produce weak lensing convergence maps for several redshift sources. 
-We show that, despite being generated at low computation costs, we recover a good match for redshift equal or higher than $z=0.91$. 
+We show that, despite being generated at low computation costs, we recover good match for redshift equal or higher than $z=0.91$. 
 To demonstrate the potential of our tool, as a first use case, we exploit the automatic differentiability of the simulations to do Fisher forecast. 
@@
 \begin{itemize}
-    \item  We confirm that the peak count statistics outperform the two-point statistics as found in \cite{ajani2020constraining},
+    \item  We confirm that the peak count statistics outperform the two point statistics as found in \cite{ajani2020constraining},
  even in high dimensional cosmological and nuisance parameter space.
@@
 BH is supported by the AI Accelerator program of the Schmidt Futures Foundation.
-The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
+The presented work used computing resources provided by DESC at the the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
 Department of Energy under Contract No.
@@
 \section{Validation against a theory prediction}
-We show the $2\sigma$ constraints obtained from our Fisher analysis of standard $C_{\ell}$ (orange) and the theoretical prediction from halofit (blue contours) in \autoref{fig:Fisher_result_theory}.
+We show the $2\sigma$ constraints obtained from our Fisher analysis of standard $C_{\ell}$ (blue contours) and the theoretical prediction from halofit (orange) in \autoref{fig:Fisher_result_theory}.
 The dashed black contours define the prior used for the forecasting.
-The analysis is performed for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
+The analysis is performed for one single source redshift at z=0.91 and the the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
 
 The constraints from the theoretical predictions
-are compatible with the ones obtained from the mock DLL maps for all cosmological parameters, except $n_s$.
-\denise{Indeed, despite sharing the same direction of the degeneracy, the theoretical contours for $n_s$ are narrower compared to the ones obtained in our analysis.
-In general, this translates into an increased uncertainty in constraining $n_s$, most likely due to the deficit in power observed for the $C_{\ell}$ at small scales.
-}
+are comparable to the ones obtained from the mock DLL maps for all cosmological parameters, except $w_0$.
+In this case, the results obtained from our maps lead to narrower constraints, but despite this, the two analyses share the same direction of the degeneracy except for the pair $w_0$ and $n_s$.
 
-The theoretical predictions are computed using the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}. 
+The theoretical prediction are computed using the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}. 
 We want to highlight that both the theoretical Fisher matrices and the ones from our analysis are obtained by automatic differentiation.
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/figures/Fisher_IA_theory_n.pdf}
+    \includegraphics[width=\textwidth]{paper/figures/Fisher_IA_theory.pdf}
     \caption{ $2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
     We compare the Fisher matrix constraints on cosmological parameters and $A_{IA}$ amplitude obtained with the $C_{\ell}$ from our mock maps (orange) and the theoretical $C_{\ell}$ (blue) obtained from the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}.
-    In both cases, the constraints are obtained by applying  the wavelet pass-band filter for the $C_{\ell}$ as described in \autoref{Validating_simulations_for_LSST_Y}.
+    In both cases, the constraints are obtained applying the the wavelet pass-band filter for the $C_{\ell}$ as described in \autoref{Validating_simulations_for_LSST_Y}.
 The dashed black contours are the prior used for the forecasting.}
@@
     \centering
-        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_ps_new.pdf}
-        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_peak_1sigma_new.pdf}
+        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_ps.pdf}
+        \includegraphics[width=0.65\textwidth]{paper/figures/Fisher_stability_peak.pdf}
     \caption{ $1\sigma$ Fisher contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y} for the $C_{\ell}$ (upper panel) and the Peak counts (lower panel).
@@
 \end{figure*}
-\denise{
-\section{Validation with higher resolutions simulations}
-In \autoref{Validating_simulations_for_LSST_Y}, we presented a validation of our simulations by comparing the statistics from DLL and $\kappa$TNG-Dark.
-In particular, we have seen a discrepancy on small scales for both the $C_{\ell}$ and the peak counts.
-We have attributed this bias to the low resolution of the simulations.
-Therefore, to justify this assumption, we simulate convergence maps of higher resolution, i.e, we raise the number of particles but keep the same box of 205$^3$($h^{-1}$Mpc$)^3$ in the simulation.
-In the left panel of  \autoref{fig:ps_comp_high}, we present the angular power spectrum computed from our DLL with the original number count of particles ($128^3$) and the power spectrum computed from higher resolutions DLL simulations ($212^3$).
-The two outputs are compared to the $\kappa$TNG predictions.
-In the right panel  of \autoref{fig:ps_comp_high} the fractional differences between the convergence power spectra from the two maps and the $\kappa$TNG are shown.
-We can see that, by increasing the number of particles, we can improve the accuracy of the lensing $C_{\ell}$ up to $~20\%$.
-As for the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different resolutions.
-We use the same wavelet decomposition presented in \autoref{peak_sec}.
-As for the power spectrum, we note the same tendency to recover better accuracy when the resolution is increased.
 
-Finally, we reproduce the results of the Fisher analysis for the intrinsic alignment parameter $A_{IA}$ with higher-resolution simulations.
-We adopt the same Forecast criteria presented in \autoref{Application_Fisher_forecast_for_HOS}.
-However, for this specific test, we compute the derivatives numerically using the finite differences.
-The step sizes used for these variations are $\Delta x_{IA}=0.15$ for the $C_{\ell}$ and $\Delta x_{IA}=1.2$ for the peak counts.
-% These step sizes have been tested by comparing the Fisher results obtained from those to the ones obtained from different step sizes. 
-In order to check the reliability of the numerical derivatives, we investigate the stability of the Fisher forecast against different step sizes used to compute them.
-The derivatives are computed as the mean of 3000 independent realizations for both $C_{\ell}$ and peak counts.
+% \section{Impact of the different starlet scales}
+% In \autoref{fig:Fisher_result_scales} we compare the constraints relative to map filtered using [$9.33, 18.70, 37.38$] arcmin together and as single scales.
+The results are obtained from the fiducial analysis  without applying any prior.
+% As for the other results in the analysis, to compute the fisher matrix, both the jacobian and the mean of the peak statistic are averaged over 1500 and 5000 independent realizations, computed on maps after applying Gaussian noise and filtered them using a starlet filter.
+As it can be seen, the different scales contribute in different way to the final contours.
+In particular, for all the cosmological parameters except $w_0$, the setting [9.33, 18.76, 9.33+18.76+37.38 ] arcmin shares the same direction of the degeneracy, but differ for size of the ellipse.
+On the contrary, the scale 37.38 arcmin leads to larger contours and different orientation.
+\denise{not sure if this is useful, and if show this plot or the one with the prior}
 
- We confirm the peak counts provide the most stringent constraints on the galaxy intrinsic alignment amplitude $A_{IA}$.
-As for the full analysis, we tested the stability of the Fisher forecast by varying the number of simulated maps used to compute the derivatives.
-In \autoref{tuning_high} we present the $1\sigma$ error on $A_{IA}$ when varying the number of independent realizations used to compute the derivatives.
-It is interesting to note, that, even in this case, the derivatives of the $C_{\ell}$ can not be considered fully converged.
-However, as can be noted from the stability plots of \autoref{tuning_high}, the noise in the derivatives leads to tighter constraints in the Fisher forecast.
-Hence, the fully converged derivatives of the $C_{\ell}$ would result in even broader constraints, without changing the results we found.
-
-\renewcommand{\thefigure}{C\arabic{figure}}
-\setcounter{figure}{0}
-\begin{figure*}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/cls_DLL_vs_ktng_high.pdf}
-        \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_high.pdf}
-    \caption{
-    \textbf{Left panel}: Angular power spectra of PM simulations with original resolution (number count 128$^3$, blue line) and higher resolution (number count 212$^3$, red line) compared to the $\kappa$TNG prediction.
-\textbf{Right panel}: fractional angular power spectrum of PM simulations with original and higher resolution and the $\kappa$TNG prediction.
-The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the error on the mean.
-The spectra are computed for the source redshift $z_s=0.91$.
-}
-    \label{fig:ps_comp_high}
-\end{figure*}
-
-\renewcommand{\thefigure}{C\arabic{figure}}
-\setcounter{figure}{1}
-\begin{figure*}\label{peaks_high}
-    \centering
-    \includegraphics[width=\columnwidth]{paper/figures/res_peak_DLL_vs_ktng_high.pdf}
-    \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations.
-The results are shown for the number counts $128^3$ (blue lines) and $212^3$ (orange lines).
-The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmins (lower panel).
-  The results mean over 100 independent map realisations, the shaded regions represent the error on the mean. The statistics are computed for the source redshift $z_s=0.91$. }
-\end{figure*}
-
-\renewcommand{\thefigure}{C\arabic{figure}}
-\setcounter{figure}{2}
-\begin{figure*}\label{tuning_high}
-    \centering
-     \includegraphics[width=\columnwidth]{paper/figures/tuning_snsim_cls.pdf}
-        \includegraphics[width=\columnwidth]{paper/figures/tuning_snsim_peaks.pdf}
-    \caption{
-    $1\sigma$ error on $A_{IA}$ derived for one single source redshift at z=0.91 for different numbers of independent realizations used to mean the Jacobian in the \autoref{Fisher_matrix}.
-The results are shown for the $C_{\ell}$ (left panel) and the peak counts (right panel).
-}
-\end{figure*}
-
-\renewcommand{\thefigure}{C\arabic{figure}}
-\setcounter{figure}{3}
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{paper/figures/Fisher_IA.pdf}
-    \caption{$1\sigma$ error on $A_{IA}$ for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}, from mock simulations with $212^3$ particles.
-The results are obtained by applying the starlet Peak counts (yellow contours) computed on noisy maps filtered using a starlet kernel of [$9.33, 18.70, 37.38$] arcmin together and the wavelet pass-band filter for the $C_{\ell}$ statistics (grey contours) as described in \autoref{Validating_simulations_for_LSST_Y}.
-}
-     \label{fig:Fisher_result_ia}
-\end{figure*}
-}
+% \renewcommand{\thefigure}{C\arabic{figure}}
+% \setcounter{figure}{0}
+%  \begin{figure*}
+%     \centering
+%     \includegraphics[width=\textwidth]{paper/figures/Fisher_different_scales.pdf}
+%     \caption{ $2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}. 
+%     Constraints corresponding to 9.33 arcmin map are shown in blue, the ones coming from 18.70 arcmin in yellow, the ones coming from 37.38 arcmin in black and the full wavelet decomposition as taken into account in this paper in red.
+% The dashed black lines are located at the fiducial parameter values.}
+%      \label{fig:Fisher_result_scales}
+% \end{figure*}
 

### 2023-05-10 paper/journal_paper.tex
A&A template

--- 2023-03-16 paper/paper.tex
@@
-\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
-\documentclass[twocolumn,twocolappendix]{aastex63}
+\documentclass{aa}
 
-% Add your own macros here:
-\pdfoutput=1 %for arXiv submission
-%\usepackage{amsmath,amssymb,amstext}
-\usepackage{amsmath,amstext}
-\usepackage[T1]{fontenc}
-\usepackage{apjfonts}
-\usepackage{ae,aecompl}
-\usepackage[utf8]{inputenc}
-\usepackage[figure,figure*]{hypcap}
-\usepackage{hyperref}
-\usepackage{url}
-\urlstyle{same}
-\usepackage{lineno}
-\linenumbers
-%\modulolinenumbers[2]
-
-\newcommand{\placeholder}[1]{\textit{PLACEHOLDER: #1}}
-
-\newcommand{\jl}[1]{{\color{orange}JL: #1}}
-\newcommand{\EiffL}[1]{{\color{cyan}FL: #1}}
-\newcommand{\denise}[1]{{\color{red}DL: #1}}
-\usepackage{microtype}
 \usepackage{graphicx}
-\usepackage{fontawesome}
-\newcommand{\github}{\href{https://github.com/DifferentiableUniverseInitiative/flowpm/tree/master}{\faGithub}}
-\newcommand{\nblink}[1]{\href{https://github.com/DifferentiableUniverseInitiative/flowpm/tree/nbody_ode/notebooks/#1.ipynb}{\faFileCodeO}}
-% header settings
-\shorttitle{Differentiable Lensing Simulations}
-\shortauthors{Lanzieri et al.\ (LSST~DESC)}
-
-% ======================================================================
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{txfonts}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}
 
 \begin{document}
+
 \title{Forecasting the power of Higher Order Weak Lensing Statistics with automatically differentiable simulations}
-\input{authors}
 
-\begin{abstract}
-We present the Differentiable Lensing Lightcone (DLL), a fully differentiable physical model designed for being used as a forward model in Bayesian inference algorithms requiring access to derivatives of lensing observables with respect to cosmological parameters.
-We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones \denise{and implementing the Born approximation} in the Tensorflow framework.
+\author{Denise Lanzieri \inst{1}
+\and
+Fran\c{c}ois Lanusse \inst{2}
+\and
+Chirag Modi \inst{3}
+\and 
+Benjamin Horowitz \inst{4, 5}
+\and
+Joachim Harnois-Déraps \inst{6}
+\and
+Jean-Luc Starck \inst{2}
+\and
+The LSST Dark Energy Science Collaboration (LSST DESC)
+}
+\institute{Université Paris Cité, Université Paris-Saclay, CEA, CNRS, AIM, F-91191, Gif-sur-Yvette, France
+\and
+Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France;
+\and
+Center for Computational Astrophysics,
+Center for Computational Mathematics,
+Flatiron Institute, New York, NY 10010, USA;
+\and
+Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, 94720, CA, USA;
+\and
+Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA
+\and
+School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU Newcastle-upon-Tyne, UK
+}
+
+\date{Received xxxx; accepted xxx}
+
+% \abstract{}{}{}{}{} 
+% 5 {} token are mandatory
+
+  \abstract
+  % context heading (optional)
+  % {} leave it empty if necessary  
+   {}
+  % aims heading (mandatory)
+   {We present the Differentiable Lensing Lightcone (DLL), a fully differentiable physical model designed for being used as a forward model in Bayesian inference algorithms requiring access to derivatives of lensing observables with respect to cosmological parameters.
+}
+  % methods heading (mandatory)
+   {We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones and implementing the Born approximation in the Tensorflow framework.
 Furthermore, DLL is aimed at achieving high accuracy with low computational costs.
@@
 As opposed to forecasts based on finite differences, these statistics can be analytically differentiated with respect to cosmology, or any systematics included in the simulations at the same computational cost of the forward simulation.
-We find that the peak counts outperform the power spectrum on the cold dark matter parameter $\Omega_c$, on the amplitude of density fluctuations $\sigma_8$, and on the
-amplitude of the intrinsic alignment signal $A_{IA}$.
-\end{abstract}
+}
+  % results heading (mandatory)
+   {We find that the peak counts outperform the power spectrum on the cold dark matter parameter $\Omega_c$, on the amplitude of density fluctuations $\sigma_8$, and on the
+amplitude of the intrinsic alignment signal $A_{IA}$.}
+  % conclusions heading (optional), leave it empty if necessary 
+   {}
 
-\keywords{methods: statistical -- dark energy}
+   \keywords{methods: statistical -- dark energy
+               }
 
-%\accepted{}
-%\submitjournal{the Astrophysical Journal Supplement}
-
-%\tableofcontents%-----------------------------
-%===========================
-% BEGINNING OF THE MAIN TEXT
-%===========================
+   \maketitle
+%
+%-------------------------------------------------------------------
 
@@
 The upcoming stage-IV surveys, such as the Legacy Survey of Space and Time (LSST) of the Vera C.
-Rubin Observatory \citep{ivezic2019lsst}, the Nancy Grace Roman Space Telescope \citep{spergel2015wide}, and  the Euclid Mission \citep{laureijs2011euclid}, will provide measurements of billions of galaxy shapes with unprecedented accuracy, which in turn will lead to tight constraints on dark energy models \citep[e.g.][]{mandelbaum2018lsst}.
+Rubin Observatory \cite{ivezic2019lsst}, the Nancy Grace Roman Space Telescope \citep{spergel2015wide}, and  the Euclid Mission \citep{laureijs2011euclid}, will provide measurements of billions of galaxy shapes with unprecedented accuracy, which in turn will lead to tight constraints on dark energy models \citep[e.g.][]{mandelbaum2018lsst}.
 
@@
  This has led to the introduction of a number of  higher-order statistics to access the non-Gaussian information from weak lensing data: 
-the weak lensing one point PDF \citep{liu2019constraining, uhlemann2020fisher, boyle2021nuw}, lensing peak counts \citep{liu2015cosmology, liu2015cosmological, lin2015new, kacprzak2016cosmology, peel2017cosmological, shan2018kids, martinet2018kids, ajani2020constraining, harnois2021cosmic, zurcher2022dark}, Minkowski functionals \citep{kratochvil2012probing, petri2013cosmology}, moments of mass maps \citep{gatti2021dark}, wavelet and scattering transforms \citep{ajani2021starlet, cheng2021weak},, and 3 point statistics \citep{takada2004cosmological, semboloni2011weak, rizzato2019tomographic, halder2021integrated}.
+the weak lensing one point PDF \citep{liu2019constraining, uhlemann2020fisher, boyle2021nuw}, lensing peak counts \citep{liu2015cosmology, liu2015cosmological, lin2015new, kacprzak2016cosmology, peel2017cosmological, shan2018kids, martinet2018kids, ajani2020constraining, harnois2021cosmic, zurcher2022dark}, Minkowski functionals \citep{kratochvil2012probing, petri2013cosmology}, moments of mass maps \citep{gatti2021dark}, wavelet and scattering transforms \citep{ajani2021starlet, cheng2021weak}, and 3 point statistics \citep{takada2004cosmological, semboloni2011weak, rizzato2019tomographic, halder2021integrated}.
 
@@
 data structures representing units of computation), then it works backward through the graph by applying the chain rule at each node.
-\denise{Unlike MADlens, our tool is GPU-based and provides derivatives with respect to all the cosmological parameters.
-There are also differences in the implementation of various functions to improve accuracy and speed.}
+Unlike MADlens, our tool is GPU-based and provides derivatives with respect to all the cosmological parameters.
+There are also differences in the implementation of various functions to improve accuracy and speed.
 
@@
 
-This paper is structured as follows: in \autoref{weak_lesning_modeling} we briefly review the weak lensing modeling including the theoretical framework and the summary statistics used in this work.
+This paper is structured as follows: in \ref{weak_lesning_modeling} we briefly review the weak lensing modeling including the theoretical framework and the summary statistics used in this work.
 In \autoref{Fast_and_Differentiable_Lensing_Simulations} we introduce the numerical simulations illustrating the numerical methods used to generate mock WL maps.
@@
 We finally discuss our results and present our conclusions afterward, in \autoref{Discussion} and \autoref{Conclusions}.
+
+%--------------------------------------------------------------------
 
@@
 In the limit of weak-field metric (small $\Phi$), the integral in \autoref{sep} can be approximated by considering the series expansion in power of $\Phi$ and truncating the series at the first term.
-With this assumptions, given that $\nabla_{\bot}\boldsymbol{\Phi}^0$ not dependent from $\boldsymbol{\theta}$, the Jacobian matrix can be written as:
+With these assumptions, given that $\nabla_{\bot}\boldsymbol{\Phi}^0$ is not dependent from $\boldsymbol{\theta}$, the Jacobian matrix can be written as:
 \begin{equation}
@@
  -\frac{2}{c^2}
-= \int_0^{\chi} d\chi'
+ \int_0^{\chi} d\chi'
    \frac{f_k(\chi-\chi')f_k(\chi')}{f_k(\chi)f_k(\chi')}
@@
 where $\bar{D}(z) \equiv D(1+z)$ \citep{harnois2021cosmic}.
-\denise{Under the Limber
+Under the Limber
 approximation the projected angular power spectra for the IA terms become:
@@
 \end{align}
-}
 
@@
 This multiscale approach is well-suited for the study of astronomical data since their complex hierarchical structure.
-\denise{A wavelet function $\psi(x)$ is a function that satisfies the admissibility condition:
+A wavelet function $\psi(x)$ is a function that satisfies the admissibility condition:
 \begin{equation}
@@
 
-where $\psi_{a,b}$ is the so-called \textit{daughter wavelets}, scaled and translated version of the \textit{mother} wavelet, with $a$ and $b$ scaling and translation parameters.
+where $\psi_{a,b}$ are the so-called \textit{daughter wavelets}, scaled and translated version of the \textit{mother} wavelet, with $a$ and $b$ scaling and translation parameters.
 The continuous wavelets transform is defined from the projections of a function $f \in L_2(\mathbb{R})$ onto the family of daughter wavelets.
@@
 \begin{equation}
-    W_f(a,b)=\int_{\mathbb{R}} f(x)\psi^{*}_{a,b}(x)dx=\frac{a}{\sqrt{a}}\int_{\mathbb{R}}f(x)\psi^{*}\left( \frac{x-b}{a}\right)dx ,
+    W_f(a,b)=\int_{\mathbb{R}} f(x)\psi^{*}_{a,b}(x)dx=\frac{1}{\sqrt{a}}\int_{\mathbb{R}}f(x)\psi^{*}\left( \frac{x-b}{a}\right)dx ,
 \end{equation}
-with $\psi^{*}$ the complex conjugate of $\psi$, and $ \forall a \in \mathbb{R}^{+}$, $ b \in \mathbb{R.}$  }
+with $\psi^{*}$ the complex conjugate of $\psi$, and $ \forall a \in \mathbb{R}^{+}$, $ b \in \mathbb{R.}$  
 In this work, we filter the original convergence maps with the starlet transform, an isotropic and undecimated (i.e.
@@
 \end{equation}
-\denise{
-The N-dimensional scaling functions can be built starting from the separable product of N $\phi_{1D}$: $\phi(x_1,x_2)=\phi_{1D}(x_1)\phi_{1D}(x_2)$. }
+
+The N-dimensional scaling functions can be built starting from the separable product of N $\phi_{1D}$: $\phi(x_1,x_2)=\phi_{1D}(x_1)\phi_{1D}(x_2)$. 
 Each set of wavelet coefficients $w_j$ is obtained as the convolution of the input map with the corresponding wavelet kernel.
@@
 To circumvent this issue, one approach is to rely on generating a suite of numerical simulations.
-In the following section, we introduce our weak lensing map simulation procedure, including a description of the N-body simulator and the \denise{lightcone construction}.
+In the following section, we introduce our weak lensing map simulation procedure, including a description of the N-body simulator and the lightcone construction.
 
@@
 \end{equation}
-with $\mathbf{x}$ and $\mathbf{v}$ the position and the velocity of the particles, \denise{\textit{a} the cosmological scale factor, $E(a)$ the ratio between the Hubble expansion rate and the Hubble parameter and $\mathbf{F}$ the gravitational force experienced by the dark matter particles in the mesh.}
+with $\mathbf{x}$ and $\mathbf{v}$ the position and the velocity of the particles, \textit{a} the cosmological scale factor, $E(a)$ the ratio between the Hubble expansion rate and the Hubble parameter and $\mathbf{F}$ the gravitational force experienced by the dark matter particles in the mesh.
 
@@
  \begin{equation}
-     \mathcal{F}(\textbf{z}(t_1))=   \mathcal{F} (\text{ODESolve}(\textbf{z}(t_0),f,t_0,t_1, \theta)).
+     \mathcal{F}(\textbf{z}(t_1))=   \mathcal{F} (\text{ODESolve}(\textbf{z}(t_0),f,t_0,t_1, \theta))
  \end{equation}
@@
 In the adjoint ODE approach, this is instead replaced by solving another ODE backward in time when evaluating the gradient.
-We illustrate the potential of differentiating through ODE solvers, highlighting the fact that the simulations and the gradients presented in this paper are computing using one single GPU for $128^3$ particles.
+We illustrate the potential of differentiating through ODE solvers, highlighting the fact that the simulations and the gradients presented in this paper are computed using one single GPU for $128^3$ particles.
 
@@
 contributions of the two terms.
-\denise{By comparing the results obtained from different values of $\lambda$ in the fiducial setting and outside the training regime, we find that $\lambda= 0.1$ provided the optimal balance in terms of overall correction and overfit.
-}
+By comparing the results obtained from different values of $\lambda$ in the fiducial setting and outside the training regime, we find that $\lambda= 0.1$ provided the optimal balance in terms of overall correction and overfit.
 
@@
 After creating a Cartesian grid of coordinates, each slice is interpolated onto sky coordinates.
-\denise{.
 This procedure differs from the one implemented in the MADLens package \citep{bohm2021madlens}.
-In MADLens the lightcone is built by translating the redshift of the particles into distances, then the particles are projected onto the convergence map at the proper evolution step corresponding to that distance.}
+In MADLens the lightcone is built by translating the redshift of the particles into distances, then the particles are projected onto the convergence map at the proper evolution step corresponding to that distance.
 
@@
 \end{align}
-where $\sigma_g$ defines the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $\sim $ refers to the Fourier transformed quantities, $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight, and the indices $(i,j)$ represent the $x$ or $y$ component.
+where $\sigma_g$ defines the smoothing scale of a two-dimensional smoothing kernel $\mathcal{G}_{2D}$, the tilde symbols $\sim $ refers to the Fourier transformed quantities and $\textbf{k}_{\bot}$ denotes the two Fourier wave-vector components perpendicular to the line of sight.
 Combing \autoref{complex_e} and \autoref{trans_ell} we can calculate the intrinsic alignment as part of the convergence map:
@@
 At redshift $z=0.91$ most of the missing
-power is recovered by the HPN correction up to $k \sim 1$, after which the method overemphasizes the small-scale power.
-\denise{In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.}
+power is recovered by the HPN correction up to $k\sim 1$, after which the method overemphasizes the small-scale power.
+In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.
 
@@
 We present the results in \autoref{peaks_z}.
-These results are shown in terms of S/N, where the signal to noise is defined as the ratio between the amplitude of wavelet coefficients over the standard deviation of the noise expected for our survey choice in each wavelet band.
+These results are shown in terms of S/N, where the signal to noise is defined as the ratio between the amplitude of wavelet coefficients over the noise expected for our survey choice.
 At wavelet scale $\theta=9.33$ arcmin the differences for the $z_s=0.91$ curves are within the $20\%$ up to $S/N=3$, for $S/N>3$ the accuracy is between the $20\%$ and the $50\%$.
@@
 investigate the impact of systematic sources or forecast the expected constraining power of the analysis \citep{tegmark1997karhunen}.
-It can be thought as a tool to forecast error from a given experimental setup e quantify how much information we can extract from it.
+It can be thought as a tool to forecast error from a given experimental setup and quantify how much information we can extract from it.
 The Fisher matrix is defined as the expectation value of the Hessian matrix of the negative log-likelihood $\mathcal{L}(C(\ell);\theta)$:
@@
  \end{equation}
-where we set the shape noise $\sigma_e = 0.26$, the pixel area \denise{$A_{pix}=0.29$ arcmin$^2$ and the galaxy number density $n_{gal}=20$ arcmin$^{-2}$. } 
+where we set the shape noise $\sigma_e = 0.26$, the pixel area $A_{pix}=0.29$ arcmin$^2$ and the galaxy number density $n_{gal}=20$ arcmin$^{-2}$.  
 We assume a parameter-independent covariance matrix computed as:
@@
 Although it is straightforward to generalize all the results shown in this paper to the tomographic case, this will require increasing the resolution of the simulation at lower redshifts (as illustrated by \autoref{fig:clsktng_comp}) in order to model correctly low redshift bins.
-\denise{Since the maximum number of particles we can adopt in a simulation is closely limited to the GPU memory, we are building a distributed implementation of DLL, which will allow us to increase the resolutions of the simulations to the point of modeling correctly even the smaller scales at the lower redshifts.
-}
+Since the maximum number of particles we can adopt in a simulation is closely limited to the GPU memory, we are building a distributed implementation of DLL, which will allow us to increase the resolutions of the simulations to the point of modeling correctly even the smaller scales at the lower redshifts.
 
@@
 Hence, the natural next step will be to implement a ray-tracing algorithm beyond the Born approximation in our pipeline.
-\denise{ We aim to adopt the multiple-lens-plane approximation \citep{1986ApJ...310..568B, Stella_Seitz_1994, jain2000ray, Vale_2003, refId0}, i.e.
+ We aim to adopt the multiple-lens-plane approximation \citep{1986ApJ...310..568B, Stella_Seitz_1994, jain2000ray, Vale_2003, refId0}, i.e.
 by introducing lens planes perpendicular to the line-of-sight, the deflection experienced by the light rays due to the matter inhomogeneities will be approximated through multiple deflections at the lens planes.
-More specifically, we will implement the memory-efficient ray-tracing scheme proposed by \cite{refId0} in the Tensorflow framework.}
+More specifically, we will implement the memory-efficient ray-tracing scheme proposed by \cite{refId0} in the Tensorflow framework.
 
@@
 
-\section*{Acknowledgments}
-BH is supported by the AI Accelerator program of the Schmidt Futures Foundation.
-The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
+\begin{acknowledgements}
+
+DESC acknowledges ongoing support from the IN2P3 (France), the STFC 
+(United Kingdom), and the DOE, NSF, and LSST Corporation (United States).  
+DESC uses resources of the IN2P3 Computing Center 
+(CC-IN2P3--Lyon/Villeurbanne - France) funded by the Centre National de la
+Recherche Scientifique; the National Energy Research Scientific Computing
+Center, a DOE Office of Science User Facility supported under Contract 
+No.\ DE-AC02-05CH11231; STFC DiRAC HPC Facilities, funded by UK BEIS National 
+E-infrastructure capital grants; and the UK particle physics grid, supported
+by the GridPP Collaboration.  This work was performed in part under DOE 
+Contract DE-AC02-76SF00515.
+This work was granted access to the HPC/AI resources of IDRIS under the allocation 2022-AD011013922 made by GENCI.
+BH is supported by the AI Accelerator program of the Schmidt Futures Foundation; JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1); The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
 Department of Energy under Contract No.
 DEAC02-05CH11231;
-%=====================
-% END OF THE MAIN TEXT
-%=====================
+This paper has undergone internal review in the LSST Dark Energy Science Collaboration. We thank the internal reviewers, Virginia Ajani, William Coulton, and Jia Liu for their constructive comments.
+Author contributions to this work are as follows: Denise Lanzieri led the analysis and the writing of the paper.
+Jean-Luc Starck provided his expertise on wavelet peak counting and higher-order weak lensing statistics.
+All the authors provided feedback on
+the text.
+\end{acknowledgements}
 
-%%%%%%%%%%%%%%%%%%%%%  APPENDIX %%%%%%%%%%%%%%%%%%
-\appendix
+% WARNING
+%-------------------------------------------------------------------
+% Please note that we have included the references to the file aa.dem in
+% order to compile it, but we ask you to:
+%
+% - use BibTeX with the regular commands:
+%   \bibliographystyle{aa} % style aa.bst
+%   \bibliography{Yourfile} % your references Yourfile.bib
+%
+% - join the .bib files when you upload your source files
+%-------------------------------------------------------------------
+\bibliographystyle{aa} % style aa.bst
+\bibliography{paper/biblio} 
+\begin{appendix}
 
@@
 are compatible with the ones obtained from the mock DLL maps for all cosmological parameters, except $n_s$.
-\denise{Indeed, despite sharing the same direction of the degeneracy, the theoretical contours for $n_s$ are narrower compared to the ones obtained in our analysis.
+Indeed, despite sharing the same direction of the degeneracy, the theoretical contours for $n_s$ are narrower compared to the ones obtained in our analysis.
 In general, this translates into an increased uncertainty in constraining $n_s$, most likely due to the deficit in power observed for the $C_{\ell}$ at small scales.
-}
 
-The theoretical predictions are computed using the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}. 
+The theoretical predictions are computed using the public library \texttt{jax-cosmo} \citep{Campagne_2023}. 
 We want to highlight that both the theoretical Fisher matrices and the ones from our analysis are obtained by automatic differentiation.
@@
     \caption{ $2\sigma$ contours derived for one single source redshift at z=0.91 and the survey setup presented in \autoref{Validating_simulations_for_LSST_Y}.
-    We compare the Fisher matrix constraints on cosmological parameters and $A_{IA}$ amplitude obtained with the $C_{\ell}$ from our mock maps (orange) and the theoretical $C_{\ell}$ (blue) obtained from the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}}.
+    We compare the Fisher matrix constraints on cosmological parameters and $A_{IA}$ amplitude obtained with the $C_{\ell}$ from our mock maps (orange) and the theoretical $C_{\ell}$ (blue) obtained from the public library  \href{https://github.com/DifferentiableUniverseInitiative/jax_cosmo}{\texttt{jax-cosmo}} \citep{Campagne_2023}.
     In both cases, the constraints are obtained by applying  the wavelet pass-band filter for the $C_{\ell}$ as described in \autoref{Validating_simulations_for_LSST_Y}.
@@
 \end{figure*}
-\denise{
+
 \section{Validation with higher resolutions simulations}
@@
 We can see that, by increasing the number of particles, we can improve the accuracy of the lensing $C_{\ell}$ up to $~20\%$.
-As for the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different resolutions.
+In \autoref{peaks_high}, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different resolutions.
 We use the same wavelet decomposition presented in \autoref{peak_sec}.
@@
 \end{figure*}
-}
 
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-\bibliography{biblio.bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{appendix}
 \end{document}

### 2023-06-06 paper/journal_paper.tex
Submitted version

@@
 
-\author{Denise Lanzieri \inst{1}
+\author{Denise Lanzieri \inst{1}\fnmsep\thanks{ Contact: denise.lanzieri@cea.fr}
 \and
@@
 \and
-Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France;
+Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France
 \and
@@
 Center for Computational Mathematics,
-Flatiron Institute, New York, NY 10010, USA;
+Flatiron Institute, New York, NY 10010, USA
 \and
-Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, 94720, CA, USA;
+Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, 94720, CA, USA
 \and
@@
 
-   \keywords{methods: statistical -- dark energy
-               }
+\keywords{methods: statistical -- cosmology: large-scale structure of Universe --gravitational lensing:weak}
 
@@
 \subsection{{Cosmic shear}}
-Weak gravitational lensing is a powerful probe to infer the projected matter density distribution between an observer and a source.
+Weak gravitational lensing is a powerful probe to infer the distribution of matter density between an observer and a source.
 The effect of gravitational lensing 
@@
 This paper has undergone internal review in the LSST Dark Energy Science Collaboration. We thank the internal reviewers, Virginia Ajani, William Coulton, and Jia Liu for their constructive comments.
-Author contributions to this work are as follows: Denise Lanzieri led the analysis and the writing of the paper.
-Jean-Luc Starck provided his expertise on wavelet peak counting and higher-order weak lensing statistics.
-All the authors provided feedback on
-the text.
+Author contributions to this work are as follows: Denise Lanzieri led the analysis and the writing of the paper. Fran\c{c}ois Lanusse designed the project, contributed to code and text development.
+Chirag Modi contributed to the PM code and text development.
+Benjamin Horowitz contributed to the text and made minor code developments.
+Joachim Harnois-Déraps contributed to the intrinsic alignment modeling, provided general advice on simulations, and contributed to the text.
+Jean-Luc Starck provided expertise on wavelet peak counting and higher-order weak lensing statistics. 
 \end{acknowledgements}

### 2023-07-23 paper/journal_paper.tex
figures new

@@
 As such, it integrates a novel Hybrid Physical-Neural parameterisation able to compensate for the small-scale approximations resulting from particle-mesh schemes for cosmological N-body simulations.
-We validate our simulations in an LSST setting against high-resolution $\kappa$TNG simulations by comparing both the lensing angular power spectrum and multiscale peak counts.
+We validate our simulations in an LSST setting against high-resolution \textbf{$\kappa$TNG-Dark} simulations by comparing both the lensing angular power spectrum and multiscale peak counts.
 We demonstrate an ability to recover lensing $C_\ell$ up to a 10\% accuracy at $\ell=1000$ for sources at redshift 1, with as few as $\sim 0.6$ particles per Mpc/h.
@@
 
-We validate our simulations against the cosmological N-body simulations $\kappa$TNG \citep{osato2021kappatng} by comparing both the lensing angular power spectrum and multiscale peak counts.
+We validate our simulations against the cosmological N-body simulations \textbf{$\kappa$TNG-Dark} \citep{osato2021kappatng} by comparing both the lensing angular power spectrum and multiscale peak counts.
 
@@
 
+\begin{table}
+	\centering
+	\caption{Approximate execution times of different parts of the simulations. The values represent the mean and the standard deviation of 7 runs, 1 loop each.}
+	\begin{tabular}{lc} 
+		\hline 
+		Model  & Time  \\
+             \hline
+		LPT & 744 ms  $\pm 10.7$ ms  \\ 
+		N-Body (128$^3$) & 16.5 s $\pm 7.89$ ms   \\ 
+		N-Body ODE (128$^3$) & 13 s $\pm 120$ ms    \\ 
+    N-Body ODE+HPN (128$^3$) & 1 min 24 s $\pm$ 573 ms    \\ 
+		N-Body (256$^3$) & 1 min 14 s $\pm$ 14.1 ms  \\
+		N-Body ODE (256$^3$) & 1 min 39 s $\pm$ 181 ms   \\
+		Raytracing (Born Approximation) & 320 ms $\pm$ 16.9 ms    \\
+		\hline
+	\end{tabular}
+	\label{tab:computational_cost}
+\end{table}
+
 \subsection{Differentiable Particle-Mesh N-body simulations}
@@
 \section{Validating simulations for LSST}\label{Validating_simulations_for_LSST_Y}
-In this section, we compare the results from our simulation to other works, including the analytic models for the matter power spectrum \textit{Halofit} \citep{smith2003stable,takahashi2012revising} and the cosmological N-body simulations, $\kappa$TNG \citep{osato2021kappatng}.
+In this section, we compare the results from our simulation to other works, including the analytic models for the matter power spectrum \textit{Halofit} \citep{smith2003stable,takahashi2012revising} and the cosmological N-body simulations, \textbf{$\kappa$TNG-Dark} \citep{osato2021kappatng}.
 
@@
 We assume the following cosmological parameters: $h=0.6774$, $n_s =0.9667$, $M_{\nu} = 0.0$ eV, $w=-1$, $\Omega_k = 0.$, $\Omega_m=0.3075$, $\sigma_8= 0.8159$, such that they match the results of Planck 2015 \citep{ade2016planck}.
-We reproduce the same configuration of $\kappa$TNG, i.e. each map is on a regular grid of $1024^2$ pixels and $5\times 5$ deg$^2$.
+We reproduce the same configuration of \textbf{$\kappa$TNG-Dark}, i.e. each map is on a regular grid of $1024^2$ pixels and $5\times 5$ deg$^2$.
 
@@
     \caption{
-    \textbf{Upper panel}: Angular power spectra of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model compared to the $\kappa$TNG prediction.
-\textbf{Lower panel}: fractional angular power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the $\kappa$TNG prediction.
+    \textbf{Upper panel}: Angular power spectra of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model compared to the \textbf{$\kappa$TNG-Dark} prediction.
+\textbf{Lower panel}: fractional angular power spectrum of PM simulations before and after using the Hybrid Physical-Neural (HPN) correction model and the \textbf{$\kappa$TNG-Dark} prediction.
 The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the standard deviation from 100 DLL realisations.
@@
 In the upper panel of \autoref{fig:ps_comp}, we present the angular power spectrum computed from our Differentiable Lensing Lightcone (DLL hereafter) complemented by the HPN scheme and a conventional DLL simulation with the same resolution.
-Both the outputs are compared to the $\kappa$TNG prediction.
-In the lower panel  of \autoref{fig:ps_comp} the fractional differences between the convergence power spectra from the two maps and the $\kappa$TNG are shown.
+Both the outputs are compared to the \textbf{$\kappa$TNG-Dark} prediction.
+In the lower panel  of \autoref{fig:ps_comp} the fractional differences between the convergence power spectra from the two maps and the \textbf{$\kappa$TNG-Dark} are shown.
 Both the power spectra and ratios are averaged over $N = 100$ realisations.
 We can see that the HPN  model reduces the relative deviations of the angular power spectra to within 30\%. 
-We also observe a perfect match at large scales, since the $\kappa$TNG and the DLL simulations have the same box size of 205 Mpc/h$^3$.
+We also observe a perfect match at large scales, since the \textbf{$\kappa$TNG-Dark} and the DLL simulations have the same box size of 205 Mpc/h$^3$.
 
@@
 \subsection{Lensing $C_\ell$}
-To quantify the accuracy of the simulations we aim to reproduce the summary statistics from the Dark Matter Only $\kappa$TNG simulations. 
+To quantify the accuracy of the simulations we aim to reproduce the summary statistics from the Dark Matter Only \textbf{$\kappa$TNG-Dark} simulations. 
 We compare the results from the angular power spectrum for different source redshift, just investigating how well we can recover the power spectrum for a given source plane.
-The results of the angular power spectrum from the sources redshift z=[0.25,0.46,0.65,0.91,1.30] are shown in the upper panel of \autoref{fig:clsktng_comp}, as well as the fractional differences between the $\kappa$TNG and DLL maps in the lower panel.
+The results of the angular power spectrum from the sources redshift z=[0.25,0.46,0.65,0.91,1.30] are shown in the upper panel of \autoref{fig:clsktng_comp}, as well as the fractional differences between the \textbf{$\kappa$TNG-Dark} and DLL maps in the lower panel.
 \begin{figure}
@@
     \textbf{Upper panel}: Angular power spectra for 5 source redshift from
-our DLL maps compared to the $\kappa$TNG predictions.
- \textbf{Lower panel:} Fractional angular power spectra of DLL simulations and $\kappa$TNG simulations for different source redshift.
+our DLL maps compared to the \textbf{$\kappa$TNG-Dark} predictions.
+ \textbf{Lower panel:} Fractional angular power spectra of DLL simulations and \textbf{$\kappa$TNG-Dark} simulations for different source redshift.
   The power spectra mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
@@
 This can be explained considering that a given value of $\ell$ at lower redshift corresponds to smaller scales, some of those below the resolution of our simulations.
-We conclude that, if for z=0.91 and z=1.30 we have a general agreement with $\kappa$TNG, with this specific setting of the model, we can not model correctly cases with sources redshift lower than z=0.91.
+We conclude that, if for z=0.91 and z=1.30 we have a general agreement with \textbf{$\kappa$TNG-Dark}, with this specific setting of the model, we can not model correctly cases with sources redshift lower than z=0.91.
 
- We want to highlight that the results shown are produced keeping the resolution of the simulations extremely low, and we do not aspect to get the same precision as $\kappa$TNG.
+ We want to highlight that the results shown are produced keeping the resolution of the simulations extremely low, and we do not \textbf{expect} to get the same precision as \textbf{$\kappa$TNG-Dark}.
 The purpose of these tests, and the overall goal of the paper, is to present a proof of concept of the DLL package and its potential.
@@
 
-As for the power spectrum, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different redshift bins.
+As \textbf{with} the power spectrum, we compare the peak counts statistic from our map to the one from the \textbf{$\kappa$TNG-Dark} for different redshift bins.
 We present the results in \autoref{peaks_z}.
@@
 
-\begin{figure}\label{peaks_z}
+\begin{figure}
     \centering
     \includegraphics[width=\columnwidth]{paper/figures/res_peak_DLL_vs_ktng.pdf}
-    \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations for different sources redshift.
+    \caption{Fractional number of peaks of DLL simulations and \textbf{$\kappa$TNG-Dark} simulations for different sources redshift.
 The peak counts distributions are shown for each starlet scales resolutions used: 9.34 (upper panel), 18.17 (center panel), 37.38 arcmins (lower panel).
   The results mean over 100 independent map realisations and the shaded regions represent the standard deviation from 100 independent DLL realisations.}
-\end{figure}
+\end{figure}\label{peaks_z}
 
@@
 If we assume a Gaussian likelihood and a Covariance matrix $C_{ij}$ independent from $\theta$, we can calculate the Fisher matrix as
-\begin{equation}\label{Fisher_matrix}
+\begin{equation}
       F_{\alpha \beta}= \sum_{ij}\frac{\partial \mu}{\partial \theta_{\alpha}} C_{ij}^{-1}
       \frac{\partial \mu}{\partial \theta_{\beta}}
-\end{equation}
+\end{equation}\label{Fisher_matrix}
 were we indicate as $ \frac{\partial \mu}{\partial \theta_{\alpha}} $ the derivatives of the summary statistics w.r.t the cosmological or nuisance parameters evaluated at the fiducial values.
@@
 we decompose the noisy convergence map in seven images, we sum back only the three maps corresponding to [9.33, 18.79, 37.38] arcmin and compute the angular $C_{\ell}$ on the resulting image.
-An example of the $C_{\ell}$ computed for each individual starlet scale image and for the summed image is depicted in \autoref{window}.
+An example of the $C_{\ell}$ computed for each individual starlet scale image and for the summed image is depicted in \autoref{fig:window}.
 
@@
 Code publicly available at: \\ \href{https://github.com/LSSTDESC/DifferentiableHOS/tree/main/DifferentiableHOS/statistics}{https://github.com/LSSTDESC/DifferentiableHOS/statistics}  }
-\begin{figure}\label{window}
+\begin{figure}
     \centering
-    \includegraphics[width=0.95\columnwidth]{paper/figures/window.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/window.pdf}
     \caption{Example of the filtered $C_{\ell}$ used for the analysis.
@@
 To allow DLL to run at low resolution without affecting significantly the accuracy, we complement the FlowPM N-body code with the Hybrid-Physical Neural scheme, a new correction scheme for quasi N-body PM solver, based on Neural Network implemented as a Fourier-space filter.
-We validate our tool by comparing the $C_{\ell}$ and peak counts statistics against predictions from $\kappa$TNG simulations. 
+We validate our tool by comparing the $C_{\ell}$ and peak counts statistics against predictions from \textbf{$\kappa$TNG-Dark} simulations. 
 To do this, we run simulations following the evolution of $128^3$ particles and we produce weak lensing convergence maps for several redshift sources. 
@@
 In the left panel of  \autoref{fig:ps_comp_high}, we present the angular power spectrum computed from our DLL with the original number count of particles ($128^3$) and the power spectrum computed from higher resolutions DLL simulations ($212^3$).
-The two outputs are compared to the $\kappa$TNG predictions.
-In the right panel  of \autoref{fig:ps_comp_high} the fractional differences between the convergence power spectra from the two maps and the $\kappa$TNG are shown.
+The two outputs are compared to the \textbf{$\kappa$TNG-Dark} predictions.
+In the right panel  of \autoref{fig:ps_comp_high} the fractional differences between the convergence power spectra from the two maps and the \textbf{$\kappa$TNG-Dark} are shown.
 We can see that, by increasing the number of particles, we can improve the accuracy of the lensing $C_{\ell}$ up to $~20\%$.
-In \autoref{peaks_high}, we compare the peak counts statistic from our map to the one from the $\kappa$TNG for different resolutions.
+In \autoref{peaks_high}, we compare the peak counts statistic from our map to the one from the \textbf{$\kappa$TNG-Dark} for different resolutions.
 We use the same wavelet decomposition presented in \autoref{peak_sec}.
@@
     \includegraphics[width=\columnwidth]{paper/figures/cls_DLL_vs_ktng_high.pdf}
-        \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_high.pdf}
+        \includegraphics[width=0.90\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_high.pdf}
     \caption{
-    \textbf{Left panel}: Angular power spectra of PM simulations with original resolution (number count 128$^3$, blue line) and higher resolution (number count 212$^3$, red line) compared to the $\kappa$TNG prediction.
-\textbf{Right panel}: fractional angular power spectrum of PM simulations with original and higher resolution and the $\kappa$TNG prediction.
+    \textbf{Left panel}: Angular power spectra of PM simulations with original resolution (number count 128$^3$, blue line) and higher resolution (number count 212$^3$, red line) compared to the \textbf{$\kappa$TNG-Dark} prediction.
+\textbf{Right panel}: fractional angular power spectrum of PM simulations with original and higher resolution and the \textbf{$\kappa$TNG-Dark} prediction.
 The power spectra and ratios are means over 100 independent map realisations and the shaded regions represent the error on the mean.
@@
     \includegraphics[width=\columnwidth]{paper/figures/res_peak_DLL_vs_ktng_high.pdf}
-    \caption{Fractional number of peaks of DLL simulations and $\kappa$TNG simulations.
+    \caption{Fractional number of peaks of DLL simulations and \textbf{$\kappa$TNG-Dark} simulations.
 The results are shown for the number counts $128^3$ (blue lines) and $212^3$ (orange lines).

### 2023-07-23 paper/paper.tex
figures new

@@
 We present the Differentiable Lensing Lightcone (DLL), a fully differentiable physical model designed for being used as a forward model in Bayesian inference algorithms requiring access to derivatives of lensing observables with respect to cosmological parameters.
-We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones \denise{and implementing the Born approximation} in the Tensorflow framework.
+We extend the public FlowPM N-body code, a particle-mesh N-body solver, simulating lensing lightcones and implementing the Born approximation in the Tensorflow framework.
 Furthermore, DLL is aimed at achieving high accuracy with low computational costs.
@@
 power is recovered by the HPN correction up to $k \sim 1$, after which the method overemphasizes the small-scale power.
-\denise{In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.}
+In this article however, we can assume that this effect does not impact the results of the cosmological parameters forecast, since it concerns scales that are beyond the range of frequencies that are taken into account for the analysis.
 
@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{paper/figures/cls_DLL_vs_ktng_hpn.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/cls_DLL_vs_ktng_hpn.pdf}
         \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng_hpn.pdf}
@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{paper/figures/IA_validation.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/IA_validation.pdf}
     \includegraphics[width=\columnwidth]{paper/figures/IA_validation_res.pdf}
@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{paper/figures/cls_DLL_vs_ktng.pdf}
+    \includegraphics[width=\columnwidth]{paper/figures/cls_DLL_vs_ktng.pdf}
     \includegraphics[width=\columnwidth]{paper/figures/res_cls_DLL_vs_ktng.pdf}
@@
 \section*{Acknowledgments}
-BH is supported by the AI Accelerator program of the Schmidt Futures Foundation.
-The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
+
+DESC acknowledges ongoing support from the IN2P3 (France), the STFC 
+(United Kingdom), and the DOE, NSF, and LSST Corporation (United States).  
+DESC uses resources of the IN2P3 Computing Center 
+(CC-IN2P3--Lyon/Villeurbanne - France) funded by the Centre National de la
+Recherche Scientifique; the National Energy Research Scientific Computing
+Center, a DOE Office of Science User Facility supported under Contract 
+No.\ DE-AC02-05CH11231; STFC DiRAC HPC Facilities, funded by UK BEIS National 
+E-infrastructure capital grants; and the UK particle physics grid, supported
+by the GridPP Collaboration.  This work was performed in part under DOE 
+Contract DE-AC02-76SF00515.
+This work was granted access to the HPC/AI resources of IDRIS under the allocation 2022-AD011013922 made by GENCI.
+BH is supported by the AI Accelerator program of the Schmidt Futures Foundation; JHD acknowledges support from an STFC Ernest Rutherford Fellowship (project reference ST/S004858/1); The presented work used computing resources provided by DESC at the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.
 Department of Energy under Contract No.
 DEAC02-05CH11231;
+This paper has undergone internal review in the LSST Dark Energy Science Collaboration. We thank the internal reviewers, Virginia Ajani, William Coulton, and Jia Liu for their constructive comments.
+Author contributions to this work are as follows: Denise Lanzieri led the analysis and the writing of the paper.
+Jean-Luc Starck provided his expertise on wavelet peak counting and higher-order weak lensing statistics.
+All the authors provided feedback on
+the text.
 %=====================
@@
 \end{figure*}
-}
 
